To create a customized cover letter for Adem Mcharek tailored to the internship opportunity at Openmesh Network, we will incorporate details from both Adem Mcharek's resume and the provided information about Openmesh Network. Adem Mcharek's relevant experiences, skills, and aspirations will be aligned with the internship requirements and responsibilities at Openmesh Network.

Here is the LaTeX code for the tailored cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Openmesh Network}
\companyaddress{
Sydney, Australia
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the internship opportunity at Openmesh Network as advertised. With a strong academic background in Artificial Intelligence and a passion for cutting-edge technologies, I am excited about the prospect of contributing to a decentralized data infrastructure that aligns with my values and aspirations.}

% Matching qualifications and skills
\lettercontent{My experiences as an AI Research Assistant at LIU Brooklyn, where I developed AI systems and deep learning models, have equipped me with the technical skills necessary for contributing to the development of blockchain consensus algorithms at Openmesh Network. I am confident that my proficiency in Python, PyTorch, TensorFlow, and my academic exposure to machine learning and deep learning will be assets in collaborating on blockchain projects and applying principles of blockchain consensus.}

% Aligning with company values and mission
\lettercontent{The mission of Openmesh Network to democratize data access and challenge centralized control resonates deeply with me. I am highly motivated to be part of a team that pioneers open data clouds and analytics engines, shaping the future of data accessibility. My leadership experience as the Founder and President of the AI Club demonstrates my ability to drive innovative projects and foster a collaborative community, qualities that I am keen to bring to Openmesh Network.}

% Closing and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter integrates Adem Mcharek's academic background, technical skills, and leadership experience with the requirements and mission of Openmesh Network. It emphasizes his enthusiasm for contributing to a decentralized data infrastructure and highlights his suitability for the internship opportunity at Openmesh Network based on the provided details.