latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Intel Corporation}
\companyaddress{
Santa Clara, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the undergraduate intern position in Wide Area Cloud (WAC) research at Intel Corporation as advertised. With a strong academic background in Electrical Engineering and Computer Science, coupled with practical experience in programming languages such as C, Python, and MATLAB, I am excited about the opportunity to contribute to Intel's mission of creating world-changing technology.}

\lettercontent{During my academic journey, I have developed a solid foundation in digital signal processing and data structures, which I believe will be instrumental in the development and validation of emerging WAC solutions, as outlined in the job description. Moreover, my exposure to Linux and cloud-native architecture, along with my continuous learning in Kubernetes, aligns with the technical requirements of the role.}

\lettercontent{I am particularly enthusiastic about the research responsibilities mentioned, where I look forward to collaborating with researchers within Intel Labs to innovate and transfer cutting-edge technologies. My experience in x86 assembly also positions me well to tackle the challenges involved in this role effectively.}

% Conclusion and signature
\lettercontent{I am eager to bring my programming skills, academic knowledge, and passion for technology to Intel Corporation. I am confident that my background and enthusiasm make me a strong candidate for this internship position. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}