Based on Adem Mcharek's resume, let's proceed to construct a tailored cover letter for the position at Intel's Wireless System Research (WSR) lab focused on Wide Area Cloud (WAC) research internship opportunity. Below is the LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{hyperref}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Intel Corporation}
\companyaddress{
Santa Clara, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the undergraduate internship position at Intel's Wireless System Research (WSR) lab focusing on Wide Area Cloud (WAC) research. With a Bachelor's degree in Artificial Intelligence and a solid foundation in relevant coursework, including Machine Learning, Cloud Computing, and Software Engineering, from Long Island University, I am eager to contribute to the innovative projects at Intel.}

\lettercontent{During my tenure as an AI Research Assistant at LIU Brooklyn, I led projects utilizing cutting-edge technologies like PyTorch and TensorFlow to develop AI-driven solutions. These experiences have honed my programming skills, critical for roles requiring proficiency in C, C++, Python, Linux, and Digital Signal Processing.}

\lettercontent{My project on Computer Vision using TensorFlow demonstrates my ability to develop solutions integrating cloud-native architectures and data structures, aligning well with the responsibilities of developing and validating emerging WAC solutions at Intel. I am excited about the opportunity to collaborate with Intel Labs researchers to drive forward-thinking technologies that enhance end-to-end Quality of Service (QoS) for users.}

% Conclusion and signature
\lettercontent{I am thrilled about the prospect of contributing to Intel's groundbreaking research and am confident that my technical skills and academic background make me a strong fit for this internship opportunity. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to Adem Mcharek's experiences and skills, emphasizing his academic background, relevant projects, and technical expertise in line with the internship position at Intel's Wireless System Research (WSR) lab focusing on Wide Area Cloud (WAC) research.