To create a tailored cover letter for Adem Mcharek applying for the Summer Analyst position at BMO Capital Markets, we will integrate key information from his resume and customize the content accordingly. Below is the LaTeX code for the cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{BMO Capital Markets}
\companyaddress{
100 King Street West \\
Toronto, Canada
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Summer Analyst position at BMO Capital Markets as advertised. With a current enrollment in an undergraduate program and a projected graduation date in Spring 2026, matched with a strong GPA of X.X/4.0, I am eager to leverage my academic background and skills to contribute to the innovative work at BMO Capital Markets.}

\lettercontent{My experiences align closely with the responsibilities outlined for the role, from developing business solutions to enhancing trading strategies through quantitative modeling. As an individual dedicated to continuous learning, I am excited about the opportunity to collaborate with and learn from the talented professionals at BMO Capital Markets.}

% Matching qualifications and skills
\lettercontent{With a diverse skill set that includes knowledge of front-end and back-end developer languages, proficiency in statistical programming languages, and expertise in Excel scripting, I am prepared to engage in tasks ranging from market research and data analytics to client presentation material development. My technical writing ability and the fluency in Excel further strengthen my suitability for this position.}

% Closing and signature
\signature{Adem Mcharek}

\end{document}
```

In this cover letter, Adem's qualifications and experiences are highlighted, showcasing how they align with the requirements and responsibilities of the Summer Analyst position at BMO Capital Markets. Feel free to adjust any details or add more personalized information as needed before submitting the application.