Based on the information extracted from Adem Mcharek's resume and the details provided about Astranis Space Technologies, I will now tailor a cover letter for the position of Software Developer, Network/Payload Software - Intern at Astranis Space Technologies. 

Here is the customized LaTeX code for the cover letter:

\documentclass[]{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Astranis Space Technologies}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Software Developer, Network/Payload Software - Intern position at Astranis Space Technologies, a company that captivates me with its commitment to bridging the global digital divide through innovative satellite technology. Currently pursuing a Bachelor's degree in Artificial Intelligence with a strong foundation in Cloud Computing, Natural Language Processing, and software development, I am thrilled about the opportunity to contribute to Astranis' mission of providing internet access to underserved communities worldwide.}

\lettercontent{My academic journey, which includes a Cumulative GPA of 3.88/4.00 and relevant coursework in machine learning, deep learning, and applicable deep learning, has equipped me with a solid technical background. Moreover, my experiences in designing, writing, and testing software align closely with the responsibilities outlined for the role at Astranis. I am particularly excited about the chance to work on software running on satellites, ground control systems, and testing software to enhance satellite performance.}

\lettercontent{Furthermore, my proficiency in C++, Python, and scripting languages, coupled with a genuine passion for leveraging technology to solve real-world challenges, positions me well to thrive in Astranis' dynamic and innovative environment. I am eager to collaborate with the engineering team to develop cutting-edge software solutions that manage satellite performance from Ground Stations and contribute to Astranis' impactful initiatives.}

\lettercontent{I am inspired by Astranis' dedication to social impact and technological advancement, and I am confident that my technical skills and eagerness to learn align with the requirements and goals of the Software Developer, Network/Payload Software - Intern position. I am excited about the prospect of contributing to Astranis' groundbreaking work and being part of a team that is revolutionizing global connectivity.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}

This cover letter is tailored to showcase Adem Mcharek's academic background, skills, and enthusiasm for the role at Astranis Space Technologies. The content highlights how Adem's experiences and aspirations align with the company's mission and the specific requirements of the internship position.