Based on the information provided about Acorns' internship opportunity for Software Engineering, I will now craft a tailored cover letter in LaTeX format for Adem Mcharek to apply for the position. I will incorporate his qualifications, experiences, and aspirations to make the cover letter stand out. Let's proceed with creating the customized cover letter.Based on Adem Mcharek's resume and the details provided about the Acorns internship opportunity, I will now generate a tailored cover letter for Adem Mcharek to apply for the Software Engineering Intern position at Acorns. Below is the LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Acorns}
\companyaddress{
Irvine, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Software Engineering Intern position at Acorns as advertised. With a Bachelor's degree in Artificial Intelligence from Long Island University and a passion for utilizing cutting-edge technologies to address real-world challenges, I am excited about the opportunity to contribute to Acorns' mission of empowering individuals through micro-investing using artificial intelligence.}

\lettercontent{Through my role as an AI Research Assistant, I have gained hands-on experience in developing AI-powered solutions, collaborating with multidisciplinary teams, and presenting findings in technical meetings. My proficiency in programming languages like Python, experience with deep learning frameworks such as PyTorch and TensorFlow, and my problem-solving skills align well with the requirements of the position.}

\lettercontent{Moreover, my active involvement in leading the AI Club and participating in international mathematical competitions has honed my leadership, teamwork, and analytical abilities. I am eager to leverage my technical skills, creativity, and proactive mindset to make meaningful contributions to Acorns' AI-powered projects, while embracing the values of leading with heart, making bold decisions, and never stopping to grow.}

\lettercontent{I am excited about the opportunity to further develop my AI concepts and methodologies, contribute to optimizing AI tools, and expand my professional network at Acorns. I am committed to embracing challenges, learning from feedback, and prioritizing tasks efficiently to deliver high-quality results.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am enthusiastic about the possibility of contributing to the innovative projects at Acorns and would welcome the opportunity to discuss how my background, skills, and dedication align with the company's mission.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to highlight Adem Mcharek's relevant experiences, skills, and aspirations that align with the requirements and responsibilities of the Software Engineering Intern position at Acorns. It emphasizes his enthusiasm for the role and his eagerness to contribute to Acorns' mission of financial wellness through innovative technologies.