Based on the information provided about Okta and the Technical Marketing Manager Internship opportunity, I will now craft a tailored cover letter for Adem Mcharek to apply for this position at Okta. I will integrate his experiences, skills, and aspirations to align with the requirements and responsibilities of the role. Below is the LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Okta}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Technical Marketing Manager Internship at Okta, as advertised. With a background in Computer Science and a passion for leveraging technology to solve real-world challenges, I am excited about the opportunity to contribute to Okta's mission of enabling secure and seamless access for everyone in the digital world.}

% Alignment with requirements and responsibilities
\lettercontent{During my academic pursuit in Computer Science, I have honed my skills in programming languages such as ES6/7, Python, and Java, allowing me to apply theoretical knowledge to practical scenarios effectively. My experience in web services and REST API aligns well with the requirement to understand and communicate technical solutions to business needs. I am eager to collaborate in creating technical assets and building product demos to showcase the capabilities of Okta's Customer Identity Cloud.}

% Incorporating desired qualifications
\lettercontent{Moreover, my familiarity with Node.js applications, deployment of applications to IaaS/SaaS platforms, and basic understanding of IAM protocols like OAuth and SAML, position me to quickly adapt and contribute to the technical content creation process at Okta. Additionally, my exposure to Terraform for Infrastructure as Code and basic video editing skills further complement the desired qualifications for this role.}

% Closing and signature
\lettercontent{In conclusion, I am excited about the prospect of joining Okta, a company renowned for its industry leadership and commitment to fostering a diverse and inclusive work environment. I am eager to leverage my technical acumen and collaborative spirit to support Okta in empowering individuals and businesses through innovative identity solutions. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to Adem Mcharek's background and experiences, aligning them with the requirements, responsibilities, and desired qualifications for the Technical Marketing Manager Internship at Okta. It highlights his technical skills, collaborative mindset, and enthusiasm for contributing to Okta's innovative identity solutions.