\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Bertram Labs}
\companyaddress{
Broomfield, CO
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Software Engineering Intern position at Bertram Labs as advertised. With a background as an AI Research Assistant at LIU Brooklyn and a demonstrated ability to drive innovative projects, I am excited about the opportunity to contribute to the dynamic environment at Bertram Capital.}

\lettercontent{During my time as an AI Research Assistant, I successfully launched and led the AI Club, fostering a community of over 50 enthusiasts and spearheading projects that significantly enhanced members' hands-on experience and research capabilities【9†source】【10†source】. Additionally, my achievements in securing bronze and silver medals at the International Youth Mathematical Olympiad attest to my analytical skills and problem-solving abilities【11†source】【12†source】.}

% Matching qualifications with requirements and responsibilities
\lettercontent{The requirements for the Software Engineering Intern position closely align with my academic background and practical experience. Currently enrolled in an undergraduate degree program in a related field, I have strong proficiency in programming languages such as Java and Python, along with experience in collaborative team projects. My exposure to source code control systems like Git further strengthens my technical skill set.}

\lettercontent{I am particularly drawn to the opportunity to work on all facets of the solution development lifecycle at Bertram Labs, including requirements gathering, project management, and release planning. My experience in leading projects and working collaboratively in a team equips me to excel in this multifaceted role【10†source】.}

% Conclusion and signature
\lettercontent{I am thrilled about the possibility of contributing to Bertram Labs and am eager to bring my passion for technology and problem-solving to your esteemed organization. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}