\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Elevance Health}
\companyaddress{
Indianapolis, Indiana
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Data Analytics Internship position at Elevance Health as advertised. Currently enrolled in a Bachelor's program in Business Analytics at an accredited university, I am thrilled about the opportunity to contribute to the GIC Operations – Unicare team and engage in quantitative data analytics, business data reporting, and impact analysis.}

% Adem's qualifications and skills alignment
\lettercontent{With a solid background in data science and analytics, I am well-equipped to develop high-quality reports, analyze large-scale datasets, and provide valuable insights to support critical projects. My experience includes utilizing data processing tools, collaborating effectively with team members, and delivering assignments accurately and on time.}

% Closing and aspiration alignment
\lettercontent{I am particularly drawn to Elevance Health's mission of improving lives and communities through a holistic approach to healthcare. I am eager to leverage my problem-solving, analytical, and organizational skills to contribute meaningfully to the team's success while enhancing my knowledge and skills in a dynamic environment.}

\lettercontent{Thank you for considering my application. I am excited about the possibility of contributing to Elevance Health and would welcome the opportunity to further discuss how my background, skills, and enthusiasm align with the internship role.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}