\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{CACI International Inc}
\companyaddress{
Reston, Virginia
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

I am writing to express my interest in the Junior Software Developer Intern position at CACI International Inc as advertised. With a strong educational background in Computer Science and relevant experience in software development and data analysis, I am excited about the opportunity to contribute to your team and enhance my skills in a dynamic environment such as CACI.

During my academic pursuits, I have acquired a solid foundation in programming languages including Python, Java, and C++, as well as hands-on experience with databases, data repositories, and open-source data science tools. My coursework and projects have equipped me with the necessary skills to perform software development, write custom queries, develop metrics, and work on system integrations, aligning well with the responsibilities outlined for the role at CACI.

Moreover, my proactive approach to learning and problem-solving, coupled with my strong communication skills, allow me to effectively collaborate with team members and contribute meaningfully to achieving project goals. I am particularly interested in the opportunity to engage in data science activities, analyze data trends, and propose analytics to drive innovation and add value to the organization's research and development efforts.

% Key qualifications and alignment with job requirements

I meet the essential requirements for the position, including U.S. Citizenship, progress towards a Computer Science degree, Security+ Certification (in progress), and proficiency in programming languages such as HTML, CSS, JavaScript, and Python. Additionally, my experience with both Windows and Linux operating systems, along with a strong foundation in cyber activities and networks, positions me well to excel in the Junior Software Developer Intern role at CACI.

I am eager to leverage my technical skills, enthusiasm for software development, and dedication to continuous learning to contribute to CACI's innovative projects and operational excellence. I am confident that my background and aspirations align closely with the job expectations and the vibrant culture of integrity and dedication that CACI International Inc upholds.

Thank you for considering my application. I am enthusiastic about the possibility of contributing to CACI's mission and would welcome the opportunity to discuss how my qualifications and passion for technology can benefit your team. 

% Conclusion and signature
\lettercontent{Sincerely,}

\signature{Adem Mcharek}

\end{document}