\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Intel Corporation}
\companyaddress{
Santa Clara, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the technical internship position at Intel focusing on Hardware Validation and System-Level Debug on next generation Intel Xeon microprocessors, as advertised. With a strong educational background and hands-on projects in areas closely related to the responsibilities outlined, I am excited about the opportunity to contribute to Intel's world-class semiconductor technology.}

\lettercontent{During my academic journey, I have delved into projects involving digital design, computer architecture, and programming, aligning closely with the qualifications required for the role. These experiences have equipped me with the skills necessary to assist with Hardware Validation and System-Level Debug effectively.}

\lettercontent{The innovative environment and emphasis on collaboration at Intel resonate with me, and I am keen to leverage my technical proficiency to contribute to the validation and debugging processes for the next generation of Intel Xeon microprocessors. My ability to translate complex technical concepts into practical solutions, honed through various projects, positions me well to excel in this role.}

\lettercontent{I am particularly drawn to Intel's commitment to technological innovation and excellence, and I am excited about the opportunity to be part of a team that drives semiconductor advancements on a global scale.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I look forward to the possibility of discussing how I can contribute to Intel's cutting-edge projects and the future of semiconductor technology.}

\signature{Adem Mcharek}

\end{document}