\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Rivian Electric Vehicles}
\companyaddress{
Irvine, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the internship opportunity at Rivian Electric Vehicles as a Demand Forecasting Intern. Currently pursuing my bachelor's degree at an accredited university, with a strong background in statistics, econometrics, and data analysis, I am excited about the chance to contribute directly to Rivian’s commercial and production strategies by forecasting demand for Rivian’s products.}

\lettercontent{Drawing from my diverse experiences in research and analysis, including projects optimizing algorithms and modeling infrastructures, I have honed the ability to translate complex mathematical concepts into practical solutions. The meticulous attention Rivian pays to vehicle capability resonates with my commitment to precision and optimization in data analysis, aligning directly with my skills and aspirations.}

% Key qualifications and contributions
\lettercontent{With technical proficiency in Excel, Powerpoint, Python, SQL, and Tableau, I am well-equipped to parse, analyze, and present key industry data to estimate demand for Rivian’s products accurately. I am eager to work on developing statistical models for demand trending and contribute to the cutting-edge demand sensing and modeling toolset at Rivian.}

% Closing and call to action
\lettercontent{Rivian’s dedication to innovation, sustainability, and technical excellence makes it a compelling environment for me to grow professionally while making a positive impact. I am keen on the opportunity to collaborate with Rivian's talented teams and contribute to its visionary goals. I have enclosed my resume for your review and look forward to the possibility of discussing how I can support Rivian's ambitions further.}

% Signature
\signature{Adem Mcharek}

\end{document}