\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Wisk Aero}
\companyaddress{
Mountain View, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Internship role with Wisk Aero, particularly in joining the Loads \& Dynamics team to contribute to the assessment of aircraft aeroelastic stability and external loads generation. With a Bachelor's degree in Engineering and over 2 years of relevant studies, I am excited about the opportunity to apply my knowledge of propeller/helicopter loads, aeroelasticity, and rotor dynamics to support the generation of aeroelastic analyses as well as preparing and processing test data, as outlined in the job requirements.}

\lettercontent{During my academic endeavors, I have gained a strong understanding of fixed-wing and rotorcraft aerodynamics, aligning well with the responsibilities of the position at Wisk Aero. Furthermore, my proficiency in MATLAB and my familiarity with tools like MSC Nastran make me well-equipped to create routines for data post-processing, a task essential for a successful evaluation of flutter, external loads, and vibration flight test data.}

\lettercontent{The prospect of working at Wisk Aero excites me not only for the technical challenges it presents but also for the opportunity to contribute to the future of urban mobility through electric, autonomous flight. I am eager to collaborate with a passionate team dedicated to solving high-impact problems and shaping a sustainable future in aviation.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am looking forward to the possibility of contributing to Wisk Aero and am excited about the chance to be part of the transformative work your team is doing.}

\signature{Adem Mcharek}

\end{document}