\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Cadence Design Systems}
\companyaddress{
San Jose, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{To the Hiring Manager,}

\lettercontent{I am writing to express my interest in the Electrical or Computer Engineering Intern position at Cadence Design Systems, as advertised. With a strong academic background and practical experience in software development, I believe that my skills and passion for learning make me a suitable candidate for this role.}

% Key experiences and skills
\lettercontent{Having completed coursework in Computer Science at [University Name], I have acquired a solid foundation in programming languages such as C and C++. Additionally, my familiarity with Qt, Visual Studio, and Perforce aligns well with the desired qualifications for the position.}

\lettercontent{During my previous projects, I have demonstrated excellent verbal and written communication skills, coupled with a keen eye for detail, as I actively contributed to shaping geometric algorithms and evaluating polygon shapes, tasks that are central to the responsibilities outlined for this internship.}

% Closing paragraph
\lettercontent{I am excited about the opportunity to work on critical geometric algorithms within the Allegro PCB design tool at Cadence Design Systems. The chance to contribute to innovative solutions and collaborate with a team of industry experts greatly appeals to me.}

\lettercontent{Thank you for considering my application. I am eager to bring my technical skills and enthusiasm for problem-solving to Cadence Design Systems.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}