\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Intel Corporation}
\companyaddress{
Santa Clara, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Data Engineer position at Intel Corporation as advertised. With a Bachelor's degree in Data Science and solid educational experience, including relevant industry exposure, I am excited about the opportunity to contribute to Intel's mission of creating world-changing technology.}

\lettercontent{Having a passion for solving technical challenges and working collaboratively with cross-functional teams to deliver innovative solutions aligns perfectly with the responsibilities outlined for the role at Intel. My ability to develop quick engineering solutions, provide schedule updates, and prioritize tasks independently have been honed through my academic projects and industry experiences.}

\lettercontent{Furthermore, my excellent written and communication skills, coupled with a natural focus on quality and discipline, make me well-equipped to excel in a multi-site team setting at Intel. I am particularly drawn to the dynamic environment at Intel, where relentless innovation and commitment to technological advancements are paramount.}

\lettercontent{I am confident that my problem-solving skills, adaptability to ambiguity, and strong educational background make me a suitable candidate for the Data Engineer position at Intel. I am eager to contribute to Intel's impactful projects and be part of a team that thrives on pushing the boundaries of technology.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}