\documentclass[]{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{The Boring Company}
\companyaddress{
Bastrop, Texas
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Software Engineering Intern position at The Boring Company, as advertised. With a deep interest in cutting-edge technology and a strong academic background in Artificial Intelligence at Long Island University, coupled with a GPA of 3.88, I am excited about the opportunity to contribute to your mission of revolutionizing transportation networks through innovative technology.}

% Matching skills and experiences
\lettercontent{My coursework in Machine Learning, Deep Learning, and Software Engineering has equipped me with a solid foundation in developing software applications using Python, C++, and high-level languages. Additionally, my projects in Cloud Computing and Natural Language Processing have honed my skills in creating practical solutions from theoretical concepts, aligning well with the responsibilities of supporting the software engineering team and designing tools for the tunnel boring machines at The Boring Company.}

% Additional skills and qualifications
\lettercontent{Moreover, my experience with SQL and NoSQL databases, as well as versioning tools like git, provides me with a strong technical background that matches the requirements of the role. I am highly motivated to learn new skills rapidly, adapt to new challenges, and work with imperfect information, ensuring efficient and effective contributions to your projects.}

% Closing and signature
\lettercontent{I am eager to leverage my academic knowledge and technical skills to support the development of automation and application software for the next generation of tunnel boring machines at The Boring Company. I am confident that my passion for innovation and problem-solving makes me a strong candidate for this role. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}