\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Raptor Maps}
\companyaddress{
Somerville, Massachusetts
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the web application development position at Raptor Maps, as advertised. With a background that includes projects optimizing algorithms and modeling for infrastructure, I am excited about the opportunity to merge my technical proficiency with the intriguing dynamics of the solar industry.}

% Skills and Experiences at Raptor Maps
\lettercontent{I have honed my skills in Python and JavaScript, essential for web application development, and I am keen on further developing my expertise in machine learning, aligning with Raptor Maps' focus on data normalization and performance enhancement across solar installations. My academic journey has equipped me with a versatile skill set, including a keen analytical acumen and a drive for delivering impactful solutions.}

% Fit with Company and Role
\lettercontent{Raptor Maps' commitment to technical advancement and industry leadership resonates with my aspirations, particularly in utilizing cutting-edge technology for climate tech solutions. The unique blend of services offered by Raptor Maps, including aerial inspections and mobile tools, aligns with my passion for renewable energy and technology.}

% Closing and Signature
\lettercontent{I am enthusiastic about the prospect of contributing to Raptor Maps' mission of enhancing solar performance and minimizing risk through innovative software solutions. I look forward to the opportunity to discuss how my skills and experiences can benefit Raptor Maps in achieving its goals.}

\signature{Adem Mcharek}

\end{document}