\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{DoubleVerify}
\companyaddress{
New York, New York
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Data Engineer Intern position at DoubleVerify. With a Bachelor's degree in Artificial Intelligence from Long Island University and a strong passion for data-driven insights, I am excited about the opportunity to contribute to DoubleVerify's mission of providing transparent and effective digital advertising solutions. My academic background, coupled with hands-on projects in artificial intelligence and data analysis, align well with the requirements and responsibilities of the role.}

% Personalized content
\lettercontent{During my tenure as an AI Research Assistant at LIU Brooklyn, I led projects integrating advanced technologies to automate academic research processes, demonstrating my ability to work on data-intensive applications efficiently. My experience developing Convolutional Neural Networks and computer vision systems, as showcased in projects like the PyTorch CNN for MNIST and Computer Vision using TensorFlow, underlines my proficiency in handling large-scale data processing and analytics. Furthermore, my leadership as the Founder and President of the AI Club reflects my collaborative nature and drive to tackle complex projects with innovative solutions.}

% Closing and signature
\lettercontent{I am particularly drawn to DoubleVerify's commitment to strengthening the digital advertising ecosystem through cutting-edge technology and data analysis, and I am eager to contribute to such impactful work. I am excited about the prospect of working in a dynamic environment like DoubleVerify, known for its culture of innovation and excellence. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}