\documentclass[]{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Astranis Space Technologies}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the 2024 Software Engineering Summer Internship – User Interface Team at Astranis Space Technologies. With a Bachelor's degree in Artificial Intelligence from Long Island University and a strong background in software engineering, particularly in AI and machine learning, I am excited about the opportunity to contribute to your innovative projects and high-profile initiatives.}

\lettercontent{My experience as an AI Research Assistant at LIU Brooklyn, where I developed AI solutions for real-time academic literature retrieval and implemented deep learning models such as Convolutional Neural Networks, has equipped me with the technical skills necessary to excel in a dynamic and challenging environment like Astranis Space Technologies. Additionally, my proficiency in technologies such as React, Typescript, and CSS aligns well with the requirements of the internship, enabling me to quickly adapt and contribute to the development of UI features across the full stack.}

\lettercontent{The responsibilities outlined for the internship, including taking ownership of production features, engaging in architecture discussions, and leveraging design systems for UI development, resonate with my passion for creating aesthetic and functional user interfaces. I am particularly excited about the opportunity to collaborate with senior developers to enhance the performance, stability, and scalability of Astranis' user interface platform, contributing to its continuous improvement and growth.}

% Conclusion and signature
\lettercontent{I am confident that my analytical mindset, creative problem-solving abilities, and strong interest in Capital Markets and Finance make me a well-suited candidate for this internship. I am eager to bring my skills and enthusiasm to the User Interface Team at Astranis Space Technologies and contribute to its mission of advancing space technology. Thank you for considering my application.}

\lettercontent{Warm regards,}

\signature{Adem Mcharek}

\end{document}