\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Plus}
\companyaddress{
Silicon Valley, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager at Plus,}

\lettercontent{I am writing to express my deep interest in the opportunity to join Plus, a global provider of highly automated driving and fully autonomous driving solutions, known for its commitment to innovation and sustainable transportation. As a Bachelor in Artificial Intelligence student with a strong foundation in relevant coursework such as Machine Learning, Deep Learning, and Cloud Computing, I am excited about the prospect of contributing to Plus's transformative technology in the autonomous driving industry.}

% Tailored content based on Adem Mcharek's skills and experiences

\lettercontent{With proficiency in Python, Linux CLI, and a keen understanding of the main components of autonomous driving software stack, I am well-equipped to review and improve existing implementations, troubleshoot software errors, and work collaboratively with engineering teams to meet functional safety standards. My academic background and hands-on projects have honed my ability to translate complex concepts into practical solutions, making me well-prepared to write production-level code and conduct thorough testing activities as outlined in the job requirements at Plus.}

\lettercontent{Moreover, my additional experiences align closely with Plus's desired qualifications. I have familiarity with collaborative documentation systems, previous work with interdisciplinary projects, and a basic understanding of functional safety concepts, which I believe will further strengthen my contributions to Plus's innovative projects in the autonomous driving sector.}

% Conclusion and signature
\lettercontent{I am enthusiastic about the opportunity to contribute to the future of autonomy at Plus and look forward to the possibility of discussing how my skills and aspirations align with the mission and values of your organization. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}