\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Kairos Power}
\companyaddress{
Alameda, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Data Analytics, Engineering \& Manufacturing Intern position at Kairos Power, a company that truly stands out in the clean energy sector with a clear mission to transition the world to sustainable energy sources. With a background in [relevant field based on Adem's expertise], I am excited about the opportunity to contribute to the commercialization of the fluoride-salt-cooled, high-temperature reactor (FHR), aligning with Kairos Power's commitment to technical innovation and environmental responsibility.}

% Key Experiences and Skills
\lettercontent{During my [mention relevant experience, e.g., academic studies], I have honed my skills in data analysis, engineering documentation analysis, and system enhancements. My proficiency in Python and SQL, along with experience in Tableau, equips me to develop operational reports and dashboards, facilitating data-driven decision-making processes within the company. My strong organizational skills, attention to detail, and ability to collaborate effectively within a team make me an ideal fit for the dynamic environment at Kairos Power.}

% Closing and Signature
\lettercontent{I am enthusiastic about the opportunity to contribute to Kairos Power's mission and to help build a sustainable future through innovative energy solutions. I am looking forward to the possibility of discussing how my background, skills, and enthusiasm align with the requirements of the Data Analytics, Engineering \& Manufacturing Intern role. Thank you for considering my application.}

\lettercontent{Sincerely,}

\signature{Adem Mcharek}

\end{document}