\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Cadence Design Systems}
\companyaddress{
San Jose, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the software engineering internship position at Cadence Design Systems. As a current student pursuing a Bachelor's degree in Artificial Intelligence at Long Island University with a strong GPA of 3.88, I have developed a solid foundation in technical skills and theoretical knowledge that aligns well with the requirements of the internship role.}

\lettercontent{During my academic journey, I have engaged in diverse projects, including optimizing algorithms and modeling for practical applications like electric scooter infrastructure. These experiences have equipped me with the ability to translate complex mathematical concepts into real-world solutions, a skill that I believe will be invaluable in contributing to Cadence's innovative projects.}

\lettercontent{I am particularly drawn to Cadence Design Systems' commitment to technological innovation and collaborative work environment. The opportunity to work on software code development for standard cell layout generation and PPA analysis and optimization aligns perfectly with my aspirations and technical skills. My exposure to advanced concepts in Artificial Intelligence and my hands-on experience make me well-prepared to tackle the challenges of the semiconductor design environment at Cadence.}

\lettercontent{I am excited about the chance to work closely with Cadence's foundry partners, an experience that I believe will enhance my understanding of the semiconductor industry and contribute to my professional growth. I am eager to leverage my educational background and dedication to problem-solving in a dynamic setting like Cadence to contribute effectively and learn from the industry leaders.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}