\documentclass[]{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{plain}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Chime}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Intern position at Chime's Funding Habits team, as advertised. Currently pursuing a Bachelor's degree in Artificial Intelligence at Long Island University, I have developed a solid foundation in relevant subjects such as Machine Learning, Deep Learning, and Software Engineering, achieving a Cumulative GPA of 3.88/4.00.}

\lettercontent{With a passion for consumer FinTech and a drive to dive into the deepest levels of technology, I am excited about the opportunity to apply my knowledge and skills in a real-world setting at Chime. The chance to work alongside experienced engineers in designing, developing, and scaling systems aligns perfectly with my career aspirations.}

% Aligning skills and responsibilities
\lettercontent{During my academic journey, I have undertaken projects that involved translating complex mathematical concepts into practical solutions, showcasing my ability to analyze and solve real-world problems. The responsibilities outlined, such as participating in the full software development lifecycle, collaborating with cross-functional teams, and learning new technologies, resonate with my experiences and aspirations.}

% Closing and signature
\lettercontent{I am confident that my strong analytical skills, passion for learning, and adaptability make me a suitable candidate for this role at Chime. I am eager to contribute to Chime's mission of providing financial peace of mind through innovative solutions. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}