\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Square}
\companyaddress{
Oakland, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the hardware engineering position at Square, a company dedicated to building infrastructure for online payments and empowering businesses in the economy. As a student with a background in Mechanical Engineering, as well as Mechatronics, I am excited about the opportunity to contribute my technical skills and passion for innovation to Square's hardware team.}

\lettercontent{Throughout my academic journey and projects, such as optimizing algorithms and modeling for various infrastructures, I have acquired a solid foundation in translating complex concepts into practical solutions. I am particularly drawn to Square's commitment to technological innovation and collaborative work environment, which align perfectly with my aspirations and capabilities.}

% Matching qualifications and responsibilities
\lettercontent{I meet the requirements for the role by pursuing a degree in a related technical field, being familiar with programming languages like Python and Matlab, and having experience in utilizing statistical methods for data analysis. Additionally, my hands-on experience with hardware lab equipment and automation systems makes me well-suited to contribute to researching technologies and analyzing test data for Square's hardware products.}

\lettercontent{I am eager to immerse myself in Square's hardware development processes, collaborate with cross-functional teams, and support continuous improvement initiatives to enhance product quality and performance. My proactive problem-solving skills, adaptability, and strong communication capabilities further position me to excel in a dynamic environment like Square.}

% Closing and signature
\signature{Adem Mcharek}

\end{document}