\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Leidos}
\companyaddress{
Reston, Virginia
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Software Engineering Intern position at Leidos, particularly within the ISRMEP/PED Systems Division. Currently pursuing a Bachelor's degree in Computer Science, with a rising senior class standing and a graduation year of 2025, I am eager to contribute my skills and enthusiasm to your team.}

\lettercontent{With a strong background in computer programming languages such as C++, Java, and Python, I am well-equipped to assist in the design, development, and maintenance of mission-critical software for national defense systems. My hands-on experience in software design, as well as my active pursuit of knowledge in state-of-the-art programming techniques, aligns well with the responsibilities outlined for the internship at Leidos.}

\lettercontent{Furthermore, my passion for innovation and continuous learning makes me excited about the opportunity to contribute to investments and research that drive technological advancements within the defense industry. I am confident that my proficiency in software development and my commitment to staying abreast of industry trends make me a suitable candidate for this role.}

\lettercontent{Thank you for considering my application. I am looking forward to the possibility of contributing to the impactful work at Leidos.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}