\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Crowd Strike}
\companyaddress{
Global Leader in Cybersecurity
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Operations Program Intern position at Crowd Strike as advertised. With a strong educational background in Business Management and a keen interest in exploring the operational facets of a Product & Engineering organization, I am excited about the opportunity to contribute to Crowd Strike’s mission of making the digital world a safer place to live and work.}

\lettercontent{My experiences, including observing and participating in cross-functional team meetings, align well with the responsibilities outlined for the role. I am proficient in utilizing Google Drive and Microsoft Outlook, essential skills that I am eager to apply in supporting the executive support, travel/meetings, and administration aspects at Crowd Strike. Furthermore, my ability to evaluate data quality and my interest in automation solutions make me well-suited for potential projects involving process improvements and streamlined operations.}

\lettercontent{I am particularly drawn to Crowd Strike's commitment to fostering a culture of diversity, equity, and inclusion. I believe in the power of collective action and a diverse workforce in driving innovation and achieving the best outcomes for customers and communities. I am excited about the prospect of joining a global team dedicated to continuous improvement and making a meaningful impact.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am eager to bring my skills and enthusiasm to the Operations Program Intern role at Crowd Strike and contribute to the company’s success. I look forward to the possibility of discussing how my background, skills, and aspirations align with the goals of Crowd Strike.}

\signature{Adem Mcharek}

\end{document}