\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Osmo}
\companyaddress{
Cambridge, Massachusetts
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Psychophysics Analyst internship position at Osmo. With a Bachelor's degree in Artificial Intelligence from Long Island University Brooklyn, combined with hands-on experience in AI research, computer vision, and machine learning projects, I am excited about the opportunity to merge my technical skills with the pioneering work at Osmo in digitizing the sense of smell.}

\lettercontent{My academic background, including relevant courses in Machine Learning, Deep Learning, Statistics, and Physics, has equipped me with a solid foundation in quantitative science. Moreover, my experience in working on AI projects, such as developing AI-enabled tools for academic literature retrieval and implementing neural networks like PyTorch CNN for image classification, demonstrates my proficiency in Python, Jupyter notebooks, and experimental design.}

\lettercontent{I am particularly drawn to Osmo's innovative culture and its mission to enhance human health and wellbeing through digital olfaction. The opportunity to collaborate with neuroscientists and software engineers to optimize data collection designs, design new experiments, and utilize data science skills aligns perfectly with my aspirations and skills. I am eager to contribute to Osmo's groundbreaking work in giving computers a sense of smell.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am looking forward to the possibility of contributing to Osmo's transformative projects.}

\signature{Adem Mcharek}

\end{document}