\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Astranis Space Technologies}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Software Engineer position at Astranis Space Technologies as advertised. With a Bachelor's degree in Artificial Intelligence from Long Island University, I have developed a strong technical foundation and problem-solving skills that align well with the requirements of the role.}

\lettercontent{During my academic journey, I have engaged in projects that involved optimizing algorithms and modeling, demonstrating my ability to translate complex mathematical concepts into practical solutions. My experiences have equipped me with the creativity, quick problem-solving capabilities, and analytical rigor necessary to excel in a fast-paced environment like Astranis Space Technologies.}

% Highlight relevant qualifications and skills
\lettercontent{I have a solid background in a programming language, particularly Java, along with a basic knowledge of Git and databases. Moreover, my interest in Capital Markets and Finance, coupled with my experience with messaging systems like Kafka, positions me well to contribute effectively to building state-of-the-art real-time applications for compliance with global financial regulations at Astranis.}

% Detail how past experiences align with the responsibilities
\lettercontent{This opportunity excites me as I see it as a perfect fit to leverage my technical skills and passion for innovation. I am eager to work on optimizing complex workflows, developing solutions, and contributing to a performant code base while actively engaging with a modern tech stack and cloud deployments using containers.}

% Closing and signature
\lettercontent{Thank you for considering my application. I am enthusiastic about the possibility of contributing to Astranis Space Technologies and am looking forward to the opportunity to discuss how my background and skills align with the company's innovative projects.}

\signature{Adem Mcharek}

\end{document}