\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Arcellx}
\companyaddress{
Rockville, Maryland
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the position at Arcellx, a clinical-stage biotechnology company reimagining cell therapy for patients with cancer and other incurable diseases. With a background in chemical engineering and a keen interest in pursuing a career in biotechnology and process engineering, I am excited about the opportunity to contribute to Arcellx's mission of advancing innovative immunotherapies.}

\lettercontent{My educational background in chemical engineering, as detailed in my resume, has equipped me with the necessary skills to establish E2E processes and systems for data collection, storage, reporting, and statistical analysis. Moreover, my exposure to college-level statistical courses in data analysis and D.O.E. design aligns well with the requirements specified for the role at Arcellx.}

\lettercontent{Through my academic projects and experiences, such as optimizing algorithms and modeling for infrastructure projects, I have demonstrated the ability to translate complex concepts into practical solutions. I am particularly drawn to the responsibilities outlined for the position, including establishing internal policies for statistical analysis and collaborating with cross-functional teams to implement shared data lakes.}

\lettercontent{I am impressed by Arcellx's core values of audacity, determination, collaboration, and originality, which resonate with my own values of continuous learning, innovation, and collaboration. I am eager to bring my skills and passion for biotechnology to Arcellx, where I believe I can contribute effectively to the cutting-edge work being done in developing safer and more effective cell therapies.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}