\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Smarsh}
\companyaddress{
Portland, Oregon
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Summer Internship 2024 opportunity at Smarsh, as advertised. With a strong background in Computer Science and a keen interest in cutting-edge technologies, I am excited about the prospect of contributing to a dynamic and forward-thinking company like Smarsh.}

% Adem's qualifications and aspirations tailored to the job requirements
\lettercontent{Through my studies towards a B.Sc in Computer Science and practical experience in programming, I have developed a solid foundation in relevant languages and technologies such as MongoDB, Elastic Search, and Kubernetes. My strong analytical and problem-solving skills, combined with a proactive approach to collaborating in agile environments, align well with the requirements outlined by Smarsh.}

\lettercontent{I am particularly drawn to the responsibility of designing and developing features in Java for enterprise-grade products, as well as the opportunity to work on internal tools to facilitate operational efficiency. I am keen to leverage my proficiency in JVM languages and interest in modern software architecture to contribute effectively to projects specializing in compliant archival, a domain that resonates with my career aspirations.}

% Conclusion and signature
\lettercontent{Smarsh's emphasis on innovation, collaboration, and fostering personal development resonates with my values and professional goals. I am eager to work alongside your team to deliver high-quality software solutions, while embracing opportunities to learn and grow under the mentorship of senior team members.}

\lettercontent{Thank you for considering my application. I am looking forward to the possibility of contributing to the success of Smarsh during the Summer Internship 2024.}

\signature{Adem Mcharek}

\end{document}