\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Leidos}
\companyaddress{
Arlington, V A
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Program Manager Intern position at Leidos as advertised. With a strong background in technical studies and demonstrated leadership skills, I am excited about the opportunity to contribute to projects of national importance within your Maritime software team.}

% Matching qualifications and responsibilities
\lettercontent{In alignment with your requirements, I am currently pursuing a degree in a technical field, coupled with a track record of leadership experience in both academic and extracurricular settings. My proficiency in the Microsoft Office suite will enable me to effectively assist in coordinating and tracking multidisciplinary projects, as mentioned in the job description. Furthermore, I am keen on obtaining a Do D Secret clearance to fully engage with the responsibilities associated with this role.}

\lettercontent{Moreover, I am well-versed in utilizing Atlassian tools such as JIRA and Confluence, which will facilitate my ability to create and deliver comprehensive reports efficiently. I am eager to leverage my analytical skills to identify, analyze, and report risk and schedule variances, collaborating closely with program management and technical teams to ensure successful project outcomes.}

% Closing the letter
\lettercontent{With a passion for program management and a keen interest in software development principles, including exposure to SQL, Linux, C++, and Java, I am confident in my ability to contribute effectively to Leidos. I am particularly excited about the prospect of collaborating with a diverse team of professionals at Leidos to drive innovation and achieve shared goals.}

\lettercontent{Thank you for considering my application. I am enthusiastic about the opportunity to potentially join the Leidos team and contribute to your mission of making the world safer, healthier, and more efficient through technology.}

% Signature
\signature{Adem Mcharek}

\end{document}