\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Astranis Space Technologies}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Strategy & Analytics Intern position at Astranis Space Technologies. As a dedicated student pursuing a Bachelor's degree in Artificial Intelligence with a strong background in machine learning, deep learning, and data analysis, I am excited about the opportunity to merge my technical skills with the challenging dynamics of the communications industry.}

\lettercontent{Throughout my academic journey, I have engaged in numerous projects that involved conducting in-depth analysis and utilizing advanced algorithms to solve real-world problems. For instance, my work on developing custom scorecards and dashboards for program performance evaluation demonstrates my ability to distill complex data into actionable insights, a skill crucial for the Strategy & Analytics role at Astranis Space Technologies.}

% Detail how Adem's skills and experiences align with the job requirements
\lettercontent{With a keen curiosity in understanding consumer behaviors and a passion for leveraging technology to drive innovative solutions, I am well-equipped to contribute fresh insights and collaborate with internal teams on analytics and strategy projects. My experience as the Founder and President of the "AI Club" showcases my leadership skills and ability to foster a collaborative environment for tackling high-level projects, aligning with the teamwork required at Astranis.}

\lettercontent{Moreover, my proficiency in Microsoft Office programs, particularly Excel and PowerPoint, will enable me to create and present well-organized reports and presentations, essential for communicating data-driven recommendations effectively. I am excited about the opportunity to immerse myself in the latest trends in Experiential Marketing and contribute meaningfully to agency newsletters, aligning with my continuous learning ethos.}

% Conclusion and signature
\lettercontent{I am optimistic about the prospect of joining Astranis Space Technologies, a global leader in the communications industry, and contributing to your mission of delivering creative and impactful solutions. I am confident that my blend of technical expertise, problem-solving abilities, and passion for innovation make me a strong fit for the Strategy & Analytics Intern role.}

\signature{Adem Mcharek}

\end{document}