\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Visa}
\companyaddress{
Foster City, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Software Engineer Intern position at Visa. With a Bachelor's degree in Artificial Intelligence from Long Island University and a strong foundation in machine learning, deep learning, and software engineering, I am excited about the opportunity to contribute to Visa's mission of connecting more people to the global economy through innovative technology solutions.}

\lettercontent{During my academic journey, I have undertaken diverse projects that demonstrate my proficiency in leveraging AI technologies for real-world applications. For instance, I orchestrated an AI Research Assistant incorporating multi-agent systems for academic literature retrieval and developed a Convolutional Neural Network in PyTorch for image classification. These experiences have honed my problem-solving skills and ability to translate complex concepts into practical solutions.}

\lettercontent{I am particularly drawn to Visa's commitment to technological innovation and collaboration. The responsibilities outlined for the Software Engineer Intern align perfectly with my skills and aspirations. I am eager to contribute to analyzing, designing, and testing software solutions that drive global transactions, as well as developing robust applications for mobile banking.}

\lettercontent{I am confident that my background in AI, coupled with my leadership experience as the Founder and President of the AI Club at LIU Brooklyn, positions me well to thrive in Visa's dynamic and innovative environment. I am excited about the prospect of working on impactful initiatives at Visa and contributing to its continued success.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am looking forward to the opportunity to discuss how I can contribute to Visa's pioneering projects.}

\signature{Adem Mcharek}

\end{document}