\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Truveta}
\companyaddress{
Greater Seattle Area
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Undergraduate Engineering Internship position at Truveta. Currently pursuing a Bachelor's degree in Artificial Intelligence at Long Island University, with a strong foundation in machine learning, deep learning, and software engineering, I am excited about the opportunity to apply my technical skills in a real-world health solutions-oriented environment like Truveta.}

\lettercontent{With experiences such as orchestrating an AI Research Assistant and developing Convolutional Neural Networks for image classification, I have honed my abilities in data analytics and machine learning, aligning well with Truveta’s mission to enable researchers to find cures faster and empower clinicians with data-driven insights. My collaborative projects, including computer vision applications, have equipped me to tackle complex challenges effectively.}

% Matching qualifications
\lettercontent{I meet the specified requirements for the role, being proficient in programming languages like Python and Java, with a demonstrated skill in time management and completing projects in a collaborative environment. My background in AI research and hands-on projects reflects my ability to contribute meaningfully to Truveta's innovative initiatives.}

% Conclusion and signature
\lettercontent{Truveta's commitment to innovation and impactful solutions resonates with my aspirations, and I am eager to bring my technical expertise to your dynamic team. I am enthusiastic about the opportunity to contribute to Truveta's mission of revolutionizing healthcare through data-driven solutions.}

\signature{Adem Mcharek}

\end{document}