\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Weiss Asset Management}
\companyaddress{
Boston, Massachusetts
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{With a keen enthusiasm for quantitative analysis and a passion for understanding complex markets, I am excited to apply for the Summer Investment Analyst position at Weiss Asset Management. As a current \textbf{sophomore} at [University Name], I am dedicated to continuously learning and improving, traits that I believe align perfectly with the ethos of Weiss Asset Management.}

\lettercontent{My experience in \textbf{quantitative analysis} and \textbf{research skills} positions me well to contribute effectively to all stages of the investment process at Weiss Asset Management. I am particularly drawn to the collaborative culture fostered at the firm, where voicing dissenting opinions is encouraged and valued.}

\lettercontent{I am driven by ethical decision-making and thrive in flat structures where talent and work ethic are paramount. I am excited about the opportunity to work directly with your investment team, contribute to research and strategy development, and engage in event participation to deepen my understanding of the industry.}

% Conclusion and signature
\lettercontent{Weiss Asset Management's commitment to integrity, continuous learning, and professional development resonates strongly with my own values and aspirations. I am eager to bring my skills and enthusiasm to your esteemed firm and contribute to its culture of excellence.}

\lettercontent{Thank you for considering my application. I look forward to the possibility of contributing to the success of Weiss Asset Management as a Summer Investment Analyst.}

\signature{Adem Mcharek}

\end{document}