\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Bose}
\companyaddress{
Framingham, Massachusetts
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the mobile application development position at Bose, as advertised. With a degree in engineering and a solid background in mobile app design and development, particularly in Swift and Kotlin coding, I am excited about the opportunity to contribute to Bose's innovative projects that integrate with cloud and hardware systems.}

\lettercontent{During my tenure, I have acquired essential skills in Swift Concurrency and MVVM architecture, aligning well with the technologies commonly used in mobile app development at Bose. Moreover, my experience in collaborating with cross-functional teams and my strong foundation in object-oriented design and data structures make me well-equipped to excel in this role.}

\lettercontent{What particularly draws me to Bose is its commitment to disruptive innovation and the opportunity to work on exciting projects using cutting-edge technologies. I am motivated by the prospect of further advancing my skills in Kotlin and Swift while contributing to a culture based on learning and collaboration.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am eager to bring my expertise in mobile app development to the talented team at Bose and to contribute to the company's mission of creating better solutions for its customers.}

\signature{Adem Mcharek}

\end{document}