\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Affinitiv}
\companyaddress{
Deer Park, Illinois
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Software Engineering Intern position at Affinitiv as advertised. With a strong academic background and hands-on experience in C#, Java, SQL, and version control systems, I am excited about the opportunity to contribute to your team and gain valuable insights into the automotive customer lifecycle.}

\lettercontent{During my studies, I have maintained a GPA above 3.0, showcasing my commitment to academic excellence. Additionally, my practical experience with Python and MySQL, coupled with my proficiency in Angular/JavaScript frameworks, aligns well with the technical skills you are seeking in a candidate.}

\lettercontent{I am particularly drawn to Affinitiv's dedication to driving the next-generation customer experience and its focus on innovation in software solutions for the automotive industry. The emphasis on end-to-end project completion, collaboration within the Essentials team, and exposure to cutting-edge technologies resonates with my career aspirations in software development.}

% Conclusion and signature
\lettercontent{I am eager to leverage my skills in software engineering, attention to detail, and passion for problem-solving to contribute to Affinitiv's mission of inspiring loyalty and retailer performance. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}