\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Astranis Space Technologies}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Software Developer Intern position at Astranis Space Technologies as advertised. Currently pursuing a full-time degree in Software Engineering, I am excited about the opportunity to contribute to the design, development, and evolution of innovative space systems at Astranis.}

\lettercontent{With a solid background in Software Engineering and hands-on experience in projects involving Java and Object-Oriented Programming, I am well-equipped to fulfill the responsibilities of designing, documenting, implementing, and unit testing server components at your esteemed organization. My knowledge of scripting languages like Perl and Python, coupled with my familiarity with Linux and Windows platforms, further reinforces my capability to ensure that products meet quality standards.}

\lettercontent{Moreover, my previous projects have honed my software troubleshooting skills, and I am eager to apply this expertise in a challenging and dynamic environment like Astranis. Additionally, my excellent communication skills, both oral and written, position me well to collaborate effectively with the talented teams at Astranis Space Technologies.}

% Conclusion and signature
\lettercontent{I am particularly excited about the opportunity to work on cutting-edge space technologies and contribute to the advancement of the aerospace industry. I am confident that my technical skills, enthusiasm for innovation, and commitment to excellence make me a suitable candidate for this role. I am looking forward to the possibility of discussing how my background aligns with the vision and goals of Astranis Space Technologies.}

\signature{Adem Mcharek}

\end{document}