\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Zoox}
\companyaddress{
Foster City, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am delighted to express my enthusiasm for the opportunity to join Zoox's HD Mapping team, where cutting-edge technology and innovative solutions meet the future of personal transportation. With a solid foundation in Applied Mathematics from Sorbonne University and valuable experiences in optimizing algorithms and modeling, including projects such as electric scooter infrastructure optimization, I am eager to apply my skills to the critical work of predicting HD map elements and visual feature representations at Zoox.}

\lettercontent{My proficiency in Python, reinforced by a strong math background, aligns well with the technical qualifications required for the role. Moreover, my exposure to modern ML frameworks like PyTorch and experience in areas such as multiview geometry and 3D reconstruction complement the skill set sought by Zoox. I am particularly excited about the prospect of collaborating on algorithms to enhance HD map perception for autonomous vehicles, a field where precision and innovation are paramount.}

\lettercontent{Zoox's commitment to revolutionizing personal transportation through autonomous vehicles resonates with my aspiration to contribute to groundbreaking technological advancements. The opportunity to work on HD map elements, including traffic lights, signs, lanes, and 3D representations, presents a challenging yet rewarding environment that I am eager to be a part of.}

% Conclusion and signature
\lettercontent{I look forward to the possibility of contributing my skills and passion to Zoox's mission of transforming urban mobility. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}