\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Okta}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the opportunity to join Okta as a Digital Success intern. With a Bachelor's degree in Artificial Intelligence from Long Island University and a solid foundation in relevant coursework including Machine Learning, Deep Learning, and Data Mining, I am excited about the prospect of merging my technical expertise with cutting-edge digital strategies at Okta.}

\lettercontent{My academic journey, marked by a Cumulative GPA of 3.88/4.00, has equipped me with the analytical acumen and data-driven mindset essential for executing small iterative improvements and maintaining program quality, as outlined in the responsibilities for the role at Okta. Furthermore, my experience in software engineering and cloud computing aligns well with the expectations of identifying areas for personalization within the in-app experience.}

% Conclusion and signature
\lettercontent{The dynamic environment at Okta, known for its commitment to innovation and fostering a collaborative atmosphere, resonates with my aspirations and skills. I am particularly drawn to the opportunity to contribute to onboarding and adoption efforts, translating the Okta customer experience into actionable recommendations to maximize success and customer value.}

\lettercontent{I am enthusiastic about the chance to leverage my technical background and genuine interest in identity security to create impactful solutions at Okta. I am confident that my combination of academic excellence, technical skills, and passion for digital strategies make me a valuable candidate for the Digital Success intern position.}

\signature{Adem Mcharek}

\end{document}