Based on the information provided in the uploaded files, I will create a LaTeX document that includes the company overview, requirements, responsibilities, desired qualifications, and details about the software engineering internship position at Acorns. I will organize the information neatly and professionally in a LaTeX format for the position of Software Engineering Intern at Acorns.

Let's start by extracting the key details and transforming them into a structured LaTeX document.I have gathered information from the cover letters and resumes provided by the user for different companies. Now, I will proceed to organize the details into a LaTeX document for the position of Software Engineering Intern at Acorns. Let's start by preparing the LaTeX code.\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, left=25mm, right=25mm, top=25mm, bottom=25mm}
\usepackage{xcolor}

\title{Application for Software Engineering Intern at Acorns}
\author{}
\date{}

\begin{document}

\maketitle

Dear Hiring Team,

I am writing to express my interest in the Software Engineering Intern position at Acorns. With a strong background in technology and a passion for innovation, I am excited about the opportunity to contribute to your mission of empowering individuals through micro-investing.

\section*{Company Overview}
Acorn's mission is to look after the financial best interests of the up-and-coming, beginning with the empowering step of micro-investing. The company, headquartered in Irvine, California, was founded in 2012 and has reached Series F stage with a total funding of $686 million.

\section*{Requirements}
The position requires proficiency in at least one programming language such as TypeScript, Kotlin, Python, Java, or Scala. It also necessitates an understanding of data structures, algorithms, and software design principles, along with the ability to learn and adapt to new technologies. Experience with version control systems like Git is a plus, as well as a passion for artificial intelligence, problem-solving skills, and excellent communication abilities.

\section*{Responsibilities}
As a Software Engineering Intern at Acorns, you will familiarize yourself with the company's technologies and development processes, contribute to AI-powered projects, demonstrate proficiency in programming languages, identify areas for improvement in AI tools, attend team meetings, and more. Moreover, you will deepen your understanding of AI concepts, make significant contributions to AI tools, independently tackle challenging tasks, present in engineering meetings, and participate in social and team-building activities.

\section*{Desired Qualifications}
Experience with version control systems like Git is highlighted as a desired qualification for the role.

\section*{Career Interests and Achievements}
Having pursued diverse opportunities, I have garnered valuable experience in AI research, programming projects using PyTorch and TensorFlow, and leadership roles such as founding and presiding over an AI Club. Additionally, I have a Bachelor's degree in Artificial Intelligence with a GPA of 3.88/4.00 from Long Island University.

Thank you for considering my application. I am eager to contribute to Acorns and grow both professionally and personally within your innovative team.

Warm regards,\\
[Your Name]

\end{document}