\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Acorns}
\companyaddress{
Irvine, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Software Engineering Intern position at Acorns, a company dedicated to looking after the financial best interests of individuals through micro-investing. As a dedicated Artificial Intelligence student at Long Island University, with a strong foundation in machine learning, deep learning, and software engineering, I am excited about the opportunity to contribute to Acorns and harness the power of artificial intelligence to address real-world challenges.}

% Matching qualifications and skills
\lettercontent{During my academic journey, I have undertaken various projects, such as developing an AI Research Assistant using AUTOGEN's multi-agent system and implementing a Convolutional Neural Network in PyTorch for image classification. These experiences have equipped me with proficiency in programming languages like Python, in-depth knowledge of data structures, and a strong understanding of algorithms and software design principles. My ability to quickly grasp new technologies, evidenced by my projects in AI and computer vision, aligns with the requirement to adapt to new tools efficiently at Acorns.}

% Relating to company values and responsibilities
\lettercontent{I am particularly drawn to Acorns' values of making bold decisions, continuous growth, and finding ways to overcome challenges. The responsibility to contribute effectively to ongoing AI-powered projects, propose innovative solutions, and present insights aligns with my proactive problem-solving skills and eagerness to learn and grow both professionally and personally. I am excited about the prospect of joining a motivated, mission-driven team at Acorns and participating in community-wide events to foster a deeper connection to the company's culture.}

% Closing and signature
\signature{Adem Mcharek}

\end{document}