Based on the information provided about the company Identifeye Health and the details extracted from Adem Mcharek's resume, I will now generate a customized cover letter in LaTeX format tailored to his qualifications and the internship position at Identifeye Health.

Here is the LaTeX code for the personalized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Identifeye Health}
\companyaddress{
Guilford, Connecticut
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Internship Program at Identifeye Health, a groundbreaking company revolutionizing non-invasive diagnostics through retinal health monitoring. As a dedicated Bachelor's student in Artificial Intelligence and an AI Research Assistant with a solid foundation in deep learning and software engineering, I am excited about the opportunity to contribute to Identifeye Health's mission of democratizing healthcare and personalized health insights through technology.}

% Relevant experiences and skills
\lettercontent{My hands-on experience includes developing AI-driven solutions such as an AI Research Navigator and implementing Convolutional Neural Networks for image classification. These projects, along with my leadership roles in AI clubs and achievements in mathematical olympiads, have honed my analytical skills and technical proficiency, aligning well with the responsibilities outlined for the internship. I am eager to apply my expertise in software development, data structures, and algorithms to implement new features, conduct code reviews, and evaluate software solutions at Identifeye Health.}

% Closing and aspirations
\lettercontent{Identifeye Health's commitment to technological innovation and patient-centered care resonates with my values of leveraging AI for real-world impact and empowering individuals through accessible healthcare solutions. I am excited about the opportunity to join a team that shares my passion for leveraging cutting-edge technology to improve healthcare outcomes. I am looking forward to the possibility of contributing meaningfully to Identifeye Health's innovative projects and being part of a culture that fosters technical excellence and impactful solutions.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter is crafted to reflect Adem Mcharek's experiences, skills, and ambitions, highlighting how they align with Identifeye Health's vision and the requirements of the internship program. Adem Mcharek's AI research experience, technical skills, and commitment to leveraging technology for positive impact are emphasized throughout the letter to showcase his suitability for the internship position at Identifeye Health.