To create a tailored cover letter for Adem Mcharek applying for the Internship position at Moloco, we will incorporate his qualifications and experiences to match the company's requirements and responsibilities. Below is the LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Moloco}
\companyaddress{
Redwood City, CA
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Internship position at Moloco as advertised. With a strong educational background in Computer Science and a passion for machine learning technologies, I am excited about the opportunity to contribute to Moloco's mission of empowering organizations through operational machine learning.}

\lettercontent{During my academic pursuits and practical experiences, I have developed a solid foundation in data structures, algorithms, and coding. My exposure to distributed systems and databases, along with my proficiency in languages like C++, Java, and Go, align well with the requirements outlined by Moloco.}

\lettercontent{I am particularly thrilled about the prospect of joining Moloco in building a next-generation ML based ad-serving platform. My experience in machine learning technologies, coupled with a keen interest in performance marketing, positions me well to enhance the system's scalability, performance, and efficiency as part of your team.}

% Conclusion and signature
\lettercontent{Moloco's commitment to creating a diverse workforce and fostering a culture of inclusion resonates with me, and I am eager to contribute to the innovative work being done at your company. I am excited about the opportunity to work alongside talented professionals at Moloco and contribute meaningfully to the team.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter integrates Adem Mcharek's relevant skills in Computer Science, machine learning, and coding with Moloco's requirements and responsibilities for the Internship position, showcasing his enthusiasm and alignment with the company's mission and values.