Based on the information provided, I will now proceed to craft a tailored cover letter for Adem Mcharek applying for a position at Exodus Point Capital. I will integrate relevant details from his resume and the job requirements specified for the position. Let's proceed with the customization. 

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Exodus Point Capital}
\companyaddress{
New York, New York
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the position at Exodus Point Capital. As a dedicated student with a Bachelor's in Artificial Intelligence and a solid foundation in Applied Mathematics, Data Science, and Machine Learning, I am excited about the opportunity to merge my technical expertise with the intricacies of the financial world at Exodus Point Capital.}

\lettercontent{Throughout my academic journey, I have undertaken various projects that involved intricate mathematical concepts and real-world applications, such as developing AI systems for academic literature retrieval and implementing Convolutional Neural Networks for image classification. These experiences have honed my ability to generate insights from diverse datasets and translate complex ideas into practical solutions.}

\lettercontent{The requirements outlined for the position perfectly align with my skill set, including proficiency in AWS/big data services, experience in data engineering, and a strong understanding of AI/ML products. My problem-solving skills, combined with my goal-oriented and industrial approach, make me well-equipped to contribute effectively to the analytics and data-driven projects at Exodus Point Capital.}

\lettercontent{I am particularly drawn to Exodus Point Capital's multi-strategy investment approach and its focus on innovative research within a robust risk framework. I am eager to collaborate with the team, help develop alternative uses of market data, and maintain organized databases to drive informed investment strategies.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This LaTeX code creates a tailored cover letter for Adem Mcharek, expressing his interest in the position at Exodus Point Capital. It integrates his academic background, project experiences, and skills relevant to the job requirements specified by Exodus Point Capital.