Based on the information provided from Adem Mcharek's resume and the job description for the internship at Cadence Design Systems, we can now draft a tailored cover letter for Adem to apply for the position. Below is the customized LaTeX code for Adem Mcharek's cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Cadence Design Systems}
\companyaddress{
San Jose, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my keen interest in the internship opportunity at Cadence Design Systems, as advertised. Currently pursuing a B.S. in an engineering discipline, with a strong grounding in programming skills, particularly in C++, and a deep familiarity with object-oriented programming methods, I am excited about the prospect of merging my technical proficiency with the intricate dynamics of thermal optimization, especially using machine learning algorithms.}

\lettercontent{Through my academic journey and various projects, such as optimizing algorithms and modeling for specific infrastructures, I have honed my ability to translate complex mathematical concepts into practical solutions. The internship at Cadence Design Systems focusing on developing P C B/package/chip thermal analysis software aligns perfectly with my skills and aspirations.}

% Match skills and requirements
\lettercontent{I bring prior knowledge and experience in distributed/multi-threaded programming, numerical analysis techniques, and a deep understanding of electric cooling systems, including CFD analysis. Moreover, my exposure to finite-element-based thermal simulation and meshing techniques further enhances my suitability for the role.}

% Conclusion and signature
\lettercontent{I am enthusiastic about the opportunity to work on extremely complex problems, exercising independent judgment, and providing work leadership as needed. My experience in automatic design optimization for thermal targets adds value to my potential contribution to Cadence Design Systems. I am eager to contribute to the innovative projects at Cadence and look forward to the possibility of discussing how I could be a valuable asset to your team.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter is personalized for Adem Mcharek, aligning his skills, experiences, and aspirations with the internship position at Cadence Design Systems. Adem's qualifications related to programming, numerical analysis, and thermal simulation are highlighted to demonstrate his suitability for the role.