To create a tailored cover letter for Adem Mcharek applying to a position at Gen, I will integrate details from his resume to address the company's requirements and responsibilities. The cover letter will highlight Adem's experiences, skills, and aspirations in relation to the job opportunity at Gen.

Here is the LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Gen}
\companyaddress{
Tempe, Arizona
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the position at Gen as advertised, combining my educational background in Computer Science with hands-on experience that aligns with the requirements outlined for the role.}

\lettercontent{Having pursued my degree in Computer Science and gained proficiency in installing and working with Linux, along with scripting skills in languages such as Java, Ruby, Python, and Scala, I am confident in my ability to contribute effectively to the team at Gen. My experience with cloud platforms like AWS, coupled with a solid understanding of DevOps practices and SDLC, positions me well to navigate the responsibilities associated with the role.}

\lettercontent{Moreover, I am eager to leverage my skills in system administration, configuration management, and automation using tools like Puppet and Terraform to ensure the high availability, security, and performance of both customer-facing and internal applications at Gen. I am excited about the prospect of collaborating with the Engineering and Tech Ops teams to optimize and automate operational processes while troubleshooting and resolving issues across environments.}

% Conclusion and signature
\lettercontent{With a passion for problem-solving and automation, I am enthusiastic about the opportunity to contribute to Gen's mission of empowering Digital Freedom through cutting-edge cybersecurity solutions. I look forward to the possibility of discussing how my background, skills, and enthusiasm can contribute to the success of your team.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to Adem Mcharek's qualifications and experiences, aligning them with the specific requirements and responsibilities outlined by Gen in the provided company overview. This should present a compelling application for the position at Gen.