To tailor the cover letter for Adem Mcharek applying for the Point72 Academy Summer Internship, we will incorporate his skills and experiences to align with the company's requirements and expectations. Below is the customized LaTeX cover letter based on Adem Mcharek's profile and the information provided about the internship:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Point72 Asset Management}
\companyaddress{
Stamford, Connecticut
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Point72 Academy Summer Internship, as advertised. With a passion for the financial services industry along with a strong background in finance and computer science, I am excited about the opportunity to contribute to the innovative environment at Point72 Asset Management. The firm's commitment to developing talent and leveraging data-driven decision-making perfectly aligns with my professional aspirations.}

\lettercontent{Having honed my analytical skills through relevant coursework and practical projects, I am well-equipped to meet the demands of the internship. My experience in research and problem-solving, combined with my dedication to maintaining the highest ethical standards, prepares me to thrive in the dynamic and challenging environment at Point72.}

\lettercontent{Moreover, my keen interest in financial markets, supported by a strong foundation in accounting and modeling, positions me well to acquire the fundamental knowledge necessary to succeed as an analyst. I am particularly excited about the opportunity to collaborate with the investment team, develop my presentation skills, and work closely with Academy coaches to enhance my data analysis capabilities.}

% Conclusion and signature
\lettercontent{In conclusion, I am eager to bring my self-motivation, professionalism, and intellectual curiosity to the Point72 Academy Summer Internship. I am confident that my educational background and skills make me a strong candidate for this program, and I am looking forward to the possibility of contributing to the esteemed team at Point72.}

\lettercontent{Thank you for considering my application. I am excited about the prospect of launching my investing career with Point72 and contributing to the firm's continued success.}

\signature{Adem Mcharek}

\end{document}
```

This tailored cover letter aligns Adem Mcharek's experiences and skills with the requirements and expectations of the Point72 Academy Summer Internship, showcasing his enthusiasm for the financial industry and readiness to excel in the dynamic environment offered by Point72 Asset Management.