Based on the provided information about the job opportunity at NVIDIA for a Hardware Engineering internship and Adem Mcharek's resume, I will tailor a cover letter for Adem Mcharek addressing NVIDIA's requirements and responsibilities. The cover letter will be structured to highlight Adem Mcharek's qualifications and experiences that align with NVIDIA's desired qualifications and responsibilities for the Hardware Engineering internship role. Below is the LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{NVIDIA Corporation}
\companyaddress{
Santa Clara, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Hardware Engineering internship position at NVIDIA, as advertised. With a strong background in mechanical engineering and a passion for working with multi-disciplinary teams, I am excited about the opportunity to contribute to NVIDIA's innovative projects.}

\lettercontent{Having pursued a Bachelor's degree in Mechanical Engineering, I have gained practical experience in system validation, hardware testing, and validation of new products – skills that directly align with the responsibilities outlined for the internship. My proficiency in programming languages such as Python and expertise in C A D software make me well-equipped to engage in the development of next-generation products at NVIDIA.}

\lettercontent{I am particularly drawn to the collaborative environment at NVIDIA, where I believe I can leverage my academic background and interpersonal skills to excel in system validation, hardware design, and researching new materials to enhance product performance.}

% Conclusion and signature
\lettercontent{I am enthusiastic about the opportunity to contribute to NVIDIA's culture of innovation and excellence. Thank you for considering my application. I look forward to the possibility of discussing how my skills and experiences can benefit NVIDIA's Hardware Engineering team.}

\signature{Adem Mcharek}

\end{document}
```

This LaTeX code generates a personalized cover letter for Adem Mcharek tailored to the Hardware Engineering internship position at NVIDIA. Feel free to make any further adjustments if needed.