Based on the detailed information provided about the job opportunity at My Fitness Pal and Adem Mcharek's resume, I will now proceed to generate a tailored cover letter for Adem Mcharek to apply for the Business Intelligence Analyst Intern position at My Fitness Pal. I will incorporate Adem's experiences, skills, and aspirations relevant to the job requirements and responsibilities specified by My Fitness Pal.

Let's start with the tailored cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{My Fitness Pal}
\companyaddress{
Austin, Texas
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Business Intelligence Analyst Intern position at My Fitness Pal, as advertised. As a current full-time college student with a strong passion for analysis and utilizing data to drive business decisions, coupled with my experience in S Q L and B I tools such as Tableau, I am excited about the opportunity to contribute to the growth and analysis of core marketing metrics at My Fitness Pal.}

% Customized content based on Adem's experiences and skills
\lettercontent{During my academic journey, I have actively pursued projects that involved utilizing data to derive meaningful insights. My experience with S Q L and B I tools, including Tableau, has equipped me with the necessary technical skills to produce dynamic visualizations and analyze consumer behavior effectively. I am particularly drawn to the dynamic environment at My Fitness Pal, where innovation and data-driven decision-making are crucial for success.}

% Aligning Adem's qualifications with the job requirements
\lettercontent{My curiosity-driven mindset aligns perfectly with the culture at My Fitness Pal, where seeking the truth through data is valued. I am eager to collaborate with the experienced analysts and engineers at My Fitness Pal to drive actionable insights and contribute to the strategic growth of the company. Moreover, as a self-motivated individual comfortable in a remote working environment, I am confident in my ability to thrive in a fast-paced setting while delivering exceptional results.}

% Conclusion and signature
\lettercontent{I am genuinely excited about the prospect of working with the Business Intelligence Team at My Fitness Pal and am eager to immerse myself in the vibrant culture and impactful projects at your company. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter for Adem Mcharek is tailored to emphasize his experiences, skills in S Q L and B I tools, and his passion for analysis and utilizing data to drive business decisions, all of which are aligned with the requirements of the Business Intelligence Analyst Intern position at My Fitness Pal.