Based on the provided information regarding the job opportunity at Cadence Design Systems, particularly the responsibilities, requirements, and desired qualifications for the position, I will now tailor a cover letter for Adem Mcharek to apply for this role at Cadence Design Systems.

Here is the customized cover letter in LaTeX format:

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Cadence Design Systems}
\companyaddress{
San Jose, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{To the Hiring Manager,}

\lettercontent{I am writing to express my interest in the Electrical or Computer Engineering Intern position at Cadence Design Systems, as advertised. With a strong academic background and practical experience in software development, I believe that my skills and passion for learning make me a suitable candidate for this role.}

% Key experiences and skills
\lettercontent{Having completed coursework in Computer Science at [University Name], I have acquired a solid foundation in programming languages such as C and C++. Additionally, my familiarity with Qt, Visual Studio, and Perforce aligns well with the desired qualifications for the position.}

\lettercontent{During my previous projects, I have demonstrated excellent verbal and written communication skills, coupled with a keen eye for detail, as I actively contributed to shaping geometric algorithms and evaluating polygon shapes, tasks that are central to the responsibilities outlined for this internship.}

% Closing paragraph
\lettercontent{I am excited about the opportunity to work on critical geometric algorithms within the Allegro PCB design tool at Cadence Design Systems. The chance to contribute to innovative solutions and collaborate with a team of industry experts greatly appeals to me.}

\lettercontent{Thank you for considering my application. I am eager to bring my technical skills and enthusiasm for problem-solving to Cadence Design Systems.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}

This cover letter combines Adem Mcharek's qualifications and experiences, emphasizing his relevance to the role at Cadence Design Systems. Feel free to adjust the content further to better reflect Adem Mcharek's personal experiences or aspirations if needed.