Based on the information provided in Adem Mcharek's resume and the details about the company Guidewire, I will now customize a cover letter for Adem Mcharek applying for the Summer Internship Program at Guidewire. 

Here is the tailored cover letter in LaTeX format:

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Guidewire}
\companyaddress{
San Mateo, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the opportunity to join Guidewire's Summer Internship Program. Currently pursuing a Bachelor's degree in Artificial Intelligence at Long Island University Brooklyn, with a strong foundation in machine learning, deep learning, and cloud computing, I am excited about the prospect of contributing to Guidewire's innovative projects in data-backed insurance solutions. My academic journey, including projects such as building AI research assistants and implementing computer vision systems, has equipped me with the skills in algorithms, object-oriented design, and software engineering, aligning well with the requirements for the internship at Guidewire.}

\lettercontent{Guidewire's commitment to technological innovation and collaborative work environment resonates with my values and aspirations as a budding AI professional. The opportunity to work on real-world software projects, collaborate with mentors and stakeholders, and learn the ropes of being a professional software engineer is something I eagerly anticipate. I am particularly keen on leveraging my experience with Java, Python, and cloud-native infrastructures to contribute meaningfully to Guidewire's mission.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}

This cover letter integrates Adem Mcharek's academic background, project experiences, and technical skills with the requirements and company overview of Guidewire, highlighting his alignment with the company's goals and the specific internship program.