Based on the information provided and the details extracted from Adem Mcharek's resume, below is a tailored cover letter for the Security/App Dev Intern position at Hewlett Packard (HP).

The cover letter integrates Adem Mcharek's key experiences, skills, and aspirations relevant to the internship position at HP.

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Hewlett Packard (HP)}
\companyaddress{
Palo Alto, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Security/App Dev Intern position at Hewlett Packard, a company renowned for its commitment to technological innovation and humanitarian efforts. My academic journey at Long Island University, specializing in Artificial Intelligence, and my hands-on experiences have equipped me with a versatile skill set ideal for the role.}

\lettercontent{As an AI Research Assistant, I orchestrated projects utilizing advanced technologies like AI-enabled Research Navigator and PyTorch CNN for MNIST, showcasing my proficiency in AI and deep learning. Moreover, my work on Computer Vision projects using TensorFlow for real-time applications in agriculture and retail highlights my practical skills in technology implementation.}

\lettercontent{Securing medals in prestigious mathematical competitions and founding the “AI Club” demonstrate my dedication to innovation and collaborative learning. My experiences have honed my analytical acumen, translating complex concepts into actionable solutions effectively.}

\lettercontent{With a solid foundation in AI, programming languages like C#, Java Script, and frameworks such as MVC and Entity Framework, I am well-equipped to contribute to security applications development using .NET and Azure services at Hewlett Packard. My familiarity with SQL databases and Bootstrap aligns with the responsibilities of the role, ensuring a seamless integration into your team.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter leverages Adem Mcharek's academic achievements, practical experiences, and technical skills to demonstrate a strong fit for the Security/App Dev Intern position at Hewlett Packard. It is tailored to align with HP's mission and requirements while highlighting Adem's qualifications effectively.