Based on the information extracted from Adem Mcharek's resume and the job details provided for the Data Engineering Summer Internship at HP Inc., I will now proceed to draft a tailored cover letter in LaTeX format to fit the internship opportunity with HP Inc. for Adem Mcharek. 

Please find below the LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{HP Inc.}
\companyaddress{
Palo Alto, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Data Engineering Summer Internship at HP Inc., a renowned global technology company committed to innovation, client service, and industry expertise. Currently pursuing my education with a solid foundation in Computer Science and Data Science, I am excited about the opportunity to apply my skills and knowledge in a practical setting at HP Inc.}

\lettercontent{Drawing from my educational background and experiences in projects like optimizing algorithms and modeling for real-world applications, I have honed my ability to leverage analytical tools and translate complex concepts into actionable solutions. The dynamic environment at HP Inc., which values technological innovation and collaboration, aligns perfectly with my career aspirations and skill set.}

% Personalized content related to the internship requirements
\lettercontent{With a working knowledge of data visualization tools like Power BI and strong SQL coding skills, complemented by experience in Python and advanced modeling techniques, I am well-equipped to contribute effectively to the innovative projects at HP Inc. Additionally, my strong communication, collaboration skills, and self-driven nature make me a proactive learner ready to tackle challenges.}

% Conclusion
\lettercontent{I am eager at the prospect of applying my skills and knowledge to the cutting-edge projects in data engineering at HP Inc. I am confident that my background and enthusiasm for technology make me a suitable candidate for the internship opportunity. Thank you for considering my application.}

% Signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored for Adem Mcharek based on his qualifications, experiences, and the requirements of the Data Engineering Summer Internship at HP Inc. It highlights his skills, enthusiasm, and alignment with HP Inc.'s goals and values, making it a strong application for the internship opportunity.