Based on the information provided about Adem Mcharek and the job opportunity at The Boring Company, I will now proceed to draft a personalized cover letter in LaTeX format tailored to Adem Mcharek's qualifications and experiences.

Here is the LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{The Boring Company}
\companyaddress{
Bastrop, Texas
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Software Engineering Intern position at The Boring Company, as advertised. With a Bachelor's degree in Artificial Intelligence from Long Island University and a strong foundation in software development and AI technologies, I am excited about the opportunity to contribute to the development of automation and application software for the next generation of tunnel boring machines (TBMs) at The Boring Company.}

% Matching skills and experiences
\lettercontent{My experience as an AI Research Assistant, where I orchestrated AI solutions using multi-agent systems for real-time applications and developed Convolutional Neural Networks (CNNs) for image classification, aligns well with the requirement for developing software applications in Python and other high-level languages at The Boring Company. Additionally, my proficiency in Python, TensorFlow, and database management, along with a keen interest in machine learning and data visualization, make me well-equipped to support the software engineering and controls team in writing code for tunnel boring machines and designing data pipelines.}

% Closing and signature
\lettercontent{I am particularly drawn to The Boring Company's commitment to technological innovation and its mission to revolutionize transportation through underground tunnels. I am excited about the prospect of contributing my skills and knowledge to a dynamic and cutting-edge environment such as The Boring Company. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}
```

This LaTeX code creates a tailored cover letter for Adem Mcharek applying for the Software Engineering Intern position at The Boring Company. It highlights his educational background, relevant experiences, and skills that align with the job requirements and the company's mission. Feel free to adjust the content further if needed.