Based on the information provided in Adem Mcharek's resume and the job description for the position at Plus, I will now draft a tailored cover letter in LaTeX format.

Here is the customized LaTeX cover letter for Adem Mcharek:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Plus}
\companyaddress{
Silicon Valley, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the position at Plus, a global provider of highly automated driving and fully autonomous driving solutions, known for its transformative technology and commitment to making transportation safer and greener. With my Bachelor's degree in Artificial Intelligence from Long Island University Brooklyn and a solid foundation in machine learning, deep learning, and computer vision, I am excited about the opportunity to contribute to the innovative work at Plus.}

\lettercontent{During my academic journey, I have undertaken various projects incorporating AI technologies, such as developing a Convolutional Neural Network in PyTorch for image classification and creating a hand gesture recognition system using TensorFlow. These experiences have equipped me with a deep understanding of key elements of the autonomous driving perception stack, aligning well with the requirements of the role at Plus.}

\lettercontent{I am particularly drawn to Plus's dedication to technological innovation and collaborative partnerships with industry leaders, as evidenced by its recognition by Forbes and Fast Company. The chance to enhance and optimize camera drivers for automotive SoCs, as well as to leverage vision accelerators and DSPs, excites me to contribute to the future of autonomous driving at Plus.}

\lettercontent{Enclosed is my resume, providing a comprehensive overview of my experiences and skills. I am eager to discuss how my background and passion for AI can align with Plus's mission and contribute to its continued success. Thank you for considering my application.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to showcase Adem Mcharek's relevant experiences and skills, aligning them with the requirements and aspirations of the position at Plus.