Based on the information provided in Adem Mcharek's resume and the job description for the Software Engineer Intern position at Chime, we can now proceed to create a tailored cover letter for Adem Mcharek.

Let's integrate the relevant details into the cover letter format provided:

### Cover Letter for Adem Mcharek

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Chime}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my genuine interest in the Software Engineer Intern position at Chime, as advertised. Currently pursuing a Bachelor's degree in Artificial Intelligence with a notable GPA of 3.88/4.00 at Long Island University Brooklyn, I am excited about the opportunity to contribute to Chime's mission of making financial peace of mind a reality for everyone.}

\lettercontent{With a strong foundation in Artificial Intelligence and a passion for technology and innovation, I am well-equipped to work on projects that directly impact Chime members and the business. My academic background, including relevant courses in AI and machine learning, has provided me with the necessary skills to design, develop, and scale backend implementations that drive consumer product features.}

\lettercontent{Furthermore, my experiences in optimizing algorithms and modeling real-world solutions during my academic journey have honed my analytical acumen and problem-solving skills, making me well-prepared to collaborate with the engineering team at Chime from design inception to product launch.}

\lettercontent{I am particularly drawn to Chime's commitment to innovation, transparency, and fairness in financial services. The opportunity to work in fintech and contribute to building resilient APIs for consumer-facing mobile applications excites me, aligning perfectly with my career aspirations in the technology sector.}

% Conclusion and signature
\lettercontent{I am confident that my strong organizational skills, analytical mindset, and passion for consumer FinTech make me a great fit for the Software Engineer Intern position at Chime. I am eager to bring my technical expertise to your dynamic team and contribute to Chime's mission of empowering individuals through financial progress.}

\lettercontent{Thank you for considering my application. I look forward to the possibility of contributing to Chime's critical initiatives and learning from the wealth of experience within your engineering team.}

\signature{Adem Mcharek}

\end{document}

This cover letter integrates Adem Mcharek's academic background, skills, and aspirations with the job requirements and responsibilities at Chime, aligning them to showcase his suitability for the Software Engineer Intern role.