Based on the provided information from Adem Mcharek's resume and the job description for the Consulting Intern position at Blue Cottage of Cannon Design, we can tailor a cover letter for Adem Mcharek as follows:

Let's integrate Adem Mcharek's background and skills into the cover letter template for the Consulting Intern position at Blue Cottage of Cannon Design:

---

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Blue Cottage of Cannon Design}
\companyaddress{
    New York, New York
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Consulting Intern position at Blue Cottage of Cannon Design. As a rising senior in a Bachelor's degree program in Data Analytics and with a strong GPA of 3.8, I am excited about the prospect of contributing to your team.}

% Mid-Section with experiences and skills
\lettercontent{My academic journey has equipped me with the skills to perform detailed analytical models using advanced Excel functions, and I have experience with tools such as Tableau and Power BI. I have worked on various projects involving data analysis and visualization, which have honed my ability to derive meaningful insights from complex datasets.}

\lettercontent{Moreover, my experience in research, statistical modeling, and machine learning algorithms aligns well with the responsibilities outlined for the role at Blue Cottage. I am highly proficient in Excel, PowerPoint, and data visualization, and I thrive in fast-paced environments where I can manage multiple tasks independently.}

% Conclusion
\lettercontent{I am particularly drawn to Blue Cottage's commitment to Living-Centered Design and the opportunity to work with a team dedicated to innovation and creating impactful solutions. I am excited about the possibility of collaborating with your team to drive value and provide compelling analysis and data visualization.}

\lettercontent{Thank you for considering my application. I am eager to discuss how my skills and experiences can contribute to the continued success of Blue Cottage of Cannon Design.}

% Signature
\signature{Adem Mcharek}

\end{document}

---

This cover letter integrates Adem Mcharek's academic background and skills in data analytics and visualization with the specific requirements and responsibilities outlined for the Consulting Intern position at Blue Cottage of Cannon Design.