Based on the information provided from the company overview and the job description for the Artificial Intelligence Engineering Intern position at Hewlett Packard, I will now craft a customized cover letter for Adem Mcharek tailored to this opportunity. The cover letter will highlight his qualifications and experiences relevant to the role at Hewlett Packard's Inkjet Technology division. 

Here is the tailored LaTeX cover letter for Adem Mcharek:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Hewlett Packard Inc.}
\companyaddress{
Palo Alto, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Artificial Intelligence Engineering Intern position at Hewlett Packard Inc., as advertised. With a strong background in Computer Science and valuable skills in ChatGPT, Generative AI, Java, Python, and experience with AWS and Databricks, I am excited about the opportunity to contribute to your Inkjet Technology division.}

\lettercontent{During my academic journey at a four-year college, I have delved deep into AI-related projects and completed market analysis tasks similar to those outlined in the job responsibilities. My experiences have equipped me to identify key pain points in the adoption of AI in the office environment and propose practical solutions.}

\lettercontent{Moreover, my passion for innovation and my commitment to pushing the boundaries of technology align well with Hewlett Packard's vision of engineering experiences that amaze. I am eager to bring my fresh ideas and skills to your team, contributing to the development and integration of cutting-edge AI technologies into printing systems.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am enthusiastic about the opportunity to apply my knowledge and skills at Hewlett Packard Inc., and I am looking forward to the possibility of contributing to your team.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to Adem Mcharek's experiences and skills, focusing on his alignment with the job requirements and his enthusiasm for contributing to Hewlett Packard Inc.'s Inkjet Technology division.