To create a tailored cover letter for Adem Mcharek applying for a Data Engineering position at Bose, we can integrate his experiences and skills with the job requirements and company details provided. Below is the LaTeX code incorporating this information:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Bose Corporation}
\companyaddress{
Framingham, Massachusetts
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Data Engineering position at Bose Corporation, as advertised. With a strong background in data pipelines, data acquisition, ML model deployment, and proficiency in Python and SQL coding, I am excited about the opportunity to contribute to the development and enhancement of Bose Data Platforms.}

% Adapting job requirements and responsibilities
\lettercontent{My hands-on experience aligns well with the requirements outlined, including working with data pipelines, collaborating in multi-functional agile teams, and proficiency in Python, SQL, and AWS Serverless solutions. I am eager to leverage my skills to design, develop, and optimize scalable and serverless solutions, and to stay updated on the latest technologies for continuous improvement.}

% Incorporating desired qualifications
\lettercontent{Moreover, my familiarity with Snowflake, Databricks, and AWS Serverless technologies positions me well to contribute effectively in enhancing Bose's Data Platforms. I am keen on working under the mentorship of senior data engineers to further develop my expertise and deliver impactful outcomes in a collaborative environment.}

% Closing the letter
\lettercontent{I am excited about the opportunity to be part of a company like Bose that values innovation, learning, and creating transformative sound experiences. I am confident in my ability to actively contribute to the Data Engineering team and drive forward the data-driven transformation at Bose.}

\lettercontent{Thank you for considering my application. I look forward to the possibility of discussing how my background, skills, and enthusiasm align with the goals of Bose Corporation.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to Adem Mcharek's experiences and skills, reflecting his alignment with the job requirements at Bose Corporation. Adjustments can be made further based on feedback or additional information provided.