Based on the information provided and the details extracted from Adem Mcharek's resume, here is a tailored cover letter for the position at Astranis Space Technologies:

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Astranis Space Technologies}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the position at Astranis Space Technologies, where my background in Artificial Intelligence and hands-on experience in machine learning projects align well with the role you have outlined.}

\lettercontent{During my academic journey at Long Island University, I have led various projects that demonstrate my proficiency in AI and machine learning technologies. Particularly, orchestrating an AI Research Assistant using RAG for academic literature retrieval and developing a PyTorch CNN for image classification showcase my ability to apply cutting-edge technology in real-world scenarios.}

\lettercontent{The responsibilities outlined for this role, such as providing user prompts for the AI platform, evaluating results, and debugging the RAG pipeline, resonate with my experiences in project management and technical problem-solving. I am excited about the opportunity to contribute to the feasibility assessment of the RAG/LM pipeline in customer support scenarios at Astranis Space Technologies.}

\lettercontent{With a strong foundation in programming languages and a deep interest in AI and neural networks, I am well-equipped to tackle the challenges presented in this role. Moreover, my leadership experience as the Founder and President of the AI Club at LIU Brooklyn underscores my ability to drive innovative projects and collaborate effectively within a team.}

% Conclusion and signature
\lettercontent{I am confident that my technical skills, academic achievements, and passion for AI align well with the requirements of the position at Astranis Space Technologies. I am excited about the prospect of contributing to your team and would welcome the opportunity to discuss how my background can benefit your projects. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}