Based on the information provided from Adem Mcharek's resume and the job requirements and description for the Software Engineer Intern position at Addepar's Edinburgh office, we can create a customized cover letter in LaTeX format tailored to Adem Mcharek's qualifications and aspirations. 

Here is the customized LaTeX cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Addepar, Edinburgh Office}
\companyaddress{
Edinburgh, Scotland
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Addepar Recruitment Team,}

\lettercontent{I am writing to express my strong interest in the Software Engineer Intern position at Addepar in the Edinburgh office, as advertised. Currently pursuing a Bachelor's degree in Artificial Intelligence at Long Island University, with a diverse skill set in software engineering and a passion for innovative technologies, I am excited about the opportunity to contribute to Addepar's mission of creating a more transparent financial system.}

% Detail how Adem's skills align with the job requirements
\lettercontent{During my tenure as an AI Research Assistant at LIU Brooklyn, I spearheaded projects involving cutting-edge technologies like AI-enabled research navigation and PyTorch CNN models, demonstrating my ability to apply theoretical knowledge to practical solutions. My experience in computer vision using TensorFlow and my proficiency in Python, MySQL, and machine learning align well with the technical skills sought by Addepar, particularly in developing no-code initiatives and integrating public-facing APIs.}

% Mention Adem's specific experience that relates to the desired qualifications
\lettercontent{Moreover, my achievements in international mathematical competitions and leadership roles as the Founder and President of the AI Club at LIU Brooklyn showcase my exceptional problem-solving abilities, strong analytical skills, and collaborative mindset. These qualities are essential for managing individual project priorities, collaborating effectively with team members, and documenting software functionality, as outlined in the responsibilities of the Software Engineer Intern role at Addepar.}

% Express enthusiasm to contribute to Addepar's innovative projects
\lettercontent{I am particularly enthusiastic about the opportunity to work on non-latency sensitive investment strategies leveraging machine learning and quantitative methods at Addepar. The company's commitment to technological innovation, collaborative work culture, and global impact align with my career aspirations, and I am eager to contribute to Addepar's transformative initiatives under the guidance of experienced professionals.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to highlight Adem Mcharek's relevant experiences, skills, and aspirations, showcasing how they align with the job requirements and description provided by Addepar for the Software Engineer Intern position in their Edinburgh office. Feel free to customize it further if needed!