Based on the information provided from Adem Mcharek's resume and the job description at Acadian Asset Management LLC, I will now prepare a tailored cover letter in LaTeX format for the software engineering co-op position at the company. I will incorporate Adem Mcharek's experiences and skills to make the cover letter relevant and personalized for the job opportunity at Acadian Asset Management LLC.

Here is the complete LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Acadian Asset Management LLC}
\companyaddress{
Boston, Massachusetts
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the software engineering co-op position at Acadian Asset Management LLC. Currently pursuing a Bachelor's degree in Artificial Intelligence at Long Island University, with a keen focus on machine learning and deep learning, I am thrilled about the opportunity to apply my technical skills in a dynamic and innovative environment like Acadian.}

\lettercontent{During my academic journey, I have undertaken various projects that have equipped me with hands-on experience in AI research, neural networks, and computer vision. For instance, developing a CNN for classifying handwritten digits using PyTorch and creating a hand gesture recognition system with TensorFlow demonstrate my proficiency in deep learning and computer vision, which I believe are directly applicable to the challenges at Acadian.}

\lettercontent{Furthermore, my leadership experience as the Founder and President of the "AI Club" showcases my ability to lead and collaborate effectively in team settings, aligning with Acadian's emphasis on collaboration across business units. My dedication to fostering a vibrant community of AI enthusiasts and spearheading innovative AI projects reflects my commitment to driving impactful technological solutions.}

\lettercontent{I am particularly excited about the opportunity to build competencies in financial engineering and data analysis at Acadian. My solid foundation in mathematics, coupled with my programming skills in Python, align well with the responsibilities outlined for the role, such as working on complex problems and enhancing applications alongside different business units.}

% Conclusion and signature
\lettercontent{I am eager to contribute to Acadian's mission of finding unique investment opportunities through a combination of fundamental insights and cutting-edge technology. I am confident that my technical prowess, analytical skills, and commitment to excellence make me a suitable candidate for this software engineering co-op position. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to Adem Mcharek's qualifications and experiences, aligning them with the requirements and responsibilities of the software engineering co-op position at Acadian Asset Management LLC.