Based on the information gathered from the resume and the job description for the S S D Architecture position at Western Digital, I will now proceed to craft a tailored cover letter for Adem Mcharek to apply for the role at Astranis Space Technologies. Taking inspiration from Adem Mcharek's educational background, skills, and experiences, the cover letter will be customized to highlight his qualifications and interest in the position.

Here is the LaTeX code for Adem Mcharek's tailored cover letter for Astranis Space Technologies:

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Astranis Space Technologies}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the S S D Architecture position at Astranis Space Technologies, as advertised. With a projected graduation date in 2025 as a Bachelor's student, majoring in Applied Mathematics and possessing a solid background in coding languages such as Python and C, I am well-equipped to contribute effectively to the cutting-edge innovations and advancements in the field.}

\lettercontent{My educational journey has not only provided me with a strong analytical skill set but has also honed my problem-solving abilities, essential for defining future requirements, analyzing performance capabilities, and troubleshooting S S Ds. Through projects like optimizing algorithms and modeling electric scooter infrastructure, I have demonstrated my capability to translate complex mathematical concepts into practical solutions, a skill vital for designing and modifying firmware and A S I Cs at Astranis Space Technologies.}

\lettercontent{The opportunity to work at Astranis Space Technologies excites me, particularly the chance to contribute to setting the requirements and architecture of current and future S S Ds. I am eager to leverage my creative problem-solving skills, trade-off analysis expertise, and modeling capabilities to support the team in achieving industry-leading performance and product features.}

\lettercontent{With a keen interest in systems understanding and experience, coupled with a drive for continuous learning and innovation, I am confident in my ability to thrive in the dynamic and challenging environment at Astranis Space Technologies.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I look forward to the possibility of discussing how my background, skills, and aspirations align with the requirements of the S S D Architecture role.}

\signature{Adem Mcharek}

\end{document}

This cover letter is tailored to Adem Mcharek's experiences and qualifications, emphasizing his relevant skills and aspirations that align with the job description at Astranis Space Technologies.