Based on the information provided from Adem Mcharek's resume and the details about the position at Astranis Space Technologies, I will now draft a tailored cover letter for Adem to apply for the position of working closely with the Production team to analyze and interpret large datasets related to production quality at Astranis Space Technologies. 

Here is the LaTeX code for the cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Astranis Space Technologies}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the position at Astranis Space Technologies working closely with the Production team to analyze and interpret large datasets related to production quality. With a background in Engineering and a solid grounding in Applied Mathematics, I am excited about the opportunity to merge my technical expertise with the intricate dynamics of production quality analysis at a pioneering company like Astranis.}

\lettercontent{Throughout my academic journey, I have successfully undertaken projects that involved optimizing algorithms and modeling, showcasing my ability to translate complex mathematical concepts into practical solutions. The role at Astranis resonates with me as it offers the chance to leverage my analytical skills to enhance production quality and contribute to the company's mission of providing internet access through innovative technology.}

\lettercontent{I am particularly drawn to the collaborative environment at Astranis and the focus on utilizing cutting-edge technology to drive impactful change. My experience aligns well with the responsibilities of the role, including developing dashboards, identifying trends in defect rates, and supporting data-driven strategies for improved production quality. I am eager to bring my skills in data analysis and interpretation to Astranis to further its goals in bridging the digital divide and expanding global connectivity.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter captures Adem Mcharek's experiences and skills, aligning them with the role at Astranis Space Technologies and emphasizing his enthusiasm for contributing to the company's mission and growth. Feel free to adjust or refine any part of the cover letter to better suit Adem's preferences before submission.