Based on the information provided from Adem Mcharek's resume and the job description at Square for a hardware engineering role, we can now customize a cover letter for him to apply for this position. Below is the LaTeX code containing the tailored cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Square}
\companyaddress{
Oakland, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the hardware engineering position at Square, a company dedicated to building infrastructure for online payments and empowering businesses in the economy. As a student with a background in Mechanical Engineering, as well as Mechatronics, I am excited about the opportunity to contribute my technical skills and passion for innovation to Square's hardware team.}

\lettercontent{Throughout my academic journey and projects, such as optimizing algorithms and modeling for various infrastructures, I have acquired a solid foundation in translating complex concepts into practical solutions. I am particularly drawn to Square's commitment to technological innovation and collaborative work environment, which align perfectly with my aspirations and capabilities.}

% Matching qualifications and responsibilities
\lettercontent{I meet the requirements for the role by pursuing a degree in a related technical field, being familiar with programming languages like Python and Matlab, and having experience in utilizing statistical methods for data analysis. Additionally, my hands-on experience with hardware lab equipment and automation systems makes me well-suited to contribute to researching technologies and analyzing test data for Square's hardware products.}

\lettercontent{I am eager to immerse myself in Square's hardware development processes, collaborate with cross-functional teams, and support continuous improvement initiatives to enhance product quality and performance. My proactive problem-solving skills, adaptability, and strong communication capabilities further position me to excel in a dynamic environment like Square.}

% Closing and signature
\signature{Adem Mcharek}

\end{document}
```

This tailored cover letter aligns Adem Mcharek's skills, experiences, and aspirations with the requirements and responsibilities outlined in the job description at Square. It emphasizes his academic background, technical proficiency, and his enthusiasm to contribute to Square's innovative hardware engineering team.