Based on the information provided from Adem Mcharek's resume and the job description from Rockwell Automation, we can now proceed to create a tailored cover letter for Adem Mcharek applying for a position at Rockwell Automation. Below is the LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Rockwell Automation}
\companyaddress{
Milwaukee, Wisconsin
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the opportunity to join Rockwell Automation, a global technology leader focused on enhancing productivity and sustainability. With a background in Applied Mathematics and a passion for innovation, I am excited about the prospect of merging my technical expertise with the dynamic environment at Rockwell Automation.}

\lettercontent{Throughout my academic journey, I have worked on projects that involved optimizing algorithms and modeling for different industries, showcasing my ability to translate complex mathematical concepts into practical solutions. The commitment to technological innovation and collaborative culture at Rockwell Automation aligns perfectly with my aspirations and skills.}

\lettercontent{I am particularly drawn to the opportunity to create data models supporting digital solutions across various industries and to build scalable tools for processing structured and unstructured data. My proficiency in machine learning, data management strategies, and data visualization tools, such as R and Python, equip me to contribute effectively in such roles.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter is customized for Adem Mcharek, highlighting his experiences and skills that align with the job opportunity at Rockwell Automation. Feel free to adjust or expand the content further to better fit Adem's profile.