I have gathered all the relevant details from the provided documents. Now, I will proceed to craft a tailored LaTeX cover letter for Adem Mcharek based on the information extracted from his resume and the job requirements at Rockwell Automation. 

Let's begin with the customization.\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Rockwell Automation}
\companyaddress{
Milwaukee, Wisconsin
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Data Science Internship position at Rockwell Automation. With a Bachelor's degree in Artificial Intelligence and a solid foundation in Machine Learning, Mathematics, and Computer Science, I am excited about the opportunity to leverage my skills and knowledge in a dynamic industry leader like Rockwell Automation.}

% Summary of experiences related to the job responsibilities
\lettercontent{During my academic journey and research projects, I have developed proficiency in creating data models, building scalable tools for data processing, and implementing machine learning strategies. My experience in machine learning model development, data visualization, and data manipulation techniques aligns well with the responsibilities outlined for the role at Rockwell Automation.}

% Customized content highlighting Adem Mcharek's strengths
\lettercontent{Moreover, my academic achievements, including a 3.88 GPA, showcase my strong analytical and problem-solving skills. I have a passion for staying updated with the latest technologies, demonstrated by my active involvement in AI research and AI Club leadership. My experience as a D1 athlete in fencing and a tennis player for over 10 years reflects my versatility, discipline, and dedication to excelling in both academic and extracurricular pursuits.}

% Closing and call to action
\lettercontent{I am eager to contribute to Rockwell Automation's mission of enhancing productivity through technological advancements. I am confident that my blend of technical expertise, leadership skills, and commitment to excellence makes me a suitable candidate for the Data Science Internship. Thank you for considering my application.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}