Based on the information provided from Adem Mcharek's resume and the job requirements and responsibilities for the position at Astranis Space Technologies, I will now compose a personalized cover letter in LaTeX format tailored to Adem Mcharek's profile and the job opportunity.

Here is the customized LaTeX cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Secureworks}
\companyaddress{
Global Cybersecurity Leader
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the software engineering position at Secureworks, known for its commitment to cybersecurity and fostering innovation in a collaborative environment. With a Bachelor's degree in Artificial Intelligence from Long Island University and a diverse technical skill set, including experience in projects like AI Research Assistance, PyTorch CNN development, and Computer Vision using TensorFlow, I am excited about the opportunity to contribute to a dynamic and cutting-edge engineering culture at Secureworks.}

\lettercontent{With a solid foundation in machine learning, deep learning, and software engineering, I am well-prepared to take on the responsibilities of building performant Graph QL APIs using Golang and Kubernetes, collaborating with diverse engineering teams, and developing internal authorization systems at Secureworks. My experience working with docker, Kubernetes, and Go aligns well with the desired qualifications for the role.}

\lettercontent{I am particularly drawn to Secureworks' emphasis on continuous learning, global exposure, and innovative engineering practices, which resonate with my career aspirations and passion for leveraging technology to enhance cybersecurity. I am confident that my technical expertise, self-motivation, and ability to communicate effectively with remote teams make me a valuable candidate for contributing to Secureworks' mission of securing human progress through cutting-edge cybersecurity solutions.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am looking forward to the possibility of discussing how I can contribute to Secureworks' innovative projects and engineering excellence.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to Adem Mcharek's educational background, technical skills, and experiences, aligning them with the requirements and responsibilities of the software engineering position at Secureworks. It highlights his qualifications and enthusiasm for contributing to a leading cybersecurity company like Secureworks.