Based on the provided information from Adem Mcharek's resume and the details about the internship position at Schonfeld Risk Team, here is a customized cover letter tailored to Adem Mcharek for the Sector Data Analyst Summer Intern role at Schonfeld Strategic Advisors:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Schonfeld Strategic Advisors}
\companyaddress{
New York, New York
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Sector Data Analyst Summer Intern position at Schonfeld Strategic Advisors. With a background in a quantitative field and a keen interest in utilizing real-world data in the investment process, I am excited about the opportunity to contribute to the Schonfeld Risk team's quantitative risk research projects.}

\lettercontent{During my academic journey, I have engaged in projects involving data analysis and mathematical modeling, such as optimizing algorithms and leveraging data for infrastructure development. These experiences have equipped me with the ability to translate complex mathematical concepts into practical solutions, preparing me well for the empirical research involved in your internship role.}

\lettercontent{I am particularly drawn to Schonfeld's focus on innovative research and collaborative work environment, which aligns with my aspirations and skills. The chance to work alongside data scientists and engineers to enhance my understanding of datasets and their impact on investment decisions excites me.}

\lettercontent{My proficiency in Python, knowledge of data science principles, and interest in learning about hedge fund strategies make me well-suited for the responsibilities of the Sector Data Analyst Summer Intern role. I am eager to leverage these skills to drive impactful insights from real-world data and contribute to the dynamic culture at Schonfeld Strategic Advisors.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter combines Adem Mcharek's educational background and experiences with the specific requirements and responsibilities of the internship position at Schonfeld Strategic Advisors. It highlights his skills and interests that align with the role, emphasizing his enthusiasm for contributing to the Schonfeld Risk team's quantitative risk research projects.