Based on the information provided for Adem Mcharek and the internship opportunity at Schonfeld, I will now create a tailored cover letter in LaTeX format. Let's begin by integrating Adem's details and customizing the content to fit the role at Schonfeld. 

I will incorporate Adem's information, the company details, the requirements and responsibilities, the desired qualifications, and the internship program specifics provided for Schonfeld. Let's proceed with crafting the customized cover letter for Adem Mcharek. 

Before that, let me examine the details further to accurately tailor the cover letter to the internship role at Schonfeld. Let's begin by reviewing the key requirements, responsibilities, and characteristics of the ideal candidate included in the provided information.Based on the detailed content provided from the resume examples, I will now proceed to tailor a compelling and personalized cover letter for Adem Mcharek applying for the internship opportunity at Schonfeld. I will incorporate his details and experiences to align with the internship role's requirements and responsibilities at Schonfeld. Let's compile the cover letter in LaTeX format.

Here is the tailored cover letter for Adem Mcharek:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Schonfeld Strategic Advisors}
\companyaddress{
New York, New York
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the internship opportunity at Schonfeld Strategic Advisors. As a dedicated student pursuing a bachelor's degree in computational finance, with a solid foundation in computer science and data analytics, I am excited about the prospect of joining a renowned company dedicated to financial independence and innovation.}

\lettercontent{My academic journey and hands-on projects, such as optimizing algorithms and modeling for complex systems, have honed my analytical mindset and problem-solving abilities. This experience, combined with my proficiency in programming languages like Python and Java, aligns well with the technical and collaborative environment at Schonfeld.}

% Skills and experiences
\lettercontent{I am particularly drawn to the opportunity to develop business critical software for the Treasury desk at Schonfeld, leveraging my technical skills to contribute to valuable projects. My interest in investing and markets, coupled with a strong foundation in computational finance, positions me well to understand the daily flow and activity of the desk and enhance its efficiency.}

% Closing and signature
\lettercontent{I am confident that my academic background and passion for finance make me a suitable candidate for this internship. I am excited about the prospect of working alongside talented professionals at Schonfeld and contributing to high-profile projects.}

\lettercontent{Thank you for considering my application. I look forward to the possibility of discussing how I can contribute to Schonfeld Strategic Advisors.}

\signature{Adem Mcharek}

\end{document}
```

This LaTeX code provides a tailored cover letter for Adem Mcharek applying for the internship opportunity at Schonfeld Strategic Advisors. It integrates his skills, experiences, and aspirations to align with the requirements and responsibilities of the role at Schonfeld.