Based on the information provided about the internship opportunity at Schonfeld Strategic Advisors, we will integrate details from Adem Mcharek's resume to create a tailored cover letter for him. The cover letter will emphasize his relevant experiences, skills, and aspirations that align with the requirements and responsibilities of the internship role.

Here is the LaTeX code for the customized cover letter for Adem Mcharek:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Schonfeld Strategic Advisors}
\companyaddress{
New York, New York
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the internship opportunity at Schonfeld Strategic Advisors as advertised. With a background in computational finance and a keen interest in programming languages like Python, I am excited about the prospect of contributing to your Treasury desk team and developing business critical software during the summer internship program.}

\lettercontent{My academic pursuits in computational finance and my experience working on financial software projects have equipped me with the skills to analyze market data, develop efficient solutions, and collaborate effectively within a team setting. I am particularly drawn to the opportunity to understand the daily operations of the desk, add value to investors, and enhance the codebase to improve efficiency within the firm.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to highlight Adem Mcharek's background in computational finance and programming, aligning with the internship requirements and responsibilities at Schonfeld Strategic Advisors. Adjustments can be made based on additional information or preferences.