Based on the information extracted from Adem Mcharek's resume and the job requirements and responsibilities provided for the position at Arcellx, here is a customized LaTeX cover letter tailored to Adem Mcharek for the role at Arcellx:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Arcellx}
\companyaddress{
Rockville, Maryland
Redwood City, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the position at Arcellx reimagining cell therapy. With a solid educational background in Applied Mathematics and proven experience in optimizing algorithms and data analysis, I am enthusiastic about the opportunity to merge my analytical skills with the innovative immunotherapies developed at Arcellx. The prospect of collaborating with cross-functional teams to enhance data-driven decision making and contribute to the development of predictive models excites me.}

\lettercontent{My experiences align closely with the responsibilities outlined for the role, including collecting, processing, and analyzing data to derive insights, creating visualizations for informed decision-making, and organizing datasets for predictive modeling. I am eager to leverage my skills in Excel and my familiarity with visualization tools such as Spotfire and Tableau in this dynamic environment.}

\lettercontent{I resonate with Arcellx's core values of Character, Audacity, Determination, Collaboration, and Originality, and I am keen on contributing to the mission of advancing humanity through innovative cell therapies. My strong commitment to excellence, coupled with effective team communication and presentation skills, positions me well to support Arcellx in its quest to defeat cancer and make therapies more accessible.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to Adem Mcharek's experiences, skills, and aspirations, aligning them with the job requirements and responsibilities at Arcellx. It emphasizes Adem's analytical skills, proficiency in Excel and visualization tools, effective communication, and his educational background to demonstrate suitability for the position.