Based on the information provided in Adem Mcharek's resume and the job description for a Software Engineer Intern at Visa, I will now craft a tailored cover letter in LaTeX format for the job opportunity at Visa. 

Here is the LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Visa}
\companyaddress{
Foster City, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Software Engineer intern position at Visa. As a proactive AI Research Assistant at LIU Brooklyn with a strong background in Python, MySQL, Pytorch, Tensorflow, Docker, C++, JavaScript, Node.js, and Unity, I am excited about the opportunity to apply my technical skills and problem-solving abilities in a dynamic environment like Visa.}

\lettercontent{My experiences align closely with the responsibilities outlined for the role, such as developing software solutions, implementing robust app factories, and documenting processes. I have a solid foundation in software engineering concepts and methodologies, making me well-prepared to contribute effectively to the innovative projects at Visa.}

\lettercontent{Furthermore, my proficiency in Python and Java, along with experience in building automation tools using Selenium and REST, positions me well to excel in creating impactful solutions during the internship. I am particularly drawn to Visa's focus on innovation and global connections, and I am eager to collaborate with diverse teams to drive digital transformation.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter integrates Adem Mcharek's experiences, skills, and aspirations, aligning them with the requirements and responsibilities of the Software Engineer internship position at Visa. Feel free to adjust any details further to better suit Adem's unique qualifications and the job opportunity at Visa.