Based on the information provided in Adem Mcharek's resume and the job requirements and responsibilities at Visa, I will now draft a customized cover letter tailored to the job description at Visa for a Software Engineer internship position.

Here is the LaTeX code for Adem Mcharek's personalized cover letter:

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Visa}
\companyaddress{
Foster City, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Software Engineer internship position at Visa, a company dedicated to removing barriers and connecting more people to the global economy through innovative financial infrastructure. Currently pursuing a Bachelor's degree in Artificial Intelligence at Long Island University, with a strong GPA of 3.88/4.00, I am excited about the opportunity to apply my skills and knowledge in a dynamic and impactful environment like Visa.}

\lettercontent{With a foundation in Artificial Intelligence and a passion for technology, I have engaged in projects that involved optimizing algorithms and modeling for practical applications. These experiences have honed my ability to translate complex concepts into actionable solutions, aligning well with the requirements at Visa for analyzing, designing, and unit testing software solutions.}

\lettercontent{Furthermore, my academic background has equipped me with a solid understanding of software engineering concepts and methodologies, as well as good analytical and problem-solving skills. I have experience with programming languages such as [mention specific languages from the job requirements or your resume], and have worked on projects that required familiarity with software testing principles and the development of automation tools.}

% Conclusion and signature
\lettercontent{I am highly driven, resourceful, and results-oriented, traits that I believe align with Visa's commitment to innovation and excellence. I am eager to contribute to Visa's mission and be part of a team that leverages cutting-edge technology to shape the future of global transactions. I look forward to the opportunity to further discuss how my background and skills can contribute to Visa's continued success.}

\signature{Adem Mcharek}

\end{document}

This cover letter integrates Adem Mcharek's educational background, skills, and experiences to match the requirements and responsibilities outlined in the job description at Visa. It emphasizes his enthusiasm for the role and his alignment with Visa's mission and values.