Based on the information provided about User Testing and the specific requirements and responsibilities for the Software Engineering Intern position, I will now tailor the cover letter for Adem Mcharek to apply for this role at User Testing. The cover letter will be customized to highlight Adem's qualifications and experiences that align with the company's values and needs.

Here is the LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{User Testing}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am excited to apply for the Software Engineering Intern position at User Testing, a company that truly resonates with my passion for enhancing user experiences through human-centered approaches. With a background in front-end technologies including JavaScript, TypeScript, React, HTML, and CSS, coupled with my strong analytical and problem-solving skills, I am confident in my ability to contribute effectively to the development of the contributor experience on the User Testing platform.}

\lettercontent{I am particularly drawn to User Testing's emphasis on empathy and customer feedback, values that I hold dear in my approach to software development. My experience in full-stack software engineering and collaborating with diverse teams aligns well with the responsibilities outlined for the role, including delivering software to the UT Contributor Network and engaging in cross-team collaborations.}

% Conclusion and signature
\lettercontent{I am eager to leverage my technical skills and passion for user experience to help User Testing build the engine for human understanding. I am thrilled about the opportunity to learn and grow in a market-leading company while contributing my unique perspective and energy to the team.}

\lettercontent{Thank you for considering my application. I look forward to the possibility of contributing to User Testing and being part of a team dedicated to transforming how companies connect with their audiences through exceptional experiences.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to highlight Adem Mcharek's qualifications, experiences, and enthusiasm for the Software Engineering Intern position at User Testing, showcasing alignment with the company's values and requirements.