Based on the detailed job description for the Software Engineering Intern position at Affinitiv, we will now tailor a cover letter for Adem Mcharek with the provided information. 

We will incorporate Adem Mcharek's personal and professional details along with his skills and experiences to create a customized cover letter. Below is the LaTeX code for the tailored cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Affinitiv}
\companyaddress{
Deer Park, Illinois
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Software Engineering Intern position at Affinitiv as advertised. With a strong academic background and hands-on experience in C#, Java, SQL, and version control systems, I am excited about the opportunity to contribute to your team and gain valuable insights into the automotive customer lifecycle.}

\lettercontent{During my studies, I have maintained a GPA above 3.0, showcasing my commitment to academic excellence. Additionally, my practical experience with Python and MySQL, coupled with my proficiency in Angular/JavaScript frameworks, aligns well with the technical skills you are seeking in a candidate.}

\lettercontent{I am particularly drawn to Affinitiv's dedication to driving the next-generation customer experience and its focus on innovation in software solutions for the automotive industry. The emphasis on end-to-end project completion, collaboration within the Essentials team, and exposure to cutting-edge technologies resonates with my career aspirations in software development.}

% Conclusion and signature
\lettercontent{I am eager to leverage my skills in software engineering, attention to detail, and passion for problem-solving to contribute to Affinitiv's mission of inspiring loyalty and retailer performance. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter integrates Adem Mcharek's qualifications, skills, and aspirations with the requirements and responsibilities outlined by Affinitiv for the Software Engineering Intern position. Feel free to adjust any details further or let me know if any modifications are needed.