Based on the provided information about Adem Mcharek and the specific job opportunity at Cars Commerce, I will now proceed to craft a tailored cover letter for him to apply for the Site Analytics Intern position at Cars Commerce based on the details extracted from his resume and the job requirements and responsibilities provided.

Here is the LaTeX code for the personalized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Cars Commerce}
\companyaddress{
London, UK
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Recruitment Team,}

\lettercontent{I am writing to express my genuine interest in the Site Analytics Intern position at Cars Commerce, as advertised. With a strong background in Applied Mathematics and a demonstrated ability to translate complex mathematical concepts into practical solutions, I am excited about the opportunity to merge my technical proficiency with the dynamic environment of Cars Commerce.}

\lettercontent{Throughout my academic journey, I have undertaken various projects that have honed my analytical skills, including optimizing algorithms and modeling complex systems. My experience aligns well with the responsibilities outlined for the position, such as building dashboards, analyzing consumer behavior data, and developing processes to monitor key performance indicators.}

\lettercontent{Moreover, my proficiency in Microsoft Office suite, coupled with a detail-oriented and organized approach to tasks, make me well-suited to thrive in a fast-paced, team-oriented environment as described in the job requirements. I am currently working towards a Bachelor's degree in Applied Mathematics, which provides me with a solid foundation for data analysis and metrics creation.}

% Additional information specific to the job role
\lettercontent{I am particularly drawn to the collaborative and innovative culture at Cars Commerce, as well as the emphasis on simplifying technology to enhance automotive retail. I am eager to contribute to projects that drive local automotive retail forward using my analytical mindset and technical skills.}

% Conclusion and signature
\lettercontent{I am excited about the prospect of joining Cars Commerce and contributing to its success as a Site Analytics Intern. Thank you for considering my application. I look forward to the opportunity to discuss how I can add value to your team.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to align Adem Mcharek's experiences and skills with the requirements and responsibilities of the Site Analytics Intern position at Cars Commerce, focusing on his analytical capabilities and technical proficiency. Adjustments can be made as necessary to further personalize the content.