Based on the information provided in Adem Mcharek's resume and the job description for the Software Engineering Intern position at Ascend Analytics, I will now proceed to craft a customized cover letter for Adem Mcharek tailored to the internship opportunity at Ascend Analytics.

Here is the LaTeX code for the tailored cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Ascend Analytics}
\companyaddress{
Boulder, Colorado
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Software Engineering Intern position at Ascend Analytics, as advertised for the Summer 2024 term. With a strong academic background in Artificial Intelligence, including hands-on experience in machine learning, deep learning, and software engineering, I am excited about the opportunity to contribute to Ascend's innovative projects in energy analytics and optimization.}

\lettercontent{During my tenure as an AI Research Assistant at LIU Brooklyn, I led projects implementing cutting-edge technologies like convolutional neural networks and computer vision systems, emphasizing my ability to translate advanced technical concepts into practical applications. My proactive involvement in founding and leading the AI Club demonstrates my commitment to fostering collaborative environments and driving impactful projects.}

% Match skills and qualifications
\lettercontent{My proficiency in Python, PyTorch, TensorFlow, and React aligns well with the requirements for the internship position. With a GPA of 3.88 and a track record of achieving success in international competitions like the International Youth Mathematical Olympiad, I bring a blend of technical expertise, problem-solving skills, and a passion for creating software solutions that can drive the energy transition forward.}

% Closing and signature
\lettercontent{I am excited about the possibility of contributing to the transformative work at Ascend Analytics and am eager to bring my technical skills and commitment to excellence to your team. Thank you for considering my application. I look forward to the opportunity to discuss how my background and experiences align with the goals of Ascend Analytics.}

\signature{Adem Mcharek}

\end{document}
```

This LaTeX code incorporates Adem Mcharek's academic achievements, technical skills, and experiences to showcase a strong fit for the Software Engineering Intern position at Ascend Analytics. It aligns his skills and qualifications with the requirements of the role while expressing his enthusiasm for contributing to the innovative projects at Ascend Analytics.