Based on the information provided about Adem Mcharek and the job opportunity at Intrinsic (an Alphabet subsidiary), here is a tailored cover letter in LaTeX format that aligns with the requirements and responsibilities outlined for the position:

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Intrinsic (Alphabet Subsidiary)}
\companyaddress{
Mountain View, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Internship opportunity at Intrinsic to contribute to the development of robotics software, particularly focusing on the innovative platform Flowstate. With a strong background as a Bachelor’s student in Computer Science and a keen interest in the intersection of software development, artificial intelligence, and robotics, I am excited about the prospect of joining a dynamic team dedicated to reimagining the potential of industrial robotics.}

\lettercontent{My experience and proficiency in modern software development languages like C++, Python, and Go, combined with a solid foundation in Computer Graphics and Web development, align well with the requirements outlined for the role at Intrinsic. I am eager to collaborate with experienced professionals to explore and implement cutting-edge solutions in software development, contributing to the mission of making industrial robotics intelligent, accessible, and usable for a diverse range of businesses and developers.}

\lettercontent{Moreover, my track record of developing tools and intuitive interfaces for various applications, along with effective coordination skills acquired through previous projects, positions me well to actively contribute to the digital twins team at Intrinsic. I am particularly motivated by the opportunity to work on a unified web-friendly rendering solution for the Flowstate platform, furthering the mission of democratizing robotics technology.}

% Conclusion and signature
\lettercontent{Intrinsic's culture of celebrating diversity and fostering an inclusive workplace resonates with my values, and I am eager to bring my passion for technology and innovation to your team. I am excited about the prospect of positively impacting the future of industrial robotics through my work at Intrinsic. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}

This cover letter is tailored to Adem Mcharek's qualifications, experiences, and aspirations, aligning them with the specific job role and requirements at Intrinsic. It highlights his skills in software development, interest in robotics technology, and enthusiasm for contributing to the company's mission.