To create a tailored cover letter for Adem Mcharek applying for the Data Analyst Internship at Elevance Health for Summer 2024, we will integrate details from Adem Mcharek's resume with the job requirements and responsibilities provided by Elevance Health. Below is the LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Elevance Health}
\companyaddress{
Indianapolis, Indiana
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Data Analyst Internship for Summer 2024 at Elevance Health, as advertised. Currently pursuing a bachelor's degree in Computer Science and possessing a keen interest in healthcare technology, I am excited about the opportunity to contribute to Elevance Health's mission of reimagining the health system through advanced whole-health approaches.}

\lettercontent{With a solid foundation in Python, R, and Java, as well as experience with public cloud platforms like AWS, I am well-equipped to develop strategies, programs, and solutions that align with business priorities and consumer insights. My proficiency in data science, artificial intelligence, and machine learning, combined with my ability to quickly learn and adapt, positions me to thrive in a fast-paced environment like Elevance Health.}

% Matching skills and experiences
\lettercontent{Moreover, my experience in text analytics, natural language processing, and database querying languages, along with my knowledge of emerging AI topics, frameworks like Nextjs, and reporting tools such as Power BI, align closely with the desired qualifications for the role. I am eager to leverage these skills to support Elevance Health in creating innovative solutions that drive positive outcomes for both the company and its patients.}

\lettercontent{I am particularly drawn to Elevance Health's commitment to making healthcare more accessible and affordable, and I am enthusiastic about the opportunity to contribute to such a meaningful mission.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter integrates Adem Mcharek's skills and experiences with the specific requirements and responsibilities of the Data Analyst Internship at Elevance Health for Summer 2024, presenting a personalized and compelling application for the position.