After reviewing the resume and the job description for the Data Analyst Internship position at Elevance Health, we can create a tailored cover letter for Adem Mcharek to apply for this opportunity. Taking into consideration Adem's experiences, skills, and aspirations, we will craft a compelling cover letter that aligns with the provided job requirements and responsibilities. Below is the LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Elevance Health}
\companyaddress{
Indianapolis, Indiana
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Data Analyst Internship - Summer 2024 position at Elevance Health. As a student actively pursuing a bachelor's degree in Computer Science, with a solid foundation in Statistics and Physics, I am excited about the opportunity to leverage my academic background and skills in a dynamic healthcare tech environment like Elevance Health.}

\lettercontent{With projects focusing on optimizing algorithms and modeling, I have honed my ability to translate complex mathematical concepts into practical solutions. The commitment of Elevance Health to reimagine the health system resonates with me, and I am eager to contribute to the company's mission of improving outcomes and accessibility in healthcare.}

\lettercontent{I am well-equipped to meet the responsibilities of the internship, including developing strategies based on business priorities, gathering market requirements, and learning quickly to apply new knowledge. My experience has prepared me to work 40 hours per week throughout the Summer 2024 internship period.}

\lettercontent{Furthermore, my proficiency in Python, R, Java, and other tools aligns with the desired qualifications for the role. I am a quick learner, comfortable in fast-paced environments, and possess strong communication and collaboration skills, essential for effective cross-functional teamwork.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to Adem Mcharek's qualifications and aspirations, emphasizing his academic background, project experiences, technical skills, and alignment with the job requirements at Elevance Health.