Based on the information provided about the job opportunity at Olo, I will now generate a tailored cover letter for Adem Mcharek. This cover letter will emphasize his experiences, skills, and aspirations relevant to the Data Science Intern position at Olo. 

Here is the customized cover letter in LaTeX format:

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Olo}
\companyaddress{
New York, New York
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Data Science Intern position at Olo as advertised. With a background in Data, Computer Science, and Statistical Analysis, coupled with proficiency in SQL, Python, and experience working within Jupyter Notebooks, I am excited about the opportunity to contribute to Olo's innovative approach to enabling restaurant brands to scale online ordering and delivery while personalizing guest experiences.}

% Adem's qualifications and skills matching the requirements
\lettercontent{My significant coursework in Data Science, combined with practical project work, has equipped me with the skills to work closely with your data science team to set up tests, gather insights, and contribute new ideas to existing data products and reports. I am driven by continuous growth and learning, and my curiosity to explore unknowns aligns perfectly with the aim of discovering new business insights at Olo.}

% Contribution to the team and capstone project
\lettercontent{I am eager to collaborate with Software Engineers, Product Managers, and Design interns on the Summer Capstone Project, where I can leverage my skills to contribute effectively to team documentation, data dictionaries, and iterate on data products to enhance Olo's platform.}

% Closing statement and signature
\lettercontent{Thank you for considering my application. I am enthusiastic about the possibility of contributing to Olo's dynamic team and being part of a company that drives the digital transformation of the restaurant industry.}

\signature{Adem Mcharek}

\end{document}



This cover letter aims to highlight Adem Mcharek's qualifications and enthusiasm for the Data Science Intern position at Olo, focusing on his skills and experiences that align with the company's requirements and expectations.