Based on the information provided, I will now proceed to incorporate Adem Mcharek's skills, experiences, and aspirations into a customized cover letter tailored to the internship opportunity at Identifeye Health, a company pioneering non-invasive diagnostic platforms. Let's craft the cover letter using LaTeX:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% Header section with personal information
\namesection{Ademb}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Identifeye Health}
\companyaddress{
Guilford, Connecticut
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Software Engineering Internship at Identifeye Health. As a dedicated student pursuing a Bachelor's degree in Artificial Intelligence at Long Island University, with a strong foundation in software development and hands-on experience in AI projects, I am excited about the opportunity to contribute to the innovative work happening at Identifeye Health.}

\lettercontent{Through my role as an AI Research Assistant, where I orchestrated complex AI systems for real-time academic research, and my projects involving PyTorch CNN for MNIST and Computer Vision using TensorFlow, I have developed a solid understanding of software development, deep learning, and neural network architecture. My achievements in international mathematical competitions and leadership roles, including founding the AI Club at LIU Brooklyn, have honed my problem-solving skills and ability to lead collaborative projects.}

\lettercontent{Identifeye Health's commitment to democratizing access to health information aligns with my goal of applying technology to solve real-world problems and make a positive impact in the healthcare industry. I am particularly excited about the opportunity to work on iOS development, implement new features, participate in code reviews, and contribute meaningfully to your innovative products.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter incorporates Adem Mcharek's academic background, relevant AI projects, leadership experiences, and enthusiasm for contributing to Identifeye Health's mission. Feel free to adjust any details or add more personalized elements as needed.