Based on the information provided in Adem Mcharek's resume and the job description for the internship program at Western Digital in summer 2024, we can tailor a cover letter for Adem to apply for the internship position. Below is the customized cover letter in LaTeX format incorporating Adem's experiences, skills, and aspirations:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Western Digital}
\companyaddress{
San Jose, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the internship program at Western Digital in the summer of 2024, particularly for the opportunity to participate in the development of the Flash Memory Testing Platform. With a Bachelor's degree in Artificial Intelligence from Long Island University, relevant coursework in machine learning, deep learning, and software engineering, and hands-on experience in AI research projects, including developing AI-enabled solutions for real-time applications, I am keen to contribute my technical skills to advancing Western Digital's Enterprise-grade SSD solutions.}

\lettercontent{My proficiency in Python, experience with neural network architectures such as Convolutional Neural Networks, and practical projects in computer vision using TensorFlow align well with the requirements of developing software programs and tester hardware for the Flash Memory Testing Platform. The emphasis on electronic hardware design and collaborative troubleshooting resonates with my experience in team projects focusing on AI and machine learning applications.}

\lettercontent{Being a current student pursuing a Bachelor's degree in Artificial Intelligence and expecting to graduate in 2025, I am eager to apply my skills in programming, object-oriented design, and data analysis to contribute effectively to the innovative projects at Western Digital. I am excited about the opportunity to work with System Design Engineers, leveraging my expertise in AI and software development to enhance the test platform's capabilities.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter highlights Adem's academic background in Artificial Intelligence, relevant technical skills, experience with AI research projects, and his alignment with the internship requirements at Western Digital. It showcases his motivation to contribute to the development of the Flash Memory Testing Platform and his readiness to collaborate with the System Design Engineers at Western Digital.