Based on the information extracted from Adem Mcharek's resume, which includes his projects, skills, and leadership experience, we can tailor a cover letter for him applying for the internship position at Tegus as part of the engineering team. Below is the LaTeX cover letter customized for Adem Mcharek:

```
\documentclass[]{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Tegus}
\companyaddress{
Seed Total Funding: \$111.5 M \\
Founded: 2017 \\
Headquarters: Chicago, Illinois
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm in applying for the intern position at Tegus, a leading market intelligence platform. With a background encompassing projects focused on optimizing algorithms and modeling, along with a robust skill set in areas such as Ruby on Rails, Python, and Vue, I am thrilled about the opportunity to contribute to the engineering team at Tegus. The culture of innovation, collaborative spirit, and commitment to excellence exhibited by Tegus align perfectly with my aspirations and technical proficiency.}

% Additional tailored content
\lettercontent{Throughout my academic journey, I have honed my abilities to develop robust and effective software solutions, which I believe will be instrumental in shipping new features to customers and addressing complex engineering challenges at Tegus. My experience in analyzing and designing solutions to business problems, coupled with a passion for continuous learning, makes me well-prepared to thrive in Tegus' dynamic environment.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter integrates Adem Mcharek's pertinent skills, experiences, and aspirations to present a tailored application for the intern position at Tegus. The content highlights his technical proficiency, project backgrounds, and alignment with Tegus' company culture and values.