Based on the information provided for the 2024 Summer Print Software Engineer Intern position at HP, Inc., I will now prepare a tailored cover letter in LaTeX format for Adem Mcharek. This cover letter will reflect his experiences, skills, and aspirations relevant to the internship opportunity at HP, Inc. Let's proceed with creating the cover letter.I have gathered the necessary information from Adem Mcharek’s resume and the details about the 2024 Summer Print Software Engineer Intern position at HP, Inc. I will now proceed to generate a tailored cover letter in LaTeX format for Adem Mcharek based on the provided information. Let's create the cover letter.Here is the LaTeX code for the customized cover letter for Adem Mcharek applying for the 2024 Summer Print Software Engineer Intern position at HP, Inc:

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{HP, Inc.}
\companyaddress{
Palo Alto, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the 2024 Summer Print Software Engineer Intern position at HP, Inc. With a solid academic background in Artificial Intelligence and a diverse set of technical skills, including proficiency in Python, Pytorch, and TensorFlow, I am excited about the opportunity to apply my knowledge to real-world challenges in developing cutting-edge printing technology at HP, Inc.}

% Qualifications and skills tailored to the job description
\lettercontent{During my tenure as an AI Research Assistant at LIU Brooklyn, I orchestrated projects using advanced technologies such as Convolutional Neural Networks and Machine Learning algorithms, showcasing my ability to translate complex mathematical concepts into practical solutions. My experiences in developing AI applications for real-time academic literature retrieval and hand gesture recognition systems align well with the innovative and technology-driven environment at HP, Inc.}

% Desire to contribute and learn at HP, Inc.
\lettercontent{I am particularly drawn to HP, Inc.'s commitment to innovation and providing a platform for interns to make a meaningful impact. The opportunity to collaborate with diverse teams, engage in executive speakers, and work on big projects resonates with my passion for pushing boundaries and learning from experienced professionals in the field. I am eager to contribute to HP, Inc.'s vision of engineering experiences that inspire progress.}

% Closing and signature
\lettercontent{Thank you for considering my application. I am excited about the possibility of contributing to HP, Inc.'s innovative projects and am eager to discuss how my background and skills align with the requirements of the Summer Print Software Engineer Intern position.}

\signature{Adem Mcharek}

\end{document}

This cover letter is tailored to highlight Adem Mcharek's relevant experiences, skills, and aspirations, making him a strong candidate for the 2024 Summer Print Software Engineer Internship at HP, Inc.