Based on the information provided and Adem Mcharek's resume, I will now compose a tailored cover letter in LaTeX format for the position at Moloco. Incorporating Adem's experiences and skills, the cover letter will be personalized to highlight his qualifications and interest in the role at Moloco. 

Here is the LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Moloco}
\companyaddress{
Silicon Valley, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Machine Learning intern position at Moloco, a company that is at the forefront of empowering organizations to unlock the full value of their unique first-party data through cutting-edge machine learning technologies. As a Bachelor's student in Artificial Intelligence with a diverse background in machine learning and deep learning, along with hands-on experience in developing AI systems and conducting experiments on state-of-the-art models, I am excited about the opportunity to contribute to Moloco's mission of leveraging machine learning to drive growth and innovation in the digital economy.}

% Skills and experiences related to the job requirements
\lettercontent{My AI Research Assistant role at LIU Brooklyn, where I orchestrated an AI-driven research assistant utilizing advanced multi-agent systems for academic literature retrieval, has equipped me with the skills to work on sophisticated machine learning projects. I have a strong foundation in data structures, algorithms, and coding, evident from projects like developing a PyTorch CNN for MNIST digit classification and implementing Computer Vision systems using TensorFlow. These experiences have honed my abilities to optimize algorithms, build data pipelines, and develop machine learning tools, aligning closely with the responsibilities outlined for the intern role at Moloco.}

% Closing and aspirations
\lettercontent{I am particularly drawn to Moloco's commitment to innovation and fostering a culture of inclusion and belonging. I am eager to further develop my skills and contribute to the impactful work at Moloco, leveraging my technical expertise and passion for machine learning. I am enthusiastic about the possibility of collaborating with the talented team at Moloco and being part of a company that is shaping the digital economy through operational machine learning.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to reflect Adem Mcharek's qualifications, skills, and experiences in the field of machine learning, aligning them with the requirements and responsibilities of the internship position at Moloco. He expressed his enthusiasm, skills, and aspirations in a professional and personalized manner to make a strong case for his application.