Based on the information provided from Adem Mcharek's resume and the internship opportunity at Kargo in New York for an Intern, Data Analytics position, we can create a tailored cover letter in LaTeX format. Let's integrate Adem Mcharek's educational background, experiences, and skills into the template provided to craft a personalized cover letter for the internship at Kargo.

Here is the LaTeX code for the customized cover letter for Adem Mcharek applying to the Intern, Data Analytics position at Kargo:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Kargo}
\companyaddress{
New York, NY
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Intern, Data Analytics position at Kargo. With a Bachelor's degree in Artificial Intelligence from Long Island University and a strong background in Machine Learning, Deep Learning, Statistics, and Data Mining, I am excited about the opportunity to contribute to Kargo's Analytics team.}

\lettercontent{During my academic journey, I have undertaken impactful projects such as developing AI Research Assistants, implementing Convolutional Neural Networks, and creating solutions in Computer Vision using TensorFlow. These experiences have equipped me with the technical skills and analytical mindset required for the internship role at Kargo.}

\lettercontent{I am particularly drawn to Kargo's focus on maximizing revenue through data insights and creating automated dashboards using Looker, which aligns well with my experience in constructing analytical solutions. I am eager to collaborate with professionals from Engineering, Product, Operations, and Sales departments to address data needs effectively.}

\lettercontent{Moreover, my curiosity and passion for learning about the Ad Tech Industry make me excited about the prospect of contributing to Kargo's innovative initiatives. With proficiency in SQL, Python, and experience with tools like Looker and Google Analytics, I am confident in my ability to excel in leveraging data for business impact at Kargo.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am keen on the opportunity to bring my skills and dedication to the dynamic environment at Kargo. I look forward to the possibility of contributing to Kargo's continued success.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter integrates Adem Mcharek's educational background, projects, technical skills, and enthusiasm for the Ad Tech Industry, aligning them with the internship position at Kargo. It highlights relevant experiences and skills to showcase a strong fit for the role.