Based on the detailed information provided regarding Aero Vect, I will now proceed to create a tailored cover letter in LaTeX format for Adem Mcharek applying for the Planning Engineer position at Aero Vect. I will incorporate relevant details from Adem Mcharek's resume and customize the content accordingly. Let's begin with the customization.Based on Adem Mcharek's resume, we will tailor the cover letter below to reflect his relevant experiences, skills, and aspirations for the Planning Engineer position at Aero Vect.

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Aero Vect}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Planning Engineer position at Aero Vect as advertised. With a Bachelor's degree in Artificial Intelligence and a solid background in machine learning, deep learning, and software engineering, I am enthusiastic about the opportunity to contribute to revolutionizing ground handling with autonomy at Aero Vect.}

\lettercontent{My experience as an AI Research Assistant, where I orchestrated an AI Research Assistant system using multi-agent technology for real-time academic literature retrieval, honed my skills in system optimization and enhancing operational efficiency – vital attributes for enhancing autonomous driving systems in structured environments.}

\lettercontent{Having developed a Convolutional Neural Network (CNN) in PyTorch for image classification and implemented a hand gesture recognition system using TensorFlow, I have proven abilities in building and optimizing intelligent systems, aligning with the core responsibilities of the Planning Engineer role at Aero Vect.}

\lettercontent{The ethos of continuous learning and collaboration at Aero Vect resonates with my experience as the Founder and President of the AI Club, where I led innovative projects and fostered a community of AI enthusiasts to tackle complex challenges collaboratively. I am eager to bring this proactive and collaborative spirit to the autonomous driving projects at Aero Vect.}

\lettercontent{Thank you for considering my application. I am excited about the opportunity to contribute to Aero Vect's mission of redefining ground handling operations with autonomous systems. I look forward to the possibility of discussing how my background, skills, and enthusiasm align with the requirements of the Planning Engineer position.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document} 

This cover letter is tailored to highlight Adem Mcharek's academic background, project experience, and leadership skills, demonstrating his suitability for the Planning Engineer role at Aero Vect.