To generate a tailored cover letter for the Machine Learning Engineer and Data Science intern position at Seismic, we will incorporate details from Adem Mcharek's resume to create a personalized and professional document. Below is the LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Seismic}
\companyaddress{
San Diego, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Machine Learning Engineer and Data Science intern position at Seismic, as advertised. With a background in STEM focusing on Machine Learning and Data Science, and a keen enthusiasm for leveraging cutting-edge technologies to drive innovation, I am excited about the opportunity to contribute to Seismic's global leadership in sales enablement.}

% Personalized content based on Adem Mcharek's experiences and skills
\lettercontent{My academic foundation in Machine Learning, AI, and Computer Science aligns perfectly with the requirements of the role at Seismic. During my studies, I have developed a solid understanding of a wide range of technologies such as AI, Generative AI, and Python libraries, which I am eager to apply in a practical setting. Additionally, my strong organizational skills and attention to detail have been instrumental in my academic projects, ensuring precision and efficiency in my work.}

% Conclusion and signature
\lettercontent{Seismic's commitment to a knowledge-sharing environment and fostering growth among its employees resonates with my values and professional aspirations. I am enthusiastic about the opportunity to collaborate with a team of experts in Machine Learning, software development, and product management to bring AI capabilities to life and enhance user experiences. I am eager to contribute to Seismic's innovative projects and immerse myself in the fast-paced world of Enterprise SaaS product development.}

\signature{Adem Mcharek}

\end{document}
```

This LaTeX code integrates Adem Mcharek's qualifications and aspirations to create a well-tailored cover letter for the Machine Learning Engineer and Data Science intern position at Seismic.