Based on the information gathered from Adem Mcharek's resume and the job details for an internship at Ultima Genomics, I will now proceed to craft a tailored cover letter for Adem Mcharek in LaTeX format. I will integrate Adem Mcharek's relevant experiences and skills to align with the requirements and responsibilities of the internship position at Ultima Genomics. 

Let's create the LaTeX cover letter using the details provided.Here is the LaTeX code for the tailored cover letter for Adem Mcharek applying to the internship position at Ultima Genomics:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Ultima Genomics}
\companyaddress{
Fremont, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager at Ultima Genomics,}

\lettercontent{I am writing to express my strong interest in the Internship position at Ultima Genomics as advertised. Currently pursuing a Bachelor's degree in Artificial Intelligence at Long Island University, where I have excelled in relevant courses such as Machine Learning, Deep Learning, and Software Engineering, I am eager to leverage my skills and experiences in a fast-paced, cutting-edge environment such as Ultima Genomics.}

\lettercontent{With a Cumulative GPA of 3.88/4.00 and hands-on experience in AI research, computer vision, and software development, including projects such as the development of an AI Research Assistant and a PyTorch CNN for MNIST, I am well-equipped to contribute effectively to the System Analytics team at Ultima Genomics. My strong analytical skills, programming proficiency in languages like Python, C++, and JavaScript, and experience with technologies like PyTorch and TensorFlow align well with the requirements of the internship role.}

\lettercontent{I am particularly drawn to Ultima Genomics' commitment to driving the scale of genomic information for advancements in biology and human health. The emphasis on technical innovation, collaboration, and impactful work resonates with my own aspirations of making a meaningful contribution in the field. I am excited about the opportunity to develop Software Quality Assurance for internal-facing analytics tools, enhance my industry knowledge, and work alongside a diverse team of experts at Ultima Genomics.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I look forward to the possibility of contributing to Ultima Genomics and being a part of a pioneering company that is transforming genomics technology.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter integrates Adem Mcharek's relevant experiences in artificial intelligence, software development, and AI research to align with the requirements and responsibilities of the internship position at Ultima Genomics.