Based on the information provided, including Adem Mcharek's resume details and the job description for the position at Skyways, I will now proceed to craft a tailored cover letter for Adem Mcharek to apply for a position at Astranis Space Technologies. Let's put together a compelling cover letter for Adem using LaTeX.

Here is the LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Astranis Space Technologies}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in joining Astranis Space Technologies, a company at the forefront of creating innovative solutions for the future of transportation. With a Bachelor's in Artificial Intelligence from Long Island University and a cumulative GPA of 3.88/4.00, I am excited about the opportunity to contribute to your team.}

% Skills and experiences relevant to the job
\lettercontent{My educational background has equipped me with a solid foundation in Artificial Intelligence and relevant coursework in programming, aligning well with the requirements of a Bachelor student in related fields with experience in programming as specified for the role at Astranis Space Technologies.}

% Personalized touch and enthusiasm
\lettercontent{I am particularly drawn to the responsibility of building a flight log parser to ensure preventative maintenance through data analysis, a task that resonates with my passion for translating complex concepts into practical solutions. My experiences have honed my analytical skills, making me well-suited to scope, design, and implement such a project effectively.}

% Closing and eagerness to contribute
\lettercontent{With a drive to deliver results, a curious mindset, and a friendly demeanor, I am confident in my ability to collaborate effectively with your engineering and flight testing teams. Additionally, my bonus experience in drones/aviation further complements my qualifications for this position. I am enthusiastic about the opportunity to contribute to Astranis Space Technologies' mission and be a part of the future of transportation.}

% Signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to Adem Mcharek's qualifications, skills, and aspirations, aligning them with the job requirements and responsibilities at Astranis Space Technologies. It emphasizes his relevant educational background, programming experience, and interest in advancing innovation in transportation technology.