Based on the job opportunity at NVIDIA for a Software Engineering internship with specific requirements and responsibilities, we will tailor a cover letter for Adem Mcharek to apply for this position. The cover letter will focus on highlighting Adem's experiences, skills, and qualifications that align with the job description provided.

Here is the refined LaTeX code for the tailored cover letter for Adem Mcharek applying for the NVIDIA internship:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{NVIDIA Corporation}
\companyaddress{
Santa Clara, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the NVIDIA Software Engineering internship position as advertised. Currently pursuing a Master's degree in a relevant field, with a solid background in Data Structures and Algorithms, Operating Systems, and Distributed Systems, I am excited about the opportunity to contribute to NVIDIA's cutting-edge projects.}

% Aligning skills and experiences with job requirements and responsibilities
\lettercontent{With a keen interest in GPU development and data science, I have actively engaged in projects involving GPGPU APIs like CUDA, along with proficient skills in C++, Python, and Unix/Shell Scripting. My experience in building GPU-accelerated AI streaming platforms aligns well with NVIDIA's focus on AI computing advancements. I am eager to leverage my technical skills to contribute to the development and optimization of GPU architectures at NVIDIA.}

% Demonstrating desired qualifications and a passion for the role
\lettercontent{Moreover, my proficiency in various technologies including GitLab, Docker, AWS, and Apache Spark, combined with a strong foundation in data processing tools, positions me well to support the software tools infrastructure at NVIDIA. I am confident in my ability to collaborate effectively with cross-functional teams and contribute meaningfully to projects that drive innovation in cloud storage infrastructure and GPU technologies.}

% Closing remarks
\lettercontent{I am excited about the prospect of contributing to NVIDIA's legacy of innovation and technological advancements. I look forward to the opportunity to further discuss how my skills and experiences align with the requirements of the internship. Thank you for considering my application.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter encapsulates Adem Mcharek's qualifications and enthusiasm for the NVIDIA Software Engineering internship, aligning his skills with the company's requirements and responsibilities. It highlights his relevant experiences and technical proficiency while expressing a genuine interest in contributing to NVIDIA's innovative projects.