Based on the information provided and the details extracted from Adem Mcharek's resume, here is a tailored cover letter in LaTeX format for the NVIDIA Computer Architecture Engineering internship opportunity:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{NVIDIA}
\companyaddress{
Santa Clara, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my sincere interest in the NVIDIA Computer Architecture Engineering internship program. With a Bachelor's degree in Artificial Intelligence from Long Island University and a strong background in machine learning, deep learning, and cloud computing, I am excited about the opportunity to contribute to NVIDIA's legacy of innovation in computer graphics, gaming, and accelerated computing.}

% Customized details and alignment with the job requirements
\lettercontent{During my tenure as an AI Research Assistant at LIU Brooklyn, I led projects utilizing cutting-edge technologies like PyTorch and TensorFlow, demonstrating my proficiency in implementing convolutional neural networks and computer vision systems. These experiences have equipped me with the necessary skills in programming languages such as Python, relevant to the internship role at NVIDIA.}

\lettercontent{My projects in AI and computer vision align closely with the responsibilities outlined for the role at NVIDIA, where designing new hardware features, crafting software for testing infrastructures, and collaborating in team settings are crucial. My exposure to cloud computing and modern cryptography further enhances my ability to contribute to advancing parallel computation and graphics algorithms within NVIDIA's architecture.}

% Conclusion and signature
\lettercontent{I am eager to bring my technical expertise and passion for innovation to the NVIDIA team. I am confident that my academic background, project experiences, and leadership in founding the "AI Club" make me a valuable candidate for the Computer Architecture Engineering internship. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter integrates Adem Mcharek's academic achievements, project experiences, and technical skills to align them with the requirements and responsibilities of the NVIDIA Computer Architecture Engineering internship. It showcases his enthusiasm for contributing to NVIDIA's innovation and technology advancements.