I have gathered the necessary information from the provided resume and cover letter examples to create a tailored cover letter for Adem Mcharek applying for a Software Testing Internship position at Astranis Space Technologies. Below is the customized LaTeX cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}
\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Astranis Space Technologies}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Software Testing Internship position at Astranis Space Technologies as advertised. With a background in Computer Science and a passion for technology, I am excited about the opportunity to contribute to creating robust software solutions at your esteemed company.}

% Main body
\lettercontent{During my academic journey, I have gained valuable experience in designing and developing unit tests for various applications, including those involving business logic and third-party API integration. My proficiency in utilizing automated build tools like Jenkins, along with my familiarity with XCTest, JUnit, and Jest for test writing and documentation, aligns well with the responsibilities outlined for the role at Astranis Space Technologies.}

\lettercontent{Furthermore, my educational background in Computer Science and Information Technology, coupled with my hands-on experience with object-oriented programming languages such as Java and C++, provide me with a solid foundation to effectively contribute to your team. I am particularly excited about the opportunity to leverage my skills in multi-threaded and concurrency programming to enhance the efficiency and reliability of software systems at Astranis.}

% Closing and signature
\lettercontent{I am keen on the prospect of collaborating with a team that values innovation and excellence, traits that are evident in Astranis Space Technologies' mission. I am confident that my technical acumen and commitment to quality align well with the objectives of the Software Testing Internship position. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to Adem Mcharek's experiences and skills, aligning them with the requirements and responsibilities of the Software Testing Internship position at Astranis Space Technologies.