Based on the information extracted from Adem Mcharek's resume and the job description for the Data Engineering Summer Internship at HP, Inc., I will now compose a tailored cover letter in LaTeX format for Adem Mcharek to apply for the internship position. Below is the customized cover letter incorporating Adem Mcharek's experiences and skills relevant to the internship opportunity:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{HP, Inc.}
\companyaddress{
Palo Alto, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Data Engineering Summer Internship position at HP, Inc. I am a highly motivated Bachelor in Artificial Intelligence student with a solid foundation in relevant courses such as Machine Learning, Deep Learning, and Cloud Computing.}

\lettercontent{My experiences as an AI Research Assistant, where I orchestrated AI projects using cutting-edge technologies like PyTorch and TensorFlow, have equipped me with valuable skills in machine learning and data analysis. Additionally, developing a Computer Vision project using TensorFlow reflects my proficiency in advanced modeling techniques and data visualization.}

\lettercontent{The opportunity to apply my classroom learnings to real-world challenges, as outlined in the internship responsibilities, greatly excites me. I am particularly drawn to HP's commitment to innovation and fostering a diverse and inclusive workplace, values that resonate with my own aspirations.}

\lettercontent{With a strong background in Python, PyTorch, TensorFlow, and data visualization tools, I am confident in my ability to contribute effectively to HP, Inc.'s cutting-edge projects and initiatives. I am excited about the chance to work on developing and testing innovative products in the field of printing technology at HP.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to Adem Mcharek's experiences and skills, aligning them with the internship position at HP, Inc. It highlights his relevant AI projects, technical proficiency, and enthusiasm for applying his knowledge in a real-world setting.