Based on the information gathered from Adem Mcharek's resume and the job requirements and responsibilities provided by Formlabs for the Algorithms Software Intern position, I will now customize a cover letter for Adem Mcharek to apply for the position. Kindly find the tailored cover letter below:

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Formlabs}
\companyaddress{
Somerville, Massachusetts
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Algorithms Software Intern position at Formlabs, a company dedicated to transforming 3D printing through digital fabrication innovation. As a Bachelor student in Artificial Intelligence at Long Island University with a solid foundation in mathematics, deep learning, and software engineering, I am thrilled about the opportunity to merge my technical skills with the cutting-edge work at Formlabs.}

% Matching qualifications and responsibilities
\lettercontent{My experience as an AI Research Assistant, developing machine learning models and optimizing algorithms, aligns well with the requirements of developing novel and performant algorithms in modern C++ for laser path planning, physics modeling, and computational geometry at Formlabs. I have a strong proficiency in C++ and have successfully implemented projects like a PyTorch CNN for image classification, showcasing my ability to work with complex algorithms efficiently.}

\lettercontent{Moreover, my background in computer vision using TensorFlow demonstrates my interest and skills in image processing algorithms, which could contribute significantly to tasks such as developing 3D rendering solutions. The responsibilities outlined, including end-to-end feature development, cross-platform desktop application development using C++17 and Qt, and a focus on maintainability and testing, resonate with my approach to software development.}

% Additional qualifications and conclusion
\lettercontent{With a passion for tackling complex problems and a keen interest in mathematics and science, I am enthusiastic about the opportunity to contribute to Formlabs' software team. I am confident that my experience in developing and optimizing low-level software, coupled with my proactive approach to learning and problem-solving, make me a suitable candidate for the Algorithms Software Intern position.}

\lettercontent{I am excited about the prospect of working at Formlabs, a company at the forefront of digital fabrication, and I am eager to bring my skills and enthusiasm to the team. Thank you for considering my application.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}