Based on the information provided about Shyft Labs and the Software Developer Intern position they are offering, we can now proceed to create a tailored cover letter for Adem Mcharek, incorporating his qualifications and experiences. We will adjust the details from his resume to align with the requirements and responsibilities of the position at Shyft Labs.

Let's integrate Adem Mcharek's information into the cover letter template following the job requirements:

---

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Shyft Labs}
\companyaddress{
Toronto, Canada
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Software Developer Intern position at Shyft Labs, as advertised. With a background in Angular.js, JavaScript, React.js, Node.js, Python, and MySQL, coupled with experience in a fast-paced environment, I am excited about the opportunity to contribute to your team and gain valuable insights from the Senior Developers and Engineers at Shyft Labs.}

% Main body: Matching qualifications and responsibilities
\lettercontent{Having worked on various software development projects, I have honed my skills in writing, modifying, and testing software code for diverse applications. My ability to innovate, maintain extensive software applications, and troubleshoot technical issues aligns well with the responsibilities outlined for the role. Furthermore, my experience in collaborating with teams, documenting user requirements, and researching software products prepares me to excel in a dynamic work environment like Shyft Labs.}

% Additional skills and closing
\lettercontent{I am particularly drawn to Shyft Labs' commitment to employee growth and the opportunity to work with Fortune 500 companies, which resonates with my career aspirations. I am eager to leverage my passion for learning, attention to detail, and strong communication skills to contribute to the innovative projects at Shyft Labs.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}

---

This cover letter integrates Adem Mcharek's skills, experiences, and aspirations to tailor a strong application for the Software Developer Intern position at Shyft Labs.