Based on the information extracted from Adem Mcharek's resume and the details provided about Raptor Maps and the job opportunity at the company, we can now proceed to customize a cover letter for Adem Mcharek to apply for a position at Raptor Maps.

Here is the tailored LaTeX cover letter for Adem Mcharek:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Raptor Maps}
\companyaddress{
Somerville, Massachusetts
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the web application development position at Raptor Maps, as advertised. With a background that includes projects optimizing algorithms and modeling for infrastructure, I am excited about the opportunity to merge my technical proficiency with the intriguing dynamics of the solar industry.}

% Skills and Experiences at Raptor Maps
\lettercontent{I have honed my skills in Python and JavaScript, essential for web application development, and I am keen on further developing my expertise in machine learning, aligning with Raptor Maps' focus on data normalization and performance enhancement across solar installations. My academic journey has equipped me with a versatile skill set, including a keen analytical acumen and a drive for delivering impactful solutions.}

% Fit with Company and Role
\lettercontent{Raptor Maps' commitment to technical advancement and industry leadership resonates with my aspirations, particularly in utilizing cutting-edge technology for climate tech solutions. The unique blend of services offered by Raptor Maps, including aerial inspections and mobile tools, aligns with my passion for renewable energy and technology.}

% Closing and Signature
\lettercontent{I am enthusiastic about the prospect of contributing to Raptor Maps' mission of enhancing solar performance and minimizing risk through innovative software solutions. I look forward to the opportunity to discuss how my skills and experiences can benefit Raptor Maps in achieving its goals.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to highlight Adem Mcharek's skills in web application development, machine learning, and his passion for climate tech, aligning them with the requirements and responsibilities of the job at Raptor Maps. It emphasizes his interest in merging technology with the solar industry and his excitement about contributing to the company's mission.