Based on the provided company overview and Adem Mcharek's resume details, I will now create a tailored cover letter for the Engineering Co-op position at Wasabi Technologies.

Here is the LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Wasabi Technologies}
\companyaddress{
Boston, Massachusetts
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Engineering Co-op position at Wasabi Technologies, a company that embodies innovation and efficiency in the cloud storage industry. As a current student pursuing a Bachelor's in Artificial Intelligence at Long Island University Brooklyn with a strong foundation in cloud computing, I am excited about the opportunity to contribute to a team dedicated to supporting highly reliable, secure, and scalable applications for Wasabi's hot cloud storage service.}

\lettercontent{My experiences as the Founder and President of the AI Club have honed my collaborative skills and ability to tackle complex projects, aligning well with the responsibilities of the role. I have a solid understanding of software design principles and proficiency in agile frameworks and languages like Python, fitting the requirements set by Wasabi Technologies.}

\lettercontent{I am particularly drawn to Wasabi's culture of embracing technological innovation and fostering a collaborative atmosphere, which resonates with my aspirations and skills. The focus on innovative scientific research and rigorous problem-solving aligns perfectly with my academic background and practical experience.}

\lettercontent{I am enthusiastic about the prospect of applying my software design and development knowledge to contribute meaningfully to Wasabi's mission of providing cost-effective and efficient cloud storage solutions. I am confident that my technical expertise and passion for cloud computing make me a strong fit for this role.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter combines Adem Mcharek's academic background in Artificial Intelligence with practical experience and aligns it with the requirements and responsibilities of the Engineering Co-op position at Wasabi Technologies, emphasizing the candidate's relevance and enthusiasm for the role.