To create a tailored cover letter for Adem Mcharek applying for the Point72 Academy Summer Internship, the information provided about Point72 Asset Management and the internship program will be integrated with Adem's details. Below is the personalized cover letter in LaTeX format:

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Point72 Asset Management}
\companyaddress{
Stamford, Connecticut
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the 8-week summer internship opportunity at the Point72 Academy, specifically designed for students graduating between December 2025 and July 2026. The values and culture of entrepreneurial thinking, continuous adaptation, and commitment to excellence at Point72 Asset Management resonate strongly with my professional aspirations and personal values.}

\lettercontent{With a background in [Adem's relevant experiences], I have honed my analytical skills and developed a keen interest in the financial services industry. The opportunity to collaborate with an investment team, receive training in accounting, modeling, and compliance, and further my knowledge under the guidance of Academy coaches aligns perfectly with my career goals in finance.}

\lettercontent{I am fascinated by research and problem-solving, traits that have been instrumental in my academic and professional success. My high levels of self-motivation, commitment to ethical standards, and relentless curiosity make me a proactive learner ready to contribute to the dynamic environment at Point72.}

\lettercontent{I am excited about the prospect of joining a firm that values diverse perspectives, encourages intellectual curiosity, and offers unparalleled growth opportunities. The chance to engage in portfolio casework, collaborate with experienced professionals, and prepare an investment pitch excites me as I aim to build a career as an equities analyst.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am eager to contribute to the Point72 Academy and learn from the industry's best to shape the future of finance. I look forward to the possibility of discussing how my skills and experiences align with the internship requirements.}

\signature{Adem Mcharek}

\end{document}

This cover letter for Adem Mcharek integrates his relevant experiences, skills, and aspirations with the requirements and insights from Point72 Asset Management's internship program, tailored to the position and company culture.