Based on the information provided about Adem Mcharek and the job opportunity at Roku, I will now craft a tailored cover letter in LaTeX format to match Adem's qualifications and aspirations for the Core Analytics Intern position at Roku.

Here is the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Roku}
\companyaddress{
San Jose, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Core Analytics Intern position at Roku, as advertised. With a background in quantitative studies and a keen passion for leveraging data to derive actionable insights, I am excited about the opportunity to contribute to Roku's pioneering work in the TV streaming industry.}

\lettercontent{My academic pursuits align closely with the requirements outlined for the role, as I am currently pursuing a Bachelor's degree in a quantitative field and I am set to graduate in December 2024. My coursework has equipped me with strong analytical skills and a foundational understanding of statistical concepts such as A/B testing and logistic regressions, which I am eager to apply to real-world problems at Roku. Additionally, my experience with SQL and handling big data, along with my proficiency in coding with R and Python, make me well-prepared to delve into Roku's enriched datasets to perform thorough analyses and develop insightful visualizations.}

\lettercontent{I am particularly drawn to the collaborative nature of the role, as I thrive in dynamic environments and enjoy partnering with cross-functional teams to address business needs through analytics. The opportunity to work closely with leadership, engineers, product managers, and data engineers at Roku to drive data-driven decisions excites me, and I am enthusiastic about contributing creatively to identify new applications for Roku's vast data catalog.}

% Conclusion and signature
\lettercontent{With a strong commitment to analytics and a drive to continuously improve and innovate, I am confident in my ability to make a valuable contribution as a Core Analytics Intern at Roku. I am excited about the prospect of working at a company that is shaping the future of television and am eager to bring my skills and enthusiasm to your team.}

\signature{Adem Mcharek}

\end{document}
```

This tailored cover letter integrates Adem Mcharek's academic background, analytical skills, and expertise in statistical concepts and data analysis to demonstrate his suitability for the Core Analytics Intern position at Roku.