Based on the provided information from Adem Mcharek's resume and the job description for the Data Science Intern position at Hitachi Vantara, I will now create a customized cover letter in LaTeX format tailored to Adem Mcharek's experiences and skills for the mentioned job opportunity. 

Please find the tailored LaTeX cover letter below:

\documentclass[]{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}
\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Hitachi Vantara}
\companyaddress{
Santa Clara, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Data Science Intern position at Hitachi Vantara, a company I admire for its dedication to leveraging data for growth and innovation. As a current Bachelor in Artificial Intelligence student at Long Island University, with a strong background in machine learning, deep learning, and relevant technical courses, I am excited about the opportunity to contribute to impactful projects within your organization.}

\lettercontent{My experiences, such as orchestrating an AI Research Assistant using AUTOGEN's multi-agent system and developing projects like PyTorch CNN for MNIST and Computer Vision using TensorFlow, have equipped me with the technical skills necessary to excel in machine learning-focused use cases. I have a proven track record of optimizing algorithms and implementing neural network architectures, showcasing my ability to translate complex concepts into practical solutions.}

\lettercontent{I am particularly drawn to the responsibilities of understanding the Pentaho Plus Data Ops Platform, defining machine learning use cases, and evaluating models as outlined in the job description. My passion for learning, attention to detail, and strong problem-solving skills align well with the requirements set by Hitachi Vantara.}

\lettercontent{Moreover, my leadership experience as the Founder and President of the "AI Club" demonstrates my ability to foster a collaborative environment and drive innovative projects across AI disciplines. I am eager to bring this leadership and hands-on experience to Hitachi Vantara and contribute to the digital transformation initiatives within your esteemed organization.}

\lettercontent{I am excited about the opportunity to work at Hitachi Vantara, a company that values innovation, collaboration, and societal impact. I am confident that my technical skills, creativity, and curiosity for learning make me a strong candidate for the Data Science Intern role.}

\lettercontent{Thank you for considering my application. I look forward to the possibility of contributing to the continued success and innovation at Hitachi Vantara.}

\signature{Adem Mcharek}
\end{minipage}

\end{document}

This cover letter is tailored to highlight Adem Mcharek's experiences, skills, and aspirations in line with the requirements and responsibilities of the Data Science Intern position at Hitachi Vantara. It emphasizes his technical proficiency, project experiences, leadership skills, and alignment with Hitachi Vantara's values of innovation and collaboration.