Based on the information provided in Adem Mcharek's resume and the job description for the Software Engineering Intern position at Chime, we can now proceed to create a tailored cover letter for Adem Mcharek to apply for the internship at Chime. Below is the LaTeX code for the personalized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Chime}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Software Engineering Intern position at Chime. Currently pursuing a Bachelor's degree in Computer Science, with hands-on experience as an AI Research Assistant and a background in Computer Vision using TensorFlow, I am excited about the opportunity to work alongside an experienced engineering team at Chime.}

\lettercontent{My role as the Founder and President of the "AI Club" showcases my leadership and organizational skills, aligning with the requirement for strong organizational and analytical abilities. Moreover, my experience in AI research and computer vision projects has equipped me with the technical proficiency necessary to contribute effectively to Chime's Cards Experience Team. }

\lettercontent{I am particularly drawn to Chime's innovative approach to online banking and its commitment to providing financial peace of mind to everyone. The chance to participate in the full software development lifecycle, collaborate with cross-functional teams, and work with technologies like Ruby on Rails, JavaScript, and React Native is both challenging and rewarding.}

\lettercontent{With a passion for consumer FinTech, a creative and self-starting mindset, and a willingness to tackle complex projects head-on, I am eager to leverage my skills in a fast-paced and dynamic environment like Chime. I am confident that my background and aspirations align well with the responsibilities and desired qualifications for the Software Engineering Intern role.}

\lettercontent{Thank you for considering my application. I look forward to the possibility of contributing to Chime’s critical initiative and gaining valuable professional experience within your esteemed organization.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter integrates Adem Mcharek's academic background, skills, and experiences from the provided resume with the specific requirements and responsibilities outlined for the Software Engineering Intern position at Chime.