To create a tailored cover letter for Adem Mcharek applying for a position at Roku, I will extract relevant details from his resume and the provided job description. Then, I will incorporate this information into the LaTeX cover letter template. Let's begin by reviewing the details from Adem Mcharek's resume and the job requirements:

### Adem Mcharek's Details:
- **Name:** Adem Mcharek
- **Email:** adem.mcharek@my.liu.edu
- **Phone:** +1 929-527-4331
- **LinkedIn:** [adem-mcharek](https://linkedin.com/in/adem-mcharek)
- **GitHub:** [adem-mcharek](https://github.com/adem-mcharek)
- **Education:** Computer Science, expected graduation May 2023

### Job Requirements:
1. Excellent Python skills
2. Experience with C/C++
3. Experience with Gitlab build, test, and automation
4. Experience developing on embedded platforms
5. Bachelor’s/Master’s in Computer Science/Computer Engineering/Electrical Engineering or equivalent

Now, I will proceed with integrating this information into the LaTeX cover letter template.Based on the information extracted from Adem Mcharek's resume and the provided job details at Roku, I will now proceed to create a tailored cover letter for Adem Mcharek applying for the position at Roku.

### LaTeX Cover Letter for Adem Mcharek:

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Roku}
\companyaddress{
San Jose, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the opportunity to join Roku as a Software Engineer, as advertised. With a solid educational background in Computer Science, ongoing at present, and a keen interest in embedded systems and automation, I am excited about the prospect of contributing to Roku's innovative work environment.}

\lettercontent{My experiences align closely with the requirements for the role, including my proficiency in Python, C/C++, and Gitlab for build, test, and automation. I have also worked on projects involving embedded platforms during my studies, providing me with the necessary skills to excel in developing automated test software for remotes at Roku.}

\lettercontent{Furthermore, I am eager to collaborate with senior software engineers at Roku, bringing my technical skills and proactive approach to enhancing testing processes. I believe that my ability to translate complex technical concepts into practical solutions, coupled with my dedication to quality assurance, make me a suitable fit for this position.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}

This LaTeX cover letter integrates Adem Mcharek's skills and experiences with the specific job requirements at Roku, showcasing his suitability for the Software Engineer position.