Based on the provided details about the job opportunity at Roku and Adem Mcharek's resume, we can craft a tailored cover letter for Adem to apply for a position in the voice and edge machine learning team at Roku. Below is the LaTeX code for the cover letter:

```latex
\documentclass[]{cover}
\usepackage{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Roku}
\companyaddress{
San Jose, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the position within the voice and edge machine learning team at Roku, as advertised. With a background that aligns closely with the requirements and responsibilities outlined, I am excited about the opportunity to contribute to Roku's mission of revolutionizing TV streaming platforms globally.}

\lettercontent{Throughout my academic and professional journey, I have honed my Python skills and gained hands-on experience in cloud services, especially with Amazon Web Services. My proficiency extends to technologies like Docker, SQL, and Tensorflow Lite. I have actively participated in developing machine learning model data pipelines and have a proven track record in creating machine learning models tailored for embedded platforms. My educational background in Computer Science provides a solid foundation to support these technical skills effectively.}

\lettercontent{I am particularly enthusiastic about the chance to work on the edge machine learning pipeline at Roku, collaborating on the development of innovative machine learning models for new products. My passion for cutting-edge technologies and my ability to work effectively within dynamic teams make me well-suited to contribute meaningfully to Roku's initiatives.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am eager to bring my skills and dedication to the voice and edge machine learning team at Roku, contributing to the continued success and growth of a company that is transforming the TV streaming landscape.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to Adem Mcharek's experiences and qualifications, highlighting his relevant skills and aligning them with the requirements and responsibilities of the position at Roku.