Based on the information provided in Adem Mcharek's resume and the internship opportunity at Five9, here is a tailored cover letter:

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Five9 Internship Program}
\companyaddress{
San Ramon, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Internship Program at Five9, a leading provider of cloud contact center software. As a dedicated student pursuing a Bachelor's in Artificial Intelligence with a strong foundation in machine learning and deep learning frameworks, including hands-on experience in AI research and development, I am excited about the opportunity to contribute to real-world projects at Five9 this summer.}

\lettercontent{My academic background, which includes projects such as developing AI solutions like the AI Research Assistant and implementing machine learning models like the PyTorch CNN for MNIST, has equipped me with the skills to tackle complex problems with innovative solutions. I am particularly drawn to the prospect of researching advanced analytics use cases in contact centers and building machine learning models to optimize contact center operations at Five9.}

\lettercontent{With a solid understanding of SQL, BI tools, and modern AI frameworks like PyTorch and TensorFlow, I am well-prepared to collaborate with engineering teams, procure and analyze customer datasets, and present actionable insights to senior leaders. My experience in leading the AI Club and my achievements in mathematical competitions showcase my leadership and problem-solving abilities, which I am eager to apply to the challenges at Five9.}

\lettercontent{I am excited about the opportunity to contribute to the innovative projects at Five9, learn from industry experts, and grow both professionally and personally through this internship program. I am confident that my technical skills, analytical mindset, and passion for AI will make me a valuable asset to the Product Management department at Five9.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document} 