Based on the information provided about Adem Mcharek and the job opportunity at CACI International Inc for a Cyber Engineering Intern position, I will now craft a tailored cover letter in LaTeX format using the details from Adem Mcharek's resume provided earlier. 

Let's commence with the customization of the cover letter.I have extracted relevant information from the documents. Now, I will proceed with crafting the cover letter tailored to Adem Mcharek for the Cyber Engineering Intern position at CACI International Inc, incorporating his background, experiences, and aspirations into the text. Let's begin with the customization.\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{CACI International Inc}
\companyaddress{
Reston, Virginia
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am excited to express my interest in the Cyber Engineering Intern position at CACI International Inc, a renowned company dedicated to national security and government modernization. Currently pursuing a Bachelor's degree in Artificial Intelligence, my academic background exposes me to a diverse set of skills that align with the requirements of the role, including development experience in Python, Java, and C/C++, maintaining a strong GPA, and a passion for cybersecurity.}

\lettercontent{My academic journey, focusing on Applied Mathematics and Artificial Intelligence, has equipped me with the ability to translate complex concepts into practical solutions. Projects optimizing algorithms and modeling for various applications have honed my analytical skills and problem-solving mindset. I am thrilled about the prospect of partnering with CACI's cyber leaders to gain hands-on experience and delve into themes that require thinking like an adversary, such as red teaming and penetration testing.}

\lettercontent{Moreover, my proficiency in Python and Java, coupled with a strong foundation in computer science, positions me well to contribute effectively to creating Capture The Flag challenges and developing infrastructure to support penetration testing projects. I am eager to explore the world of adversarial tools, techniques, and procedures, and deepen my understanding of embedded Internet of Things devices and virtualization technologies.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}The cover letter tailored for Adem Mcharek for the Cyber Engineering Intern position at CACI International Inc has been crafted in LaTeX format. It integrates Adem's academic background, skills, and enthusiasm for cybersecurity. Please let me know if any further adjustments are needed.