Based on the information extracted from Adem Mcharek's resume and the provided job details at Arrowhead Pharmaceuticals, Inc., I will now proceed to craft a tailored cover letter for Adem Mcharek applying for the Intern for Research Informatics position at Arrowhead Pharmaceuticals.

Here is the LaTeX code for the personalized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Arrowhead Pharmaceuticals, Inc.}
\companyaddress{
Pasadena, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Intern for Research Informatics position at Arrowhead Pharmaceuticals, Inc. With a Bachelor's degree in Artificial Intelligence from Long Island University and a demonstrated background in cutting-edge technologies and AI research, I am enthusiastic about the opportunity to contribute to Arrowhead's innovative approach to developing targeted therapies.}

\lettercontent{My involvement as an AI Research Assistant at LIU Brooklyn, where I orchestrated an AI Research Assistant using multi-agent systems for real-time academic literature retrieval, has honed my skills in generating actionable insights from data. Through projects like developing a PyTorch CNN for MNIST and creating a Computer Vision system using TensorFlow, I have showcased my proficiency in machine learning and data analysis, skills directly applicable to the responsibilities of generating reports and enhancing platforms at Arrowhead.}

\lettercontent{With a fluent proficiency in French, strong problem-solving abilities, and a passion for learning new techniques, I am well-equipped to contribute effectively to Arrowhead's Research Informatics team. I am especially drawn to Arrowhead's focus on RNA interference mechanisms and the potential to revolutionize treatment paradigms for genetic diseases through targeted therapies.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am excited about the opportunity to bring my technical skills and enthusiasm for research informatics to Arrowhead Pharmaceuticals, Inc. I look forward to the possibility of contributing to your transformative projects.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter integrates Adem Mcharek's educational background, project experiences, skills, and aspirations with the specific requirements and responsibilities of the Intern for Research Informatics position at Arrowhead Pharmaceuticals, Inc.