Based on the information provided and Adem Mcharek's resume, I will now craft a tailored cover letter for the position at Roku incorporating his relevant experiences and skills.

Here is the LaTeX code for the customized cover letter:

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Roku}
\companyaddress{
San Jose, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Core Analytics Intern (Ads) position at Roku, a company at the forefront of revolutionizing TV streaming platforms worldwide. With a Bachelor's in Artificial Intelligence from Long Island University and a robust background in machine learning, deep learning, and data analysis, I am excited about the opportunity to leverage my technical skills and passion for analytics at Roku.}

\lettercontent{During my tenure as an AI Research Assistant at LIU Brooklyn, I led projects that involved real-time academic literature retrieval and the development of advanced mathematical computations, showcasing my ability to translate complex concepts into tangible solutions. My experience in developing a PyTorch CNN for image classification and a hand gesture recognition system using TensorFlow aligns well with the analytical requirements at Roku.}

\lettercontent{I am particularly drawn to Roku's emphasis on using enriched datasets for in-depth analysis and developing data visualizations to illustrate platform phenomena. My proficiency in R, Python, SQL, and working with big data, combined with a strong foundation in statistical concepts such as A/B testing and logistic regressions, positions me well to contribute effectively to new product launches and business needs at Roku.}

\lettercontent{I am enthusiastic about the opportunity to work alongside Roku's diverse teams and contribute to innovative projects that push boundaries in the TV streaming industry. I am confident that my analytical skills, project management capabilities, and passion for data-driven insights make me a valuable candidate for the Core Analytics Intern (Ads) role at Roku.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}

This cover letter combines Adem Mcharek's educational background, project experiences, technical skills, and alignment with the requirements and responsibilities of the Core Analytics Intern position at Roku. It demonstrates his enthusiasm for the role and the potential contributions he can make to Roku's data analytics team.