Based on the information provided about Rivian and the internship opportunity, we will now proceed to create a tailored cover letter in LaTeX format for Adem Mcharek to apply for the Internship position at Rivian. We will integrate Adem's qualifications, experiences, and aspirations into the cover letter using the details provided. Let's create the customized cover letter accordingly.Based on Adem Mcharek's resume and the details provided about the internship position at Rivian, here is the tailored cover letter in LaTeX format:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Rivian}
\companyaddress{
Irvine, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Internship position at Rivian as advertised. With a Bachelor's degree in Artificial Intelligence from Long Island University and hands-on experience in AI research and development, I am excited about the opportunity to contribute to Rivian's innovative projects.}

\lettercontent{My involvement as an AI Research Assistant, where I led the development of AI systems for real-time academic literature retrieval and implemented Convolutional Neural Networks for image classification, has equipped me with the skills in embedded platform architecture, Python, and C programming, aligning well with the requirements of the position at Rivian.}

\lettercontent{I am particularly drawn to Rivian's dedication to environmental sustainability and technical precision in the automotive industry. My background in AI, machine learning, and software engineering, coupled with a passion for cutting-edge technologies, positions me well to support Rivian's mission of innovation and global impact.}

\lettercontent{I am enthusiastic about the opportunity to contribute to the design and implementation of a Software Application Framework at Rivian, working collaboratively with peers and stakeholders to address hardware and software challenges. My experience in project leadership and problem-solving, including winning accolades in international competitions, reflects my commitment to excellence and innovation.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am eager to bring my skills and enthusiasm to the Electrical Hardware team at Rivian and contribute to the company's pioneering initiatives.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter integrates Adem Mcharek's educational background, project experiences, leadership roles, and technical skills to align with the internship requirements at Rivian. It emphasizes his suitability for the position and his enthusiasm for contributing to Rivian's innovative projects.