Based on the information from Adem Mcharek's resume and the job requirements and responsibilities at Gametime, here is a tailored cover letter for Adem Mcharek to apply for the Data Engineering Intern position at Gametime:

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Gametime}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Data Engineering Intern position at Gametime, a company dedicated to creating memorable live experiences through innovative technology. As a current Bachelor's student in Computer Science with a strong foundation in technical skills and a passion for data engineering, I am excited about the opportunity to contribute to building and optimizing data pipelines at Gametime.}

% Relevant experiences and skills
\lettercontent{My academic background and projects, including optimizing algorithms and modeling for real-world applications, have equipped me with the ability to tackle complex data challenges efficiently. I have a solid proficiency in SQL and Python, essential for writing advanced queries and scripts for data manipulation. Moreover, my familiarity with cloud platforms, particularly AWS, complements my understanding of cloud services and infrastructure relevant to data engineering.}

% Fit with responsibilities
\lettercontent{The responsibilities outlined for the role, such as developing scalable data pipelines using Apache Airflow, Python, and SQL to ensure efficient data integration across AWS and Snowflake environments, resonate with my technical abilities and interests. I am eager to collaborate with cross-functional teams to implement data engineering solutions that drive data-driven decision-making at Gametime.}

% Closing and aspiration
\lettercontent{I am particularly drawn to Gametime's commitment to innovative solutions and data-driven decision-making, aligning with my aspirations for continuous learning and problem-solving in a dynamic environment. I am excited about the prospect of contributing to the data infrastructure at Gametime, ensuring data quality and accessibility to drive impactful projects.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}