Based on the information from Adem Mcharek's resume and the job description for the Intern position at Chime's Funding Habits team, we can create a tailored cover letter for Adem Mcharek. Below is the LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{plain}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Chime}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Intern position at Chime's Funding Habits team, as advertised. Currently pursuing a Bachelor's degree in Artificial Intelligence at Long Island University, I have developed a solid foundation in relevant subjects such as Machine Learning, Deep Learning, and Software Engineering, achieving a Cumulative GPA of 3.88/4.00.}

\lettercontent{With a passion for consumer FinTech and a drive to dive into the deepest levels of technology, I am excited about the opportunity to apply my knowledge and skills in a real-world setting at Chime. The chance to work alongside experienced engineers in designing, developing, and scaling systems aligns perfectly with my career aspirations.}

% Aligning skills and responsibilities
\lettercontent{During my academic journey, I have undertaken projects that involved translating complex mathematical concepts into practical solutions, showcasing my ability to analyze and solve real-world problems. The responsibilities outlined, such as participating in the full software development lifecycle, collaborating with cross-functional teams, and learning new technologies, resonate with my experiences and aspirations.}

% Closing and signature
\lettercontent{I am confident that my strong analytical skills, passion for learning, and adaptability make me a suitable candidate for this role at Chime. I am eager to contribute to Chime's mission of providing financial peace of mind through innovative solutions. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter combines Adem Mcharek's educational background in Artificial Intelligence, passion for technology, and interest in consumer FinTech with the responsibilities and requirements outlined in the Intern position at Chime's Funding Habits team. It aligns his skills and experiences with the desired qualifications and responsibilities for the role, making a compelling case for his candidacy.