Based on the information provided and Adem Mcharek's resume, I will now draft a tailored cover letter for the position at Vestmark based on the requirements and responsibilities mentioned for a Software Engineer Intern role requiring Java development and relational database experience. 

Here is a customized LaTeX cover letter for Adem Mcharek to apply at Vestmark:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Vestmark}
\companyaddress{
Wakefield, Massachusetts
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Software Engineer Intern position at Vestmark. As a highly motivated Computer Science student with a Bachelor's in Artificial Intelligence and a strong foundation in Java development, I am excited about the opportunity to contribute to Vestmark's innovative technology solutions.}

\lettercontent{During my academic journey, I have undertaken diverse projects, including AI research assistant roles, developing PyTorch CNN for MNIST, and working on computer vision projects using TensorFlow. These experiences have honed my Java coding skills, object-oriented design proficiency, and relational database expertise, aligning well with the requirements of the Software Engineer Intern role at Vestmark.}

\lettercontent{I am particularly intrigued by the chance to engage in hands-on software development for Vestmark's financial services applications, such as Portfolio Trading and Proposal Generation. My experience in collaborating within agile scrum teams and my commitment to continuous learning make me well-suited to thrive in Vestmark's dynamic environment.}

\lettercontent{Moreover, my achievements in algorithmic design, my proven analytical skills, and my track record of problem-solving reflect my readiness to contribute effectively to Vestmark's projects. I am eager to leverage my technical curiosity and passion for technology to support Vestmark's core values and contribute to the growth of the team.}

\lettercontent{I am enthusiastic about the opportunity to bring my skills and dedication to Vestmark and contribute to the development of innovative wealth management applications. Thank you for considering my application.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter emphasizes Adem Mcharek's relevant experiences in Java development and databases, aligning them with the requirements and responsibilities of the Software Engineer Intern position at Vestmark.