Based on the information provided about the job opportunity at First American, I will now draft a tailored cover letter for Adem Mcharek to apply for the internship position in the Information Security division at First American. I will integrate details from Adem Mcharek's resume and experiences into the cover letter.

Here is the LaTeX code for the cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{First American}
\companyaddress{
Santa Ana, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the internship opportunity within the Information Security division at First American, as advertised. With a background in Computer Science and Cybersecurity, coupled with hands-on experience in Java Script, React, and multiple programming languages, I am excited about the prospect of contributing to a renowned company like First American.}

\lettercontent{During my academic journey, I have honed my technical skills and developed a profound interest in application security. The responsibilities outlined for this internship align perfectly with my aspiration to apply my knowledge in a real-world setting. My proactive nature, ability to communicate effectively, and keen attention to detail make me well-equipped to collaborate with stakeholders, identify security vulnerabilities, and recommend robust remediation measures.}

\lettercontent{Moreover, I am eager to delve into the realms of Mortgage, Real Estate, Financial, and Title Insurance industries, demonstrating a strong willingness to learn and adapt. I am particularly drawn to the opportunity to work alongside professionals in a people-first culture, fostering an environment of inclusivity and innovation.}

% Conclusion and signature
\lettercontent{I am confident that my technical background, problem-solving abilities, and dedication to continuous learning make me a suitable candidate for this internship role. I am enthusiastic about the possibility of contributing to First American and look forward to the opportunity to discuss how my skills and experiences align with the company's mission.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored specifically for Adem Mcharek's application for the internship position at First American, highlighting his skills, experiences, and aspirations that are relevant to the job requirements and company culture.