Based on the provided information from Adem Mcharek's resume and the job details for the position at Intel, let's customize a cover letter for Adem Mcharek to apply for the AI Software Engineering Intern position at Intel. Below is the tailored cover letter in LaTeX format:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Intel Corporation}
\companyaddress{
Santa Clara, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the AI Software Engineering Intern position at Intel. As a current student pursuing a Bachelor in Artificial Intelligence at Long Island University with a robust background in machine learning, deep learning, statistics, and software engineering, I am thrilled about the opportunity to contribute to Intel's mission of creating world-changing technology through innovative AI applications.}

\lettercontent{My experiences as an AI Research Assistant, where I developed AI solutions using PyTorch and TensorFlow, align closely with the responsibilities outlined for the role at Intel. Leading model development, optimizing AI applications, and collaborating with diverse teams are areas where I have excelled and am eager to further enhance my skills.}

\lettercontent{With a solid foundation in AI frameworks such as PyTorch and TensorFlow, combined with practical experience in Large Language Models and Generative AI, I am well-prepared to contribute to Intel's cutting-edge projects in AI development and optimization. The opportunity to work on infrastructure optimizations and build end-to-end AI applications at Intel excites me, and I am confident in my ability to deliver impactful results.}

% Conclusion and signature
\lettercontent{I am particularly drawn to Intel's commitment to technological innovation and collaborative culture, which I believe perfectly align with my aspirations and skills. I am enthusiastic about the chance to leverage my technical proficiency and passion for AI to contribute to Intel's groundbreaking initiatives. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter merges Adem Mcharek's experiences, skills, and aspirations with the specific requirements and expectations outlined for the AI Software Engineering Intern position at Intel. It emphasizes his background in AI research, proficiency in relevant frameworks, and his eagerness to contribute to Intel's innovative projects in artificial intelligence.