Based on the provided information and Adem Mcharek's resume, I will now proceed with crafting a tailored cover letter for him applying for the software engineering position at Cadence Design Systems. 

Below is the LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Cadence Design Systems}
\companyaddress{San Jose, California}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the software engineering position at Cadence Design Systems, a company renowned for its innovative solutions and commitment to excellence. With a Bachelor's in Artificial Intelligence and a proven track record in AI research and development showcased through projects utilizing technologies like PyTorch and TensorFlow, I am enthusiastic about the opportunity to contribute to the cutting-edge software solutions developed at Cadence.}

% Aligning with Cadence's requirements and responsibilities
\lettercontent{At Long Island University, I have honed my skills in machine learning, Python, and deep learning libraries like PyTorch and TensorFlow, aligning with Cadence's requirements. My experience in collaborating with AI professionals and leading AI-focused initiatives positions me well to work on complex problems to develop software for product design and verification at advanced nodes, as outlined in the responsibilities at Cadence.}

% Showcasing additional qualifications and enthusiasm for the role
\lettercontent{Furthermore, my proficiency in C/C++, object-oriented programming, and familiarity with UNIX/Linux platforms, along with a solid foundation in design patterns, algorithms, and data structures, make me a strong fit for the role at Cadence. I am excited about the opportunity to leverage my technical skills and problem-solving abilities to contribute to Cadence's Intelligent System Design strategy and be part of a team dedicated to technological innovation.}

% Closing the cover letter
\lettercontent{I am eager to bring my technical expertise, analytical skills, and passion for innovation to Cadence Design Systems. Thank you for considering my application. I look forward to the possibility of contributing to Cadence's mission of transforming design ideas into tangible products.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter integrates Adem Mcharek's academic background, technical skills, and project experiences to align with the requirements and responsibilities of the software engineering position at Cadence Design Systems. Adjustments can be made as needed to further tailor the content to Adem Mcharek's preferences and experiences.