Based on the information provided in Adem Mcharek's resume and the job description for the Software Development Engineer in Test position at Shark Ninja Robotics, we can tailor a cover letter for him to apply for this opportunity. Below is the LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Shark Ninja Robotics}
\companyaddress{
Needham, Massachusetts
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Software Development Engineer in Test position at Shark Ninja Robotics. With a strong foundation in Artificial Intelligence and hands-on experience in developing and implementing AI solutions, I am excited about the opportunity to merge my technical skills with the intricate dynamics of robotic products testing at your esteemed company.}

\lettercontent{My academic background at Long Island University, where I have excelled in courses such as Machine Learning, Data Mining, and Software Engineering, has equipped me with a solid understanding of the technologies relevant to this role. Additionally, my projects, such as the AI Research Assistant using multi-agent systems and developing CNN models in PyTorch, demonstrate my proficiency in automation and software testing.}

\lettercontent{I am particularly drawn to Shark Ninja Robotics' commitment to innovation and customer satisfaction. The responsibilities outlined for this role, from reviewing product requirements to developing automated test scripts, resonate with my experience and aspirations in the field of software engineering and AI testing.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter is personalized to Adem Mcharek's qualifications, experiences, and aspirations, aligning them with the requirements and responsibilities of the Software Development Engineer in Test position at Shark Ninja Robotics.