Based on Adem Mcharek's resume and the job description for the Data Engineering Intern position at Recorded Future, here is a customized cover letter in LaTeX format:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Recorded Future}
\companyaddress{
Somerville, Massachusetts
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Data Engineering Intern position at Recorded Future. With a Bachelor's in Artificial Intelligence from Long Island University and a strong passion for utilizing technology to solve complex problems, I am eager to contribute to your mission of empowering organizations with real-time threat intelligence.}

\lettercontent{My academic background and hands-on projects, such as developing a PyTorch CNN for classifying handwritten digits and creating a hand gesture recognition system using TensorFlow, have equipped me with the Python programming and data skills necessary for this role. My experiences in AI research and computer vision have honed my ability to work with large, complex data structures, a skill vital for implementing techniques to harvest credentials on the dark web.}

\lettercontent{I am particularly drawn to Recorded Future's innovative approach in the cybersecurity and intelligence fields, and I am excited about the opportunity to learn from experienced professionals while contributing to the Security Intelligence graph. My attention to detail and excellent communication skills, as demonstrated in my project collaborations and leadership roles, align well with the responsibilities of the position.}

\lettercontent{I believe that my technical expertise, coupled with my drive for continuous learning and innovation, make me a strong fit for the Data Engineering Intern role at Recorded Future. I am eager to bring my unique perspective and contribute to a company that values high standards, inclusion, and ethical practices.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter incorporates Adem Mcharek's educational background, relevant projects, skills, and aspirations, aligning them with the requirements and responsibilities of the Data Engineering Intern position at Recorded Future. Feel free to adjust any details or formatting according to your preferences.