Based on the detailed information provided about Curai Health and the specific job opportunity at Curai Health for an AI Data Engineering Intern, I will now generate a tailored cover letter for Adem Mcharek to apply for this position. 

Here is the LaTeX code for the customized cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Curai Health}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the AI Data Engineering Intern position at Curai Health as advertised. With a strong foundation in computer science and a keen interest in leveraging AI technology to enhance healthcare experiences, I am excited about the opportunity to contribute to Curai Health's innovative approach to virtual primary care.}

\lettercontent{My academic background in computer science, combined with hands-on experience in working with distributed compute and managing large datasets, aligns well with the requirements outlined for the role. I have a solid understanding of data structures, algorithms, and software engineering principles, which I believe are essential for designing and implementing scalable data pipelines, supporting ML system evaluation, and contributing to technical decision-making.}

\lettercontent{Having a growth mindset, enjoying problem-solving in a data-driven manner, and thriving in ambiguous situations are qualities that I possess and have successfully demonstrated in my academic projects and internships. I am particularly enthusiastic about the opportunity to collaborate with a team of experienced engineers at Curai Health to shape the future of data pipelines effectively.}

\lettercontent{Moreover, my strong communication skills, honed through various team projects and presentations, will enable me to effectively engage with the AI and engineering teams at Curai Health. I am excited about the possibility of gaining hands-on experience in optimizing data pipelines and contributing to impactful AI/automation technologies that directly enhance patient care quality.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am eager to bring my technical expertise, passion for AI-driven healthcare solutions, and dedication to improving patient outcomes to the AI Data Engineering Intern role at Curai Health. I am looking forward to the opportunity to discuss how my background, skills, and aspirations align with the vision and goals of Curai Health.}

\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to Adem Mcharek's qualifications, experiences, and aspirations, focusing on how they meet the requirements and responsibilities of the AI Data Engineering Intern position at Curai Health.