Based on the information provided in Adem Mcharek's resume, we can tailor a cover letter for the position at Shark Ninja. Considering Adem's background in Artificial Intelligence, machine learning, deep learning, software engineering, and relevant projects, we will craft a personalized cover letter showcasing his skills and experiences in alignment with the job requirements and responsibilities at Shark Ninja. 

Here is the customized LaTeX cover letter for Adem Mcharek applying to the position at Shark Ninja:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Shark Ninja}
\companyaddress{
Needham, Massachusetts
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Software Development Engineer in Test position at Shark Ninja, as advertised for the Fall Co-op or Post-graduate Internship. With a Bachelor's degree in Artificial Intelligence from Long Island University Brooklyn and a passion for innovative technology solutions, I am excited about the opportunity to contribute to Shark Ninja's mission of impacting people's lives with high-quality products.}

% Match skills and experiences with requirements and responsibilities
\lettercontent{My academic background and projects have equipped me with software programming experience in Python, knowledge of the Software Development and Testing Life Cycles, and meticulous attention to detail. Specifically, my projects, such as orchestrating an AI Research Assistant for real-time academic literature retrieval and developing a PyTorch CNN for image classification, have honed my abilities to write and review automated test scripts using Python, JavaScript, and Linux shell scripts.}

\lettercontent{Moreover, my experience in developing automation tools and utilities for testing frameworks aligns well with the responsibility to extend and enhance automation test frameworks at Shark Ninja. I have also worked in lab environments, collaborated on team projects, and demonstrated a commitment to excellence through my academic achievements, including a cumulative GPA of 3.88/4.00.}

% Closing and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter combines Adem Mcharek's academic background, project experiences, and skills with the specific requirements and responsibilities of the Software Development Engineer in Test position at Shark Ninja, presenting a tailored application for the role.