Based on the provided information about Acorns and the job opportunity at the company, I will now draft a personalized cover letter for Adem Mcharek to apply for the Software Engineering Intern position at Acorns. I will incorporate Adem's skills, experiences, and aspirations into the cover letter to align with the requirements and responsibilities of the role.

I will integrate the required qualifications and responsibilities outlined by Acorns, emphasizing Adem's proficiency and enthusiasm for artificial intelligence, problem-solving skills, communication abilities, and commitment to personal and professional growth.

Let's proceed with crafting the tailored cover letter for Adem Mcharek:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Acorns}
\companyaddress{
Irvine, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Software Engineering Intern position at Acorns as advertised. As a dedicated and aspiring software engineer, with a solid background in programming and a genuine passion for artificial intelligence, I am thrilled about the opportunity to contribute to innovative projects at Acorns and further develop my skills in this dynamic field.}

% Aligning qualifications with requirements
\lettercontent{With anticipated graduation in June 2025 and proficiency in Python and Java, among other languages, I am equipped to tackle the challenges posed by artificial intelligence-powered tool projects. My understanding of data structures, algorithms, and software design principles, combined with my experience with version control systems like Git, align well with the technical requirements specified by Acorns.}

% Showcasing skills and attitude alignment
\lettercontent{Moreover, my strong problem-solving skills, proactive approach to challenges, and excellent communication abilities enable effective collaboration within teams, guiding me towards always building trust and making bold decisions when necessary. I am eager to immerse myself in Acorns' mission-driven team, contribute meaningfully to the optimization of AI tools, and engage in the vibrant professional network within the industry.}

% Closing statement
\lettercontent{I am excited about the opportunity to grow both personally and professionally at Acorns, embodying the values of leading with heart, continuous growth, and finding a way to make impactful contributions. I am confident that my enthusiasm for AI and dedication to excellence align closely with Acorns' culture and vision.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to highlight Adem Mcharek's qualifications and enthusiasm for the Software Engineering Intern position at Acorns, aligning with the company's values and requirements. Please let me know if any further adjustments are needed.