
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Wisk Aero}
\companyaddress{
Mountain View, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Information Technology intern position at Wisk Aero as advertised. With a strong educational background in computer systems and a passion for technology, I am excited about the opportunity to contribute to Wisk's mission of transforming urban mobility through autonomous flight.}

% Highlighting relevant experiences and skills
\lettercontent{During my academic pursuits in Computer and Information Systems, I have gained hands-on experience with Cloud SaaS applications and computer troubleshooting, aligning well with the requirements for the role at Wisk Aero. My ability to analyze data, provide metrics on environments, and familiarity with scripting languages make me a suitable candidate for supporting problem-solving activities and coordinating application roll-outs.}

% Expressing alignment with company values and goals
\lettercontent{I am drawn to Wisk's commitment to sustainable urban mobility and its innovative approach to solving complex technical challenges. I am eager to contribute to building the first autonomous all-electric aircraft, working alongside a passionate team dedicated to making everyday flight accessible to all individuals.}

% Closing and signature
\lettercontent{Thank you for considering my application. I am confident that my technical skills, coupled with my self-motivation and problem-solving abilities, would make me a valuable addition to the Wisk Aero team. I look forward to the possibility of discussing how my background aligns with the goals of Wisk Aero.}

\signature{Adem Mcharek}

\end{document}
