Based on the information provided from the resume and the job description at Wise, I will now draft a tailored cover letter in LaTeX format for Adem Mcharek applying for the Data Science Intern position at Wise for the 10-week internship from June 24th to August 30th, 2024.

Here is the crafted cover letter:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Wise}
\companyaddress{
London, United Kingdom
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Data Science Intern position at Wise, as advertised for the 10-week internship from June 24th to August 30th, 2024. The opportunity to work on real data science projects using up-to-date machine learning techniques at a globally recognized company like Wise excites me.}

\lettercontent{With a solid educational background in Computer Science and Applied Mathematics, including projects optimizing algorithms and modeling, I have honed my skills in translating complex concepts into practical solutions. My experience aligns with the responsibilities outlined, such as analyzing data for customer-centric product changes and building advanced machine learning solutions to fuel company scaling.}

\lettercontent{I possess a strong command of Python and SQL, along with a sound understanding of data structures, algorithms, and machine learning principles. Furthermore, my self-started projects demonstrate my proactive nature and analytical acumen essential for the role. I am eager to contribute to Wise's mission of revolutionizing the global financial landscape.}

\lettercontent{I am particularly excited about the opportunity at Wise to apply machine learning to address real-world challenges and collaborate with a diverse team committed to technological innovation. I am confident that my background and skills make me a suitable candidate for this position.}

\lettercontent{Thank you for considering my application. I am looking forward to the possibility of contributing to Wise's impactful initiatives and learning from the talented team.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to Adem Mcharek's experiences and skills as captured in the resume provided, aligning them with the job requirements and responsibilities specified by Wise for the Data Science Intern position. Feel free to adjust any details or content to better suit Adem Mcharek's profile.