Based on the information provided in Adem Mcharek's resume and the cover letter examples, we can tailor a cover letter for the internship opportunity at Alcon's Information Technology, Transformation & Continuous Improvement (ITCI) department. Below is the customized cover letter in LaTeX format for Adem Mcharek:

```latex
\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Alcon}
\companyaddress{
Cointrin, Switzerland
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the internship opportunity at Alcon's Information Technology, Transformation \& Continuous Improvement (ITCI) department. With a Bachelor's degree in Artificial Intelligence from Long Island University and a cumulative GPA of 3.88/4.00, I am eager to bring my technical expertise to contribute to Alcon's commitment to innovation in eye care products.}

\lettercontent{Through my role as an AI Research Assistant at LIU Brooklyn, where I orchestrated an AI Research Assistant using AUTOGEN's multi-agent system for real-time academic literature retrieval, I have honed my skills in artificial intelligence and gained experience in transforming scholarly research. My projects such as developing a PyTorch CNN for MNIST and working on Computer Vision using TensorFlow demonstrate my proficiency in deep learning and neural network architecture.}

\lettercontent{I am particularly excited about the opportunity to gain industry experience and work on meaningful projects at Alcon that will help patients and customers see brilliantly. My experience in software engineering, statistics, and hands-on skills in SQL, Python, AWS, and Excel align well with the desired qualifications for the internship. I am confident in my ability to collaborate in a team environment, innovate, and solve complex problems, making me a strong candidate for this internship opportunity.}

\lettercontent{I am enthusiastic about the chance to contribute to Alcon's mission of enhancing the quality of life through innovative eye care products. I am looking forward to the possibility of working at Alcon, gaining valuable experience, and furthering my skills in the field of Information Technology.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}
```

This cover letter is tailored to highlight Adem Mcharek's education, projects, skills, and aspirations that align with the internship opportunity at Alcon. It emphasizes his technical expertise, hands-on experience, and enthusiasm for contributing to innovative projects in the IT sector, particularly in the context of enhancing eye care products at Alcon.