\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Identifeye Health Inc.}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in joining Identifeye Health Inc. as an intern. Currently pursuing a Bachelor's degree in Artificial Intelligence, with a focus on machine learning, deep learning, and software engineering at Long Island University, I am excited about the opportunity to contribute to a company pioneering non-invasive diagnostic platforms.}

% Adapting to the company's values and principles
\lettercontent{Identifeye Health's commitment to democratizing healthcare resonates with my passion for using technology to make a positive impact. I am particularly drawn to the mission of providing affordable and convenient access to healthcare through innovative solutions.}

% Connecting Adem's experience with the required responsibilities
\lettercontent{With experience as an AI Research Assistant, developing CNN models, and working on computer vision projects, I am well-equipped to implement new features, participate in the code review process, and evaluate software solutions, as outlined in the internship responsibilities.}

% Closing and expressing readiness to contribute
\lettercontent{I am eager to bring my technical skills, collaborative spirit, and passion for healthcare technology to the Internship Program at Identifeye Health. I look forward to the opportunity to discuss how I can contribute to your innovative projects and learn from your esteemed team.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}