\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Alcon}
\companyaddress{
Cointrin, Switzerland
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Summer 2024 Internship opportunity at Alcon as advertised. With a solid academic background pursuing a Bachelor's degree in Artificial Intelligence at Long Island University and a Cumulative GPA of 3.88/4.00, I am excited about the prospect of contributing to Alcon's mission of enhancing eye care through innovative products.}

\lettercontent{My experience as an AI Research Assistant, where I orchestrated cutting-edge AI projects like the Research Navigator and developed a PyTorch CNN for image classification, aligns well with the responsibilities outlined for the internship at Alcon. Additionally, my hands-on projects in Computer Vision using TensorFlow demonstrate my proficiency in data analytics, scripting, and collaborating in a team environment.}

\lettercontent{I possess strong technical skills in Python, SQL, AWS, and Excel, along with a keen interest in statistics and software engineering. My innovative mindset, problem-solving abilities, and prior experience in leading AI-related initiatives as the Founder and President of the AI Club make me a well-rounded candidate for this internship.}

\lettercontent{I am particularly excited about the opportunity to work on meaningful projects that will contribute to the advancement of eye health globally, while also receiving coaching and mentoring opportunities at Alcon. I am eager to bring my technical expertise, creativity, and dedication to Alcon and engage with the talented professionals in the Information Technology, Transformation & Continuous Improvement (ITCI) function.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am looking forward to the possibility of contributing to Alcon's vision of helping people see brilliantly.}

\signature{Adem Mcharek}

\end{document}