\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Grail}
\companyaddress{
Menlo Park, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the position at Grail, a company dedicated to revolutionizing cancer detection. As a Bachelor in Artificial Intelligence student with a strong foundation in machine learning, deep learning, and cloud computing, I am excited about the opportunity to contribute to Grail's mission of early cancer detection, aligning with my passion for impactful technological solutions.}

% Adapting Responsibilites and Background
\lettercontent{Through my experience as an AI Research Assistant and projects like developing Convolutional Neural Networks for image classification and Computer Vision applications, I have honed my ability to translate complex concepts into practical solutions. I am eager to collaborate within a dynamic team at Grail, focusing on the full-stack development lifecycle to provide access to Galleri, the Multi-Cancer Early Detection Test. My proficiency in Python, machine learning, and cloud-based services on AWS align well with the requirements of the role at Grail.}

% Highlighting specific skills and qualifications
\lettercontent{Moreover, my leadership roles, such as founding the AI Club, demonstrate my commitment to fostering innovation and collaborative environments. I possess strong problem-solving skills, attention to detail, and a quick learning ability. My solid mathematical foundation, hands-on experience in software engineering, and a proactive approach to adopting new technologies make me well-equipped to thrive in a challenging and fast-paced environment like Grail.}

% Conclusion and signature
\lettercontent{I am excited about the possibility of contributing to Grail's groundbreaking work in cancer care and early detection. I look forward to the opportunity to discuss how my skills and experiences align with the innovative projects at Grail. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}