\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Astranis Space Technologies}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Software Developer, Network/Payload Software Intern position at Astranis Space Technologies, a company that is leading the way in bridging the global digital divide by providing internet access to underserved populations. Currently pursuing a B.S. in Computer Science, as well as having experience in optimizing algorithms and modeling, I am excited about the opportunity to merge my technical skills with the intricate dynamics of satellite software development at Astranis.}

\lettercontent{With a solid foundation in Applied Mathematics and experience in designing and testing software from scratch, I am well-equipped to contribute to the engineering team at Astranis. The chance to work on software running on satellites, ground control systems, and performance management software aligns perfectly with my career aspirations and technical expertise.}

\lettercontent{Moreover, my proficiency in C++, Python, and scripting languages, along with a strong analytical acumen developed through academic projects and internships, position me as a suitable candidate for this role. I am eager to collaborate with a team that values innovation, technical excellence, and social impact, which resonates deeply with Astranis' mission to connect the world through advanced satellite technology.}

% Conclusion and signature
\lettercontent{I am excited about the possibility of contributing to Astranis Space Technologies and am confident that my skills and passion for technology align well with the objectives of the Software Developer, Network/Payload Software Intern position. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}