\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Rivian}
\companyaddress{
Irvine, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Data Engineering Intern position at Rivian as advertised. With a solid academic background and practical experience in data science and engineering, I am excited about the opportunity to contribute to Rivian's mission of innovation and sustainability.}

\lettercontent{During my studies at the University of Illinois Urbana Champaign, pursuing a degree in [Adem’s degree subject], I have gained significant expertise in programming with Python and SQL, as well as working with relational databases and statistics. Additionally, I have hands-on experience with Big Data technologies like [mention any relevant technology you have experience with], which I believe align well with the requirements of the internship role at Rivian.}

\lettercontent{My passion for utilizing data to drive strategic decisions aligns perfectly with the responsibilities outlined for the internship. I am eager to identify and develop use cases, create data collection frameworks, and build intuitive dashboards to present complex information to stakeholders effectively.}

% Conclusion and signature
\lettercontent{I am confident that my academic background, technical skills, and enthusiasm for data analytics make me a strong candidate for this internship position at Rivian. I am looking forward to the opportunity to contribute to Rivian's mission and learn from the talented team at Rivian. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}