\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Equipment Share}
\companyaddress{
Columbia, Missouri
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Data Science Intern position at Equipment Share as advertised. Currently pursuing a Bachelor's degree in Computer Science, I am excited about the opportunity to apply my knowledge and skills to contribute to Equipment Share's innovative approach in the construction industry through advanced analytics and optimization solutions.}

\lettercontent{With a solid foundation in mathematics encompassing calculus, linear algebra, optimization, probability, and statistics, I have developed proficiency in applying modern advanced analytics methods like predictive modeling, machine learning, and statistical modeling. My experience with time series/forecasting modeling and optimization techniques aligns well with the requirements of the role at Equipment Share.}

\lettercontent{In terms of technical skills, I have a strong command of Python for developing numerical models and possess the necessary SQL knowledge to work with databases like Snowflake and PostgreSQL. Furthermore, my ability to effectively communicate complex technical concepts to both technical and non-technical audiences will facilitate seamless collaboration within the Data Science team at Equipment Share.}

\lettercontent{I am eager to leverage my skills in predictive analytics, machine learning, and optimization to generate internal insights and contribute to customer-facing applications. Additionally, my problem-solving abilities and willingness to seek guidance from teammates make me well-suited for the collaborative environment at Equipment Share.}

% Conclusion and signature
\lettercontent{I am excited about the prospect of joining Equipment Share as a Data Science Intern and contributing to the cutting-edge work being done in operational research and analytics. I am confident in my ability to make a meaningful impact and eager to be a part of a team that values innovation and continuous improvement.}

\lettercontent{Thank you for considering my application. I look forward to the possibility of discussing how my background, skills, and enthusiasm align with the goals of Equipment Share.}

\signature{Adem Mcharek}

\end{document}