\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Rivian}
\companyaddress{
Irvine, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager at Rivian,}

\lettercontent{I am writing to express my interest in the internship opportunity at Rivian for the upcoming summer of 2024. With a passion for adventure and a commitment to sustainability, I am excited about the prospect of contributing to Rivian's innovative approach to Electric Adventure Vehicles and its dedication to environmental protection.}

% Match skills and experiences with requirements and responsibilities
\lettercontent{Having pursued my [Degree Level] in [Field of Study], I have developed a strong foundation in [Relevant Field], aligning well with the requirements outlined for the internship position at Rivian. Through my coursework and experiences, particularly in [Mention Specific Experiences or Projects], I have honed my skills in [Relevant Skills such as data analysis, stakeholder engagement, and problem-solving].}

\lettercontent{I am particularly excited about the opportunity to work on defining requirements with stakeholders, analyzing complex business problems, and providing valuable insights through data at Rivian. My proficiency in [Specific Tools or Software such as SQL, Python, and Excel] equips me to fulfill the responsibilities of supporting manual reporting, automation of production tasks, and creating ad-hoc reports to drive both tactical and strategic initiatives.}

% Closing and signature
\lettercontent{I am eager to leverage my skills and enthusiasm for analytics to contribute effectively to Rivian's supply chain operations. Thank you for considering my application. I look forward to the possibility of discussing how my background and passion align with Rivian's mission.}

\signature{Adem Mcharek}

\end{document}