\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{CACI International Inc}
\companyaddress{
Reston, Virginia
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Software Development/Engineering Intern position at CACI International Inc for the Summer 2024 internship in Omaha, NE. As a dedicated Computer Science student with a passion for software development and a strong foundation in modern technologies, I am excited about the opportunity to contribute to your team and support the critical challenges faced in national security and government modernization.}

% Aligning experiences and skills with the job requirements
\lettercontent{With experience in modern software development languages such as Java, C++, and JavaScript, I have actively contributed to development projects focusing on applications' design, debugging, and runtime skills. Moreover, my ongoing studies in Computer Science at {Insert University} equip me with a solid understanding of software development and engineering principles. Being legally authorized to work in the United States, I am prepared to engage in all phases of the application lifecycle as outlined in the job requirements.}

% Demonstrating alignment with desired qualifications
\lettercontent{Additionally, my exposure to Linux environments, Big Data technologies like Elastic Search and Kafka, along with proficiency in tools such as Jenkins, GitLab, and Docker, position me well to meet the desired qualifications for the role. I am eager to further develop my expertise in cloud services, particularly in Amazon Web Services and Microsoft Azure, to contribute effectively to your team's innovative projects.}

% Closing and signature
\lettercontent{I am enthusiastic about the opportunity to join CACI International Inc and contribute to the innovative projects that enhance battlespace awareness and decision-making support across various domains. I am eager to bring my technical skills, passion for software development, and commitment to excellence to your esteemed organization. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}