\documentclass[]{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Astranis Space Technologies}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Manufacturing Quality Engineering Intern position at Astranis Space Technologies. With a Bachelor's degree in Artificial Intelligence from Long Island University and a solid background in machine learning, deep learning, and data analysis, I am excited about the opportunity to contribute to your innovative projects.}

% Tailored content based on Adem Mcharek's experiences and skills
\lettercontent{During my tenure as an AI Research Assistant at LIU Brooklyn, I led projects incorporating advanced mathematical computations and real-time data retrieval, demonstrating my ability to translate complex concepts into practical solutions. My experience in developing a PyTorch CNN for image classification and implementing computer vision systems aligns well with the technical rigor required in the manufacturing quality engineering role.}

\lettercontent{Moreover, my leadership roles as the Founder and President of the AI Club highlight my proficiency in fostering collaborative environments and driving high-level projects. I have honed my analytical acumen through problem-solving in math Olympiads and have a solid foundation in programming languages like Python and experience with data analysis tools such as Tableau and Excel - skills that are directly applicable to the requirements at Astranis Space Technologies.}

\lettercontent{I am particularly intrigued by Astranis' mission to revolutionize energy movement and deliver last-mile electrification, and I am eager to contribute to such impactful endeavors. My passion for innovation and technical acumen make me confident that I can support your team's goals effectively.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am excited about the prospect of bringing my skills and enthusiasm to Astranis Space Technologies. I look forward to the opportunity to discuss how my background aligns with the requirements of the role.}

\signature{Adem Mcharek}

\end{document}