\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Identifeye Health}
\companyaddress{
Guilford, Connecticut
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Software Engineering Internship at Identifeye Health, a company that is pioneering a non-invasive diagnostic platform leveraging the uniqueness of the retina for health condition detection. As a Bachelor in Artificial Intelligence student at Long Island University with a focus on machine learning, deep learning, and software engineering, I am excited about the opportunity to contribute to your mission of democratizing healthcare through innovative technology.}

% Adapting to Responsibilities
\lettercontent{Having orchestrated an AI Research Assistant using multi-agent systems and developed projects like PyTorch CNN for MNIST and Computer Vision using TensorFlow, I have honed my skills in software development, deep learning, and neural network architecture. My experience aligns well with the responsibilities of implementing new features, conducting automated tests, and actively participating in the code review process as outlined for the internship.}

% Expressing Fit and Enthusiasm
\lettercontent{Identifeye Health's focus on empowering individuals through accessible health insights resonates with my passion for using technology to solve real-world problems. I am particularly drawn to the opportunity to work on innovative projects related to non-invasive health monitoring, which aligns perfectly with my academic background and practical experience in AI and machine learning.}

% Closing Remarks
\lettercontent{I am excited about the possibility of contributing to Identifeye Health's groundbreaking work and am eager to bring my technical skills and collaborative mindset to the software engineering team. Thank you for considering my application.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}