\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Identifeye Health Inc.}
\companyaddress{
Guilford, Connecticut
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the internship opportunity at Identifeye Health Inc., a company dedicated to democratizing healthcare by leveraging cutting-edge technology for non-invasive health diagnostics. As a student pursuing a Bachelor's degree in Computer Science with a strong foundation in software development and a keen interest in innovative solutions, I am particularly drawn to the mission and vision of Identifeye Health Inc.}

% Adem's experiences and skills alignment
\lettercontent{During my academic journey, I have engaged in projects encompassing algorithm optimization and real-world problem-solving, which have equipped me with the ability to translate complex concepts into practical solutions. My solid understanding of data structures and algorithms, coupled with my experience in software development and software testing methodologies, positions me well to contribute effectively to Identifeye Health's goal of revolutionizing diagnostic platforms. Furthermore, my adaptability and proficiency in learning new programming languages, including Typescript, align with the requirements outlined for the internship position.}

% Fit with Identifeye Health and closing
\lettercontent{I am excited about the opportunity to contribute to Identifeye Health's innovative work at the intersection of healthcare and technology. The prospect of working in a fast-paced, collaborative environment to develop new features, conduct software testing, and evaluate solutions aligns perfectly with my career aspirations. I am eager to bring my technical skills and passion for healthcare advancements to Identifeye Health Inc.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}