\documentclass[]{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}
\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Cadence Design Systems}
\companyaddress{
San Jose, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the position at Cadence Design Systems, a renowned leader in electronic systems design. With a Bachelor's degree in Artificial Intelligence from Long Island University and a diverse background in AI research and development, I am excited about the opportunity to contribute to Cadence's innovative projects in transforming design concepts into tangible products using sophisticated technology.}

\lettercontent{My experience includes orchestrating an AI Research Assistant for real-time academic literature retrieval and developing advanced AI models like Convolutional Neural Networks and computer vision systems. These projects have honed my skills in algorithm development, data transformation, and deep learning applications, aligning well with the requirements for the role at Cadence.}

\lettercontent{Moreover, I have a solid foundation in Java programming, data structures, and software engineering practices, which I believe will enable me to excel in developing programs and test harnesses as outlined in the responsibilities for this position. My proactive approach to learning and problem-solving, coupled with my passion for technology and innovation, make me a suitable candidate to join Cadence's team of leaders and innovators.}

\lettercontent{I am particularly drawn to Cadence's commitment to fostering a positive work environment and its track record of being recognized as a top employer. I am eager to leverage my skills and knowledge to contribute to Cadence's mission of delivering comprehensive solutions that push the boundaries of electronic systems design.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I look forward to the possibility of discussing how my background and experiences align with the exciting opportunities at Cadence Design Systems.}

\signature{Adem Mcharek}

\end{document}