\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Wayfair Inc.}
\companyaddress{
Boston, Massachusetts
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Supply Chain, Service, and Operations Co-op position at Wayfair Inc., as advertised. With a strong background in business operations and a keen interest in analytics, I am excited about the opportunity to leverage data, build cross-functional partnerships, and contribute to driving efficient supply chain operations at Wayfair.}

% Aligning qualifications with job requirements and responsibilities
\lettercontent{During my academic journey, I have honed my analytical skills through courses in data analytics and supply chain management. Additionally, my hands-on experience with Excel and SQL, combined with a drive to solve complex problems, positions me well to analyze the Service and Operations organizations at Wayfair. I am eager to collaborate with suppliers, carriers, and field teams to enhance operational performance and fuel Wayfair’s growth momentum.}

\lettercontent{Moreover, my excellent communication skills, business acumen, and ability to tackle challenges in a fast-paced environment align well with the responsibilities of the role. I am enthusiastic about the prospect of working on strategic initiatives that optimize the supply chain while ensuring speed, reliability, and cost-efficiency.}

% Conclusion and signature
\lettercontent{I am eager to contribute to Wayfair's mission of revolutionizing the customer experience through innovative logistics solutions. Thank you for considering my application. I look forward to the possibility of discussing how my skills and experiences align with the goals of Wayfair Inc.}

\lettercontent{Warm regards,}

\signature{Adem Mcharek}

\end{document}