\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Welocalize}
\companyaddress{
New York, New York
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Content Quality Intern position at Welocalize. With a strong academic background in Artificial Intelligence and hands-on experience in AI research and projects, I am excited about the opportunity to contribute to a global leader in multilingual content transformation.}

% Highlighting relevant skills and experiences
\lettercontent{During my tenure as an AI Research Assistant at LIU Brooklyn, I have honed my skills in data training, search quality rating, and AI tools. My projects, such as developing a Convolutional Neural Network in PyTorch and implementing computer vision solutions using TensorFlow, have equipped me with a solid foundation in evaluating and optimizing algorithms – a skill set directly relevant to assessing the quality and relevance of online advertisements as outlined in the job requirements.}

% Aligning with company values and responsibilities
\lettercontent{Welocalize's commitment to quality and innovation resonates with my own values and aspirations. I am eager to collaborate with diverse teams, provide valuable feedback, and stay abreast of evolving evaluation methods, all while upholding the company's standards for content transformation across languages.}

% Closing and expressing readiness
\lettercontent{I am enthusiastic about the opportunity to leverage my passion for AI and language services within Welocalize's inclusive and dynamic environment. Thank you for considering my application.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}