\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Alarm.com}
\companyaddress{
McLean, Virginia
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the position of an embedded software engineer at Alarm.com, where innovation and technological excellence converge to redefine the landscape of Internet-of-Things solutions for residential and commercial properties. With a strong foundation in Artificial Intelligence and a passion for cutting-edge technologies, I am excited about the opportunity to contribute to your Device Engineering team by designing devices, building hardware, architecting software, and thriving in an agile work environment.}

% Alignment with requirements and responsibilities
\lettercontent{My academic journey, highlighted by projects like AI Research Assistant with multi-agent systems and development of CNN models in PyTorch, has equipped me with the skills necessary to excel in software development for embedded devices. I have experience in modern programming languages like Python, proficiency in object-oriented design, and a deep understanding of deep learning and neural network architecture. Moreover, my leadership role as the Founder and President of the "AI Club" demonstrates my collaborative spirit and ability to drive innovative projects across diverse AI domains.}

% Fit with company culture and goals
\lettercontent{I am drawn to Alarm.com's commitment to technological innovation and collaborative culture, which align perfectly with my aspirations and technical proficiency. The opportunity to work on advanced technologies like native iOS and Android applications, alongside a team that values high standards and fosters a dynamic work environment, greatly excites me. I am eager to contribute to Alarm.com's mission of providing smart security solutions and making properties safer and smarter through impactful technology.}

% Closing and signature
\signature{Adem Mcharek}

\end{document}