\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Cadence Design Systems}
\companyaddress{
San Jose, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Allegro Applications Team intern position at Cadence Design Systems, as advertised. As a current student majoring in Computer Science at Ecole Polytechnique, with a strong foundation in Applied Mathematics from Sorbonne University, I am captivated by the opportunity to contribute my technical proficiency to your team and tackle real-world problems.}

\lettercontent{Throughout my academic journey, I have undertaken various projects that involved optimizing algorithms and modeling, such as the electric scooter infrastructure project. These experiences have equipped me with the ability to translate complex mathematical concepts into practical solutions, a skill set that I believe aligns well with the responsibilities outlined for the internship at Cadence Design Systems.}

\lettercontent{What resonates with me about Cadence Design Systems is the focus on innovative technology and fostering a collaborative environment, traits that I highly value. The emphasis on developing analytics applications on the Cadence JEDI platform and the opportunity to apply knowledge in circuit simulation, ML, and data processing excites me as I am keen on expanding my expertise in these areas.}

\lettercontent{I am particularly drawn to the technological innovation and strategic problem-solving aspects of the role, which align with my aspirations and skills. My proficiency in C++ and Python, coupled with my passion for learning, make me well-suited to contribute effectively to the Allegro Applications Team at Cadence Design Systems.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am looking forward to the possibility of discussing how I can contribute to the impactful work at Cadence Design Systems.}

\signature{Adem Mcharek}

\end{document}