\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Seismic}
\companyaddress{
San Diego, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Cloud Engineering internship position at Seismic for the Summer of 2024, as advertised. With a strong foundation in cloud architecture, open source technologies, and a keen enthusiasm for learning and contributing to innovative projects, I am excited about the opportunity to collaborate with a leading company in sales enablement like Seismic.}

\lettercontent{During my academic journey in \textbf{STEM majors}, set to graduate in Spring 2025, I have honed my technical skills and gained practical experience in building micro-service-based systems. I have a solid understanding of a variety of technologies, including \textbf{Azure, AWS, React, Typescript, C#/.NET}, and more, aligning well with the technological requirements of the position.}

\lettercontent{Moreover, my strong communication skills, attention to detail, and passion for leveraging technology to drive business growth make me a suitable candidate to work in an Agile, cloud-based environment as part of the Seismic team.}

\lettercontent{I am eager to bring my energy, ambition, and technical expertise to Seismic, contributing to the development of innovative solutions that empower sales and marketing teams to excel.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am looking forward to the possibility of contributing to Seismic and leveraging this internship opportunity to further develop my skills and knowledge in cloud engineering.}

\signature{Adem Mcharek}

\end{document}