\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Astranis Space Technologies}
\companyaddress{
944 Market Street, San Francisco, CA
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

I am writing to express my enthusiasm for the Data Science – Generative AI Intern position at Astranis Space Technologies, inspired by the company's commitment to engineering experiences and technological innovation. With a Bachelor's degree in Artificial Intelligence and a strong foundation in computer science and data science, including relevant coursework in Machine Learning, Deep Learning, and Natural Language Processing, I am excited about the opportunity to contribute to the advancement of large language models and adjacent areas within your team.

Drawing from my experience as an AI Research Assistant, where I orchestrated AI projects utilizing advanced mathematical computations and transformative technologies like multi-agent systems, I am well-equipped to collaborate on generative AI projects at Astranis. My proficiency in Python, coupled with my analytical skills and problem-solving abilities developed through various projects like developing a PyTorch CNN for image classification, aligns with the core requirements of the role at your esteemed organization.

Moreover, my active involvement in launching and leading the AI Club at LIU Brooklyn reflects my collaborative spirit and leadership qualities, essential for working within a project team environment. I am particularly interested in leveraging my expertise in large language models and search technologies to contribute meaningfully to Astranis Space Technologies' innovative projects and initiatives in the field of AI.

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am eager to further discuss how my background and skills align with the requirements of the Data Science – Generative AI Intern position at Astranis Space Technologies.}

\signature{Adem Mcharek}

\end{document}