\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Parallel Wireless}
\companyaddress{
Bristol, United Kingdom
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the intern position at Parallel Wireless to develop physical layer (PHY) software for 4G and 5G products. With a Bachelor's degree in Artificial Intelligence from Long Island University and a strong academic foundation in machine learning, deep learning, and software engineering, I am excited about the opportunity to contribute to the cutting-edge projects at Parallel Wireless.}

\lettercontent{During my tenure as an AI Research Assistant at LIU Brooklyn, I led projects utilizing multi-agent systems for real-time academic literature retrieval and developed a PyTorch CNN for MNIST, demonstrating my proficiency in deep learning and neural network architecture. Additionally, my experience in computer vision using TensorFlow for hand gesture recognition reflects my practical skills in software development.}

% Skills and experiences related to the requirements
\lettercontent{My background in Python and C++ programming, along with exposure to machine learning algorithms, directly aligns with the requirements for the role at Parallel Wireless. I have a solid understanding of wireless algorithms and digital signal processing concepts, which will enable me to contribute effectively to the optimization and validation of PHY software on advanced CPUs.}

% Conclusion and signature
\lettercontent{I am inspired by Parallel Wireless's commitment to innovation and employee development. I am keen to apply my technical skills and passion for AI to support Parallel Wireless in redefining network economics and advancing telecom technology. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}