\documentclass[]{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Astranis Space Technologies}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm in applying for the Technical Program Manager Intern position at Astranis Space Technologies, as advertised. With a solid educational background in Artificial Intelligence and a wealth of hands-on experience in AI research, computer vision, and deep learning, I am excited about the opportunity to contribute to Astranis' mission of bridging the digital divide using innovative satellite technology.}

\lettercontent{My tenure as an AI Research Assistant at LIU Brooklyn has equipped me with the skills to coordinate projects, analyze risks, and streamline logistics—qualities that directly align with the responsibilities outlined for the role at Astranis Space Technologies. Moreover, my experience in developing PyTorch CNN for image classification and computer vision projects using TensorFlow demonstrates my capacity to handle complex technical tasks efficiently.}

\lettercontent{I am particularly drawn to Astranis' focus on social impact and technological innovation, as evidenced by the company's commitment to providing internet access to underserved communities globally. My leadership experience as the Founder and President of the AI Club, coupled with my participation in international mathematical competitions, reflects my dedication to driving positive change and fostering collaborative environments to solve challenging problems.}

\lettercontent{I am excited about the opportunity to work at Astranis and contribute to the advancement of satellite technology for global connectivity. My technical expertise, coupled with a strong commitment to excellence and a drive for innovation, make me a suitable candidate for the Technical Program Manager Intern position. I look forward to the possibility of discussing how my skills and experiences can benefit the innovative projects at Astranis Space Technologies.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}