\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{My Fitness Pal}
\companyaddress{
Austin, Texas
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my genuine interest in the Android internship opportunity at My Fitness Pal as advertised. As a current full-time college student pursuing a Bachelor's degree in Artificial Intelligence with a strong academic background in machine learning, deep learning, and software engineering, I am excited about the chance to contribute to a team that shares my passion for innovative technology and health-centric solutions.}

\lettercontent{My experiences, such as orchestrating an AI Research Assistant using AUTOGEN's multi-agent system and developing a PyTorch CNN for image classification, have honed my skills in software development, problem-solving, and collaborative teamwork. These experiences align well with the responsibilities outlined for the internship, including shipping production changes to Android applications and working alongside professional software engineers during the Software Development Lifecycle.}

\lettercontent{Moreover, my academic and project experiences have equipped me with a solid understanding of data structures, algorithms, and Java programming, which are essential for success in this role. My enthusiasm for software development, coupled with a proactive approach to learning and a commitment to excellence, makes me eager to contribute to the impactful work at My Fitness Pal.}

\lettercontent{I am particularly drawn to My Fitness Pal's mission of enabling individuals to make healthier choices through innovative tools and resources. The opportunity to work on projects that directly impact users aligns perfectly with my goal of leveraging technology to promote health and well-being.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}