\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Astranis Space Technologies}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the opportunity at Astranis Space Technologies. As a dedicated Bachelor student in Artificial Intelligence at Long Island University with a strong background in machine learning, deep learning, and computer vision, I am excited about the prospect of contributing to your innovative projects in the field of transportation advancement.}

% Aligning Adem's skills with the company's requirements
\lettercontent{With hands-on experience in developing AI applications, such as a camera tracking system for drones and a CNN for image classification, I believe I can effectively meet the requirements set by Astranis Space Technologies. My proficiency in Python, TensorFlow, PyTorch, and Docker aligns well with the company's focus on autonomous systems and robotics.}

% Detailing the fit with the company's growth and responsibilities
\lettercontent{Furthermore, I am captivated by Astranis Space Technologies' vision of creating new forms of transportation and its commitment to technological advancement. I am eager to collaborate with the engineering and flight testing teams to build cutting-edge solutions. My drive to deliver results and passion for continuous learning make me a perfect fit for the role of developing innovative systems for autonomous drones.}

% Conclusion and signature
\lettercontent{I am looking forward to the possibility of contributing to Astranis Space Technologies and being part of a team that is reshaping the future of transportation. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}