\documentclass[]{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Guidewire}
\companyaddress{
San Mateo, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Internship opportunity at Guidewire. Currently pursuing a Bachelor's degree in Artificial Intelligence at Long Island University Brooklyn with an expected graduation in Spring 2025, I am eager to bring my solid technical skills and experience to your innovative team.}

% Adem's experiences and skills related to the internship requirements
\lettercontent{Throughout my academic journey, I have excelled in relevant courses, honing my proficiency in Artificial Intelligence, deep learning, and neural network architecture. My experience as an AI Research Assistant involved developing AI solutions for real-time academic literature retrieval, web scraping, and mathematical computations, showcasing my ability to apply algorithms and object-oriented design effectively. Moreover, my participation in international Olympiads and hackathons reflects my agility in problem-solving and teamwork, aligning with the dynamic environment of an Agile software development team.}

% Adem's additional qualities and club involvement
\lettercontent{Apart from my technical skills, my leadership role as the Founder and President of the “AI Club” underscores my collaborative spirit and ability to foster a vibrant community of AI enthusiasts. I bring curiosity, accountability, and respect to my interactions, values that resonate with Guidewire's inclusive and collaborative culture.}

% Conclusion and signature
\lettercontent{I am excited about the opportunity to collaborate with the talented professionals at Guidewire, contribute to meaningful projects, and further develop my skills in an Agile development environment. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}