\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Precisely}
\companyaddress{
Burlington, Massachusetts
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Sales Engineer Intern position at Precisely as advertised. As an undergraduate student pursuing a degree in [Adem's field of study], I am excited about the opportunity to contribute to a global leader in data integrity like Precisely. The company's commitment to innovation, evidenced by its robust product suite and dedication to research, aligns perfectly with my aspirations for growth and learning in the field.}

\lettercontent{With a technical background in [Adem's technical program background], I bring strong communication skills, proficiency in Excel and SQL, and experience with dashboard solutions like Tableau. Moreover, my drive for critical thinking and analysis, coupled with a preference for SAP knowledge, positions me well to support Precisely in rebranding and updating product demo templates, providing feedback on product guides, creating observability dashboards, and engaging in customer-facing meetings.}

\lettercontent{I am particularly drawn to the opportunity to explore Sales Engineering as a potential career track, and I am eager to leverage this internship to gain hands-on experience, network with industry professionals, and further develop my skills in a remote work environment.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am enthusiastic about the possibility of contributing to Precisely and am excited about the prospect of learning and growing with your team.}

\signature{Adem Mcharek}

\end{document}