\documentclass[]{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Hitachi Vantara}
\companyaddress{
Santa Clara, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Data Science Intern position at Hitachi Vantara. With a strong academic background in Artificial Intelligence from Long Island University and hands-on experience as an AI Research Assistant at LIU Brooklyn, where I orchestrated AI systems for real-time academic literature retrieval and developed subprojects incorporating web scraping and advanced mathematical computations, I am excited about the opportunity to contribute to Hitachi Vantara's innovative projects.}

% Match the responsibilities and qualifications
\lettercontent{In my projects such as implementing a Convolutional Neural Network in PyTorch for image classification and developing a hand gesture recognition system using TensorFlow, I have demonstrated proficiency in machine learning and deep learning. My achievements, including securing medals in Mathematical Olympiads and participating in hackathons, showcase my problem-solving skills and creativity. I am particularly intrigued by Hitachi Vantara's focus on leveraging data for growth and the responsibilities of defining machine learning use cases and performing model training align well with my expertise.}

% Closing and signature
\lettercontent{I am eager to apply my skills in Machine Learning, AI Ops, and Data Catalog integration to contribute meaningfully to Hitachi Vantara's mission of enhancing business performance through digital solutions. I look forward to the possibility of discussing how my background and skills could benefit your team. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}