\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Elevance Health}
\companyaddress{
Indianapolis, Indiana
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Data and Reporting Analytics Intern - Undergrad position at Elevance Health as advertised. With a background in [Adem Mcharek's relevant field of study or experience], I am excited about the opportunity to contribute to your mission of reimagining the health system through a holistic approach.}

\lettercontent{During my academic and professional journey, I have developed strong problem-solving and analytical skills, which I believe align well with the responsibilities of assisting the Health Economics team in healthcare data collection, analysis, and validation at Elevance Health. My experience in [mention any relevant experience], coupled with proficiency in SQL, SAS, and R, enables me to effectively analyze data for accuracy and derive valuable insights to support your projects.}

\lettercontent{Moreover, my time management skills and ability to adapt to a fast-paced environment make me a suitable candidate to work on competitive intelligence projects and contribute to network dashboards as mentioned in the job description. I am eager to leverage my technical skills and passion for excellence to support Elevance Health's initiatives in improving healthcare accessibility and outcomes.}

\lettercontent{I am enthusiastic about the opportunity to learn from your team, engage in challenging projects, and further develop my skills in a real-world setting. I am confident that my academic background, coupled with my dedication to personal career development, make me a valuable addition to the Elevance Health team.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}