\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Bose Corporation}
\companyaddress{
Framingham, Massachusetts
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Data Engineering position at Bose Corporation as advertised. With a background in data pipelines, data acquisition, and M L model deployment, coupled with proficiency in Python, S Q L coding, and familiarity with A W S Serverless solutions, I am excited about the opportunity to contribute to Bose's innovative projects.}

% Personalized content based on Adem's experiences and skills
\lettercontent{During my previous roles, I have successfully designed and developed robust data pipelines, ensuring seamless data flow and efficient M L model deployment. My experience with A W S Serverless technologies has equipped me to collaborate effectively in multi-functional agile teams, driving impactful solutions through continuous experimentation and iteration. My proficiency in Snowflake, Databricks, and A W S Serverless technologies further enhances my capabilities to optimize and evaluate scalable solutions in alignment with Bose's objectives.}

% Additional paragraph aligning Adem's aspirations with Bose's mission
\lettercontent{I am passionate about sound engineering and technological innovation, values that resonate strongly with Bose's mission to enhance the power of sound. I am eager to leverage my skills and collaborate with the talented team at Bose to further advance the company's data platforms and contribute to its digital transformation journey.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am looking forward to the possibility of contributing to Bose Corporation and being part of a team dedicated to pushing the boundaries of audio technology.}

\signature{Adem Mcharek}

\end{document}