\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{CACI International Inc}
\companyaddress{
Reston, Virginia
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the UAV Swarm Development Intern position at CACI International Inc. The opportunity to be part of your groundbreaking projects in autonomous drone technology resonates deeply with my academic background and passion for technology innovation.}

\lettercontent{As a Bachelor student majoring in Artificial Intelligence at Long Island University, with a Cumulative GPA of 3.88/4.00, I have honed my skills in machine learning, deep learning, cloud computing, and software engineering. My experiences as an AI Research Assistant, where I orchestrated AI projects and developed AI models, have equipped me with hands-on knowledge in implementing cutting-edge technologies like AI algorithms and data pipelines.}

\lettercontent{The responsibilities outlined in the job description, such as researching drone swarm designs, implementing AI algorithms for autonomous navigation, and establishing data pipelines for drone swarm data processing, perfectly align with my project experiences and technical skills. My proficiency in programming languages like Python and my exposure to AI frameworks like PyTorch and TensorFlow make me well-equipped to contribute effectively to your projects.}

% Conclusion and signature
\lettercontent{I am enthusiastic about the prospect of applying my technical skills and passion for innovation to the UAV Swarm Development Intern role at CACI International Inc. I am confident that my academic background, project experiences, and dedication to technology advancement make me a strong candidate for this position. Thank you for considering my application.}

\lettercontent{Warm regards,}

\signature{Adem Mcharek}

\end{document}