\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Arrowhead Pharmaceuticals}
\companyaddress{
Pasadena, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the computational biology internship at Arrowhead Pharmaceuticals, particularly focused on computational siRNA target validation for neurodegenerative diseases. With a Bachelor's degree in Artificial Intelligence from Long Island University, where I excelled in relevant courses such as Machine Learning, Data Mining, and Natural Language Processing, I believe I am well-equipped to contribute effectively to your innovative research projects.}

\lettercontent{During my academic journey, I have undertaken diverse projects that have honed my analytical acumen and programming skills, such as optimizing algorithms and modeling for complex systems. I am excited about the prospect of leveraging my technical proficiency to tackle real-world challenges in computational biology at Arrowhead Pharmaceuticals, a renowned leader in RNA-targeted therapeutics.}

\lettercontent{The opportunity to collaborate with Arrowhead's research teams, utilize licensed databases, and analyze datasets to identify siRNA targets aligns perfectly with my skills and aspirations in the field of computational biology. I am particularly drawn to Arrowhead's innovative approach to drug development and its commitment to addressing diseases with a genetic basis, showcasing the potential to make a substantial impact in the field of neurodegenerative disease research.}

% Conclusion and signature
\lettercontent{Enclosed is my resume for your review, providing further insight into my academic background and project experiences. I am eager to discuss how my skill set and passion for computational biology can contribute to the groundbreaking work at Arrowhead Pharmaceuticals. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}