\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Rivian}
\companyaddress{
Irvine, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Internship position at Rivian as advertised. With a Bachelor's degree in Artificial Intelligence from Long Island University and hands-on experience in AI research and development, I am excited about the opportunity to contribute to Rivian's innovative projects.}

\lettercontent{My involvement as an AI Research Assistant, where I led the development of AI systems for real-time academic literature retrieval and implemented Convolutional Neural Networks for image classification, has equipped me with the skills in embedded platform architecture, Python, and C programming, aligning well with the requirements of the position at Rivian.}

\lettercontent{I am particularly drawn to Rivian's dedication to environmental sustainability and technical precision in the automotive industry. My background in AI, machine learning, and software engineering, coupled with a passion for cutting-edge technologies, positions me well to support Rivian's mission of innovation and global impact.}

\lettercontent{I am enthusiastic about the opportunity to contribute to the design and implementation of a Software Application Framework at Rivian, working collaboratively with peers and stakeholders to address hardware and software challenges. My experience in project leadership and problem-solving, including winning accolades in international competitions, reflects my commitment to excellence and innovation.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am eager to bring my skills and enthusiasm to the Electrical Hardware team at Rivian and contribute to the company's pioneering initiatives.}

\signature{Adem Mcharek}

\end{document}