\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Roku}
\companyaddress{
San Jose, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{As an aspiring software engineer with a strong passion for technology and a drive for creativity, I am excited to apply for the Software Engineer Intern position at Roku. With a background in computer science and non-academic coding experience, including personal projects and participation in hack-a-thons, I am eager to contribute to Roku's innovative team.}

\lettercontent{I am currently pursuing a Bachelor's degree in computer science and possess a solid understanding of software development principles and various programming languages such as Python, Java, and JavaScript. My curiosity to stay atop of tech trends aligns perfectly with Roku's commitment to driving innovation in the TV streaming industry.}

\lettercontent{I am particularly drawn to Roku's mission of connecting the entire TV ecosystem and empowering content publishers and advertisers worldwide. I am confident that my skills and enthusiasm for software development will allow me to make a valuable contribution to Roku's dynamic team.}

\lettercontent{I am thrilled at the opportunity to engage in a 12-week internship program at Roku, focusing on potential areas like Embedded and Test Engineering. My eagerness to learn and grow aligns well with Roku's emphasis on continuous exploration of new ideas and technologies. I am ready to immerse myself in the fast-paced environment at Roku and make a meaningful impact while gaining valuable experience.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}