\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Bose}
\companyaddress{
Framingham, Massachusetts
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Intern/Co-op position within the Out-Loud embedded software development team at Bose, a company renowned for its commitment to delivering high-quality sound through innovative products. With a solid foundation in Object-Oriented Software concepts and experience in programming with C/C++, I am excited about the opportunity to contribute to the next generation of Smart Speakers and Soundbars.}

\lettercontent{Having worked on projects optimizing algorithms and modeling for various applications during my academic journey, I have honed the ability to translate complex mathematical concepts into practical solutions. This experience aligns well with the responsibilities of the role, where I aim to work alongside experienced engineers in developing software features related to Whole Home Audio, Music Services, and Data Collection.}

% Conclusion and signature
\lettercontent{I am particularly drawn to Bose's emphasis on Agile software development processes, test-driven development, and automated software test environments. The chance to gain exposure to these methodologies while working on cutting-edge audio products for consumers' home entertainment excites me. I am eager to bring my technical skills and passion for innovation to your team.}

\lettercontent{Thank you for considering my application. I look forward to the possibility of discussing how I can contribute to Bose's mission of creating better products and enriching people's audio experiences.}

\signature{Adem Mcharek}

\end{document}