\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Western Digital}
\companyaddress{
San Jose, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Firmware Engineering Intern position at Western Digital. With a Bachelor's degree in Artificial Intelligence and a strong foundation in machine learning, deep learning, and software engineering, I am excited about the opportunity to contribute to the development and debugging of firmware for Hard Disk Drives within your innovative company.}

\lettercontent{During my tenure as an AI Research Assistant at LIU Brooklyn, I orchestrated AI projects utilizing cutting-edge technologies like PyTorch and TensorFlow, showcasing my proficiency in developing and implementing complex algorithms. My experience in developing a PyTorch CNN for MNIST and a computer vision system using TensorFlow reflects my ability to work with structured code efficiently.}

\lettercontent{The responsibilities outlined for the Firmware Engineering Intern align perfectly with my technical skills and academic background. My expertise in programming languages like Python and my hands-on projects in AI application development have honed my problem-solving abilities and collaborative skills, essential for effective multi-site agile development teams.}

\lettercontent{I am particularly excited about the opportunity at Western Digital to work on real-time firmware code for head-disk interface control and to optimize control parameters, aiming to enhance device capacity while improving reliability and performance. My passion for firmware development and my experience in AI projects make me eager to join your team of experienced engineers and contribute meaningfully to your projects.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am looking forward to the possibility of discussing how my skills and experiences can contribute to Western Digital's innovative projects in firmware engineering.}

\signature{Adem Mcharek}

\end{document}