\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Trumid}
\companyaddress{
New York, New York
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the 2024 Summer Intern position with Trumid in the Observability team. With a background in Computer Science and Software Engineering, closely aligned with the requirements for the role, I am excited about the opportunity to contribute to Trumid's innovative platform.}

\lettercontent{During my academic journey, I have undertaken diverse projects, including optimizing algorithms and modeling for complex systems, honing my ability to translate intricate concepts into practical solutions. The responsibilities outlined for the role, such as contributing to the development of the observability ecosystem and actively engaging with cross-functional teams, resonate with my collaborative approach to problem-solving.}

\lettercontent{My general programming experience in modern languages, coupled with a keen interest in software development and resilience, positions me well to thrive in the dynamic environment at Trumid. While I do not have direct experience with Go, I am eager to further develop my skills in this area and contribute effectively to the team.}

\lettercontent{Trumid's emphasis on fostering a collaborative atmosphere and its commitment to technological innovation perfectly align with my career aspirations. I am particularly drawn to the opportunity to enhance system monitoring efficiency and contribute to the visibility and transparency of software behavior, reflecting my dedication to impactful and transparent solutions.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}