\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Leidos}
\companyaddress{
Columbia, MD
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Software Engineer Intern position at Leidos, specifically within the Cyber SIGNIT & Solutions Operation in Columbia, MD. Currently enrolled as a senior in a Systems Engineering program, I am enthusiastic about contributing to important operational programs and leveraging my skills and knowledge in software development, Linux, and programming languages like Python and Java.}

\lettercontent{With a strong interest in understanding complex systems at a fundamental level and experience in networking implementations, I am excited about the opportunity to work on software engineering tasks, including design, development, testing, troubleshooting, and debugging of software programs. My passion for technology, combined with my active pursuit of a Top Secret Security Clearance eligibility, aligns well with the requirements of the position.}

\lettercontent{Furthermore, I have practical experience in containerization, virtualization, and cloud technologies such as Docker, Kubernetes, AWS, and GCP, which I believe will be valuable assets in supporting the development and maintenance of infrastructure and platforms, as outlined in the job responsibilities.}

\lettercontent{I am particularly intrigued by the focus on machine learning applied to real tactical problems, and I am eager to apply my skills in this area to contribute effectively to the innovative projects at Leidos.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am looking forward to the possibility of discussing how my background, skills, and interests align with the dynamic and impactful work at Leidos.}

\signature{Adem Mcharek}

\end{document}