\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Secureworks}
\companyaddress{
Global Cybersecurity Leader
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Data Engineering Intern position at Secureworks. With a background in software engineering education and experience in Java, along with a solid foundation in problem-solving skills and attention to detail, I am eager to contribute to Secureworks' mission of enhancing cutting-edge real-time detection platforms.}

\lettercontent{During my academic journey, I have successfully completed projects that involved working with large, complex data sets and writing efficient code in Java. These experiences have equipped me with the skills needed to engage in the full software development lifecycle, from concept to deployment, aligning well with the responsibilities outlined for the Data Engineering Intern role at Secureworks.}

\lettercontent{I am particularly excited about the opportunity to collaborate with experienced data engineers at Secureworks, enhancing advanced detection engines such as Tactic Graphs™ using Apache Flink, Kafka, and Kubernetes. My eagerness to learn and delve into new technologies, combined with my strong communication skills and ability to work in a collaborative agile team environment, make me well-suited for this role.}

% Conclusion and signature
\lettercontent{I am confident that my background, skills, and passion for innovation align effectively with the values and goals of Secureworks. I look forward to the possibility of discussing in more detail how I can contribute to the innovative projects at Secureworks. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}