\documentclass[]{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Sound Cloud}
\companyaddress{
New York, NY
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Finance Data Analyst Intern position at Sound Cloud, as advertised. With a strong educational background in Artificial Intelligence, including extensive coursework in machine learning, deep learning, and data mining, complemented by practical experiences such as developing AI solutions and computer vision projects, I am excited about the prospect of contributing to Sound Cloud's mission of empowering audio creators.}

\lettercontent{My proficiency in handling granular financial datasets, honed through projects like the AI Research Assistant and the PyTorch CNN for MNIST, aligns well with the responsibilities outlined for this internship. I have a moderate to advanced level of expertise in Excel and Google Sheets, alongside SQL knowledge, which are key requirements for the role.}

\lettercontent{Moreover, my leadership role as the Founder and President of the "AI Club" demonstrates my ability to foster a collaborative community and drive innovative projects, qualities that I believe resonate with Sound Cloud's values. I am highly motivated, intellectually curious, and a team player, traits that I am eager to bring to the F P\&A team at Sound Cloud.}

% Conclusion and signature
\lettercontent{I am excited about the opportunity to further discuss how my technical skills, analytical mindset, and passion for innovation can contribute to the dynamic environment at Sound Cloud. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}