\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Hewlett Packard}
\companyaddress{
Palo Alto, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Software Intern position at Hewlett Packard. Currently pursuing a [Degree] at [University], with a strong foundation in [Skills], I am excited about the opportunity to apply my technical proficiency to real-world challenges in your renowned organization known for its commitment to innovation and meaningful progress.}

% Adem's relevant experiences and skills
\lettercontent{During my academic journey, I have successfully completed projects involving [Projects], demonstrating my ability to translate complex mathematical concepts into practical solutions. Moreover, my leadership roles and volunteer experiences have honed my soft skills, such as responsibility, adaptability, and commitment, essential for thriving in a dynamic work environment like Hewlett Packard.}

% Alignment with HP's values and aspirations
\lettercontent{Hewlett Packard's focus on innovation and fostering a collaborative atmosphere resonates with my aspirations. I am particularly excited about the opportunity to work on cutting-edge technologies and contribute to solutions that shape the way the world works. I am confident that my technical expertise and passion for impactful innovation align well with the ethos of Hewlett Packard.}

% Closing and signature
\lettercontent{Thank you for considering my application. I am eager to contribute to Hewlett Packard's innovative projects and make a positive impact. I look forward to the possibility of discussing how my skills and experiences align with the requirements of the Software Intern role.}

\signature{Adem Mcharek}

\end{document}