\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Cadence Design Systems}
\companyaddress{San Jose, California}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the software engineering position at Cadence Design Systems, a company renowned for its innovative solutions and commitment to excellence. With a Bachelor's in Artificial Intelligence and a proven track record in AI research and development showcased through projects utilizing technologies like PyTorch and TensorFlow, I am enthusiastic about the opportunity to contribute to the cutting-edge software solutions developed at Cadence.}

% Aligning with Cadence's requirements and responsibilities
\lettercontent{At Long Island University, I have honed my skills in machine learning, Python, and deep learning libraries like PyTorch and TensorFlow, aligning with Cadence's requirements. My experience in collaborating with AI professionals and leading AI-focused initiatives positions me well to work on complex problems to develop software for product design and verification at advanced nodes, as outlined in the responsibilities at Cadence.}

% Showcasing additional qualifications and enthusiasm for the role
\lettercontent{Furthermore, my proficiency in C/C++, object-oriented programming, and familiarity with UNIX/Linux platforms, along with a solid foundation in design patterns, algorithms, and data structures, make me a strong fit for the role at Cadence. I am excited about the opportunity to leverage my technical skills and problem-solving abilities to contribute to Cadence's Intelligent System Design strategy and be part of a team dedicated to technological innovation.}

% Closing the cover letter
\lettercontent{I am eager to bring my technical expertise, analytical skills, and passion for innovation to Cadence Design Systems. Thank you for considering my application. I look forward to the possibility of contributing to Cadence's mission of transforming design ideas into tangible products.}

\signature{Adem Mcharek}

\end{document}