\documentclass[]{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Cadence Design Systems}
\companyaddress{
San Jose, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

\lettercontent{Dear Hiring Manager,}

I am writing to express my enthusiasm for the Data Analyst Intern position at Cadence Design Systems. With a strong background in data collection, analysis, and generative AI tools, I am excited about the opportunity to leverage cutting-edge technologies to enhance marketing strategies at Cadence. The company's leadership in electronic systems design and its commitment to fostering a positive work environment align perfectly with my career aspirations.

During my academic journey, I have undertaken diverse projects, including optimizing algorithms and modeling for various applications. These experiences have equipped me with the skills to translate complex mathematical concepts into practical solutions. I am particularly drawn to Cadence's Intelligent System Design strategy, which resonates with my passion for innovative scientific research and collaboration in a dynamic environment.

My proficiency in data collection and analysis, combined with experience in generative AI tools and statistical techniques, makes me well-suited to uncover patterns, trends, and insights from large datasets. I am eager to utilize these skills to forecast market trends, campaign outcomes, and customer responses, ultimately driving marketing strategies with innovation and efficiency.

Moreover, my ability to collaborate cross-functionally and implement AI insights aligns with Cadence's focus on integrating AI to support broader business objectives. I am keen on facilitating the adoption of AI tools within the marketing department, bridging the gap between data science and marketing to drive continuous improvement and innovation.

I am excited about the prospect of contributing to Cadence's marketing success through advanced data analytics and generative AI models. Thank you for considering my application. I look forward to the possibility of discussing how my skills and experiences can benefit the innovative work at Cadence Design Systems.

\lettercontent{Warm regards,}

\signature{Adem Mcharek}

\end{document}