\documentclass[]{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}
\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Recorded Future}
\companyaddress{
Somerville, Massachusetts
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Software Engineering Intern position at Recorded Future. As a Bachelor in Artificial Intelligence student at Long Island University Brooklyn, with a strong foundation in Software Engineering, including Modern Cryptography and Data Mining, I am excited about the opportunity to contribute to a leading intelligence company like Recorded Future.}

% Match the candidate skills and experiences with the job requirements
\lettercontent{During my academic journey, I have acquired valuable skills in Python programming and data analysis, as well as a deep understanding of complex data structures. My coursework in Modern Cryptography and Data Mining has equipped me with the knowledge to explore datasets creatively and prototype novel use cases. I am keen on implementing new techniques to extract high fidelity information from data, aligning perfectly with the responsibilities of the internship at Recorded Future.}

% Showcase relevant qualifications and aspirations
\lettercontent{My curiosity to understand data usage, combined with my experience in developing production-grade Python code, make me well-suited for the dynamic environment at Recorded Future. I am eager to apply my skills to contribute to the Security Intelligence product, aiding in shedding light on potential threats hiding in the digital landscape.}

% Closing and signature
\lettercontent{With a strong analytical background and a passion for innovative solutions, I am confident in my ability to thrive as a Software Engineering Intern at Recorded Future. I am excited about the prospect of being part of a team that tackles tough data challenges and provides real-time threat intelligence. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}