\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Earnin}
\companyaddress{
Palo Alto, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the Product Analytics Intern position at Earnin, as advertised. With a strong background in Economics and Computer Science, currently pursuing my Bachelor's degree, I am excited about the opportunity to contribute to a company that is pioneering innovations in financial accessibility like Earnin.}

\lettercontent{During my academic journey and through internships, I have honed my analytical skills, particularly in data interpretation and deriving actionable insights from complex datasets. The responsibility at Earnin to analyze large datasets, delve into financial and employment data, and create insightful reports resonates deeply with my skill set and aspirations. I am eager to leverage my expertise to contribute to Earnin's mission of delivering real-time financial flexibility to individuals relying on earned wage access.}

\lettercontent{Moreover, my proficiency in Excel, SQL, and Python, combined with my strong attention to detail and commitment to producing high-quality work, align well with the specific requirements outlined for the role. I am confident that my analytical capabilities, coupled with effective communication and collaborative skills, make me a suitable candidate for this internship opportunity.}

\lettercontent{I am thrilled about the prospect of working in a high-impact role at Earnin, presenting insights, and collaborating with a talented analytics team. The chance to grow professionally in a diverse and inclusive environment like Earnin is truly appealing to me.}

% Conclusion and signature
\lettercontent{Thank you for considering my application. I am looking forward to the possibility of contributing to Earnin's journey of financial innovation and growth.}

\signature{Adem Mcharek}

\end{document}