\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Ripple}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiastic interest in the internship opportunity at Ripple to support the Trading & Markets team, as advertised. With a strong background in Artificial Intelligence and a demonstrated passion for financial markets, I am excited about the possibility of merging my technical expertise with the intricate dynamics of trading at Ripple.}

% Customized content based on Adem Mcharek's experiences and skills
\lettercontent{Throughout my academic journey at Long Island University, I have undertaken various projects that showcase my proficiency in machine learning, deep learning, and data analysis. My experience as an AI Research Assistant, where I orchestrated complex systems for real-time academic literature retrieval and developed a PyTorch CNN for image classification, has honed my analytical skills and ability to transform theoretical concepts into practical solutions.}

\lettercontent{Furthermore, my involvement as the Founder and President of the AI Club demonstrates my leadership and collaborative skills in fostering a vibrant community of AI enthusiasts, aligning with Ripple's ethos of innovation and collaboration. I am particularly drawn to Ripple's mission of providing a frictionless experience for global financial transactions and believe that my technical acumen and passion for financial markets make me a strong fit for this role.}

% Conclusion and signature
\lettercontent{I am thrilled about the opportunity to work with a pioneering company like Ripple and contribute to revolutionizing the global financial system. I am confident that my background in Artificial Intelligence and my interest in financial markets will allow me to excel in supporting the Trading & Markets team. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}