\documentclass[]{cover}
\usepackage{hyperref}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Arrowhead Pharmaceuticals, Inc.}
\companyaddress{
Pasadena, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my enthusiasm for the Web Designer Intern position at Arrowhead Pharmaceuticals, a company dedicated to developing targeted therapies for genetic diseases through RNA interference mechanisms. With a strong academic background in Artificial Intelligence at Long Island University and hands-on experience in AI research, computer vision, and machine learning projects, I am excited about the opportunity to contribute to Arrowhead's innovative approach to drug development.}

% Matching skills and experiences with the job requirements
\lettercontent{My proficiency in HTML, CSS, JavaScript, and experience in web and mobile design align well with the job requirements outlined by Arrowhead Pharmaceuticals. Additionally, my projects in AI research, PyTorch CNN development, and computer vision using TensorFlow demonstrate my ability to translate complex technical concepts into practical solutions.}

% Demonstrating alignment with company values and aspirations
\lettercontent{Arrowhead's commitment to developing innovative therapies aligns with my passion for leveraging technology to address real-world challenges. I am particularly excited about the opportunity to work on designing intranet pages and creating interactive experiences that enhance user engagement, reflecting my desire to contribute proactively to the team at Arrowhead Pharmaceuticals.}

% Closing the letter
\lettercontent{I am eager to bring my technical skills, creativity, and enthusiasm to the Web Designer Intern role at Arrowhead Pharmaceuticals and contribute to the company's mission of revolutionizing RNA interference therapeutics. Thank you for considering my application.}

% Signature
\signature{Adem Mcharek}

\end{document}