\documentclass[]{cover}
\usepackage{hyperref}

\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{User Testing}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my interest in the Software Engineering Intern position at User Testing as advertised. With a strong foundation in back-end technologies including Node.js and Ruby on Rails, coupled with my proficiency in Object-Oriented Programming languages, I am excited about the opportunity to contribute to the development of the contributor side of the User Testing platform.}

\lettercontent{My experience aligns well with the requirements outlined for the role, particularly in my understanding of Service-Oriented Architecture and microservices, as well as my capability in software testing. Being passionate about User Experience, I am driven by a keen attention to detail and a strong analytical mindset that allows me to solve complex problems effectively.}

\lettercontent{During my academic and professional journey, I have honed my abilities in delivering high-quality software solutions and collaborating effectively with multidisciplinary teams. I am eager to leverage these skills at User Testing to enhance the User Testing Contributor Network and ensure seamless experiences for our users globally.}

% Conclusion and signature
\lettercontent{I am thrilled about the prospect of joining a renowned organization like User Testing, known for its commitment to transforming how businesses understand and connect with their customers. I am eager to contribute to this mission and grow professionally within your innovative team.}

\signature{Adem Mcharek}

\end{document}