\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Astranis Space Technologies}
\companyaddress{
San Francisco, California
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my strong interest in the Software Developer, Network/Payload Software Intern position at Astranis Space Technologies as advertised. With a background in Computer Science and a keen passion for space technology and satellite communications, I am excited about the opportunity to contribute to Astranis' mission of bridging the digital divide and connecting communities globally.}

\lettercontent{I am currently pursuing a Bachelor's degree in Computer Science at [University], where I have gained proficiency in C++, Python, and scripting languages. Through my academic projects and internships, I have honed my skills in designing, writing, and testing software from scratch, aligning closely with the responsibilities outlined for this role.}

\lettercontent{Being part of a company that not only excels in technological innovation but also prioritizes social impact is highly motivating to me. Astranis' dedication to bringing high-speed internet to underserved areas resonates with my values of using technology for the betterment of society. I am particularly intrigued by the opportunity to work on software that manages satellite performance from ground stations, a role that perfectly combines my technical skills and passion for space technology.}

\lettercontent{Furthermore, my familiarity with RF and signal processing, along with my exposure to real-time operating systems, positions me well to contribute effectively to Astranis' projects and initiatives. I am eager to collaborate with the talented engineering team at Astranis and actively participate in the development of cutting-edge software solutions for satellite communication networks.}

\lettercontent{I am thrilled about the prospect of joining Astranis Space Technologies and contributing to its groundbreaking work in revolutionizing satellite technology for global connectivity. Thank you for considering my application. I look forward to the possibility of discussing how my skills and experiences align with Astranis' goals in further detail.}

% Conclusion and signature
\signature{Adem Mcharek}

\end{document}