\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

% Header section with personal information
\namesection{Adem}{Mcharek}{
    \urlstyle{same}\href{https://github.com/adem-mcharek}{Github} |
    \urlstyle{same}\href{https://linkedin.com/in/adem-mcharek}{Linkedin} |
    +1 929-527-4331 |
    adem.mcharek@my.liu.edu
}

% Main cover letter content starts here
\hfill

\begin{minipage}[t]{0.5\textwidth}
\companyname{Hatch IT}
\companyaddress{
Tysons, Virginia
}
\end{minipage}

\begin{minipage}[t]{0.49\textwidth}
\currentdate{\today}
\end{minipage}

% Introduction and expression of interest
\lettercontent{Dear Hiring Manager,}

\lettercontent{I am writing to express my keen interest in the Internship opportunity at Hatch IT for the Modeling & Simulation, Data Analytics, and Cloud Engineering with JDSAT for Summer 2024. With a deep passion for positive change and a commitment to leveraging technology to create unprecedented outcomes, I am excited about the prospect of contributing to innovative projects that align with my academic background and aspirations.}

\lettercontent{As a current college senior majoring in Computer Science, I have acquired a solid foundation in programming languages such as Python, Java, and SQL, which I believe will be instrumental in tackling the challenges and opportunities within the fields of modeling & simulation, data analytics, and cloud engineering. My coursework and hands-on projects have honed my analytical skills and fostered a practical understanding of data manipulation techniques.}

\lettercontent{Furthermore, my exposure to cloud platforms like AWS aligns well with the desired qualifications for the Cloud Engineering aspect of the internship. I am eager to deepen my knowledge in this area and leverage cloud technologies to contribute meaningfully to the projects at JDSAT.}

% Conclusion and signature
\lettercontent{I am enthusiastic about the prospect of working on impactful projects that contribute to organizational goals, gaining valuable insights into modeling and simulation techniques, data analytics strategies, and cloud engineering best practices, as well as being part of a collaborative and inclusive team that values innovation and creativity. With a proven track record of adaptability, creativity, and dedication, I am confident in my ability to thrive in this dynamic internship environment.}

\lettercontent{Enclosed you will find my resume, and I would welcome the opportunity to discuss how my skills and experiences align with the requirements of the internship in more detail. Thank you for considering my application.}

\signature{Adem Mcharek}

\end{document}